### 2018-05-12 nips2018/CSCmodel.tex
upload draft

\section{Convolutional Sparse Coding (CSC)}
Specifically, the CSC problem is trying to minimize
\begin{equation}
\begin{split}
    \minimize{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
    \subjectto & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in {1,...K},
\end{split}
\end{equation}
where $\signal \in \mathbb{R}^D$ is a D-dimensional signal or a vectorized image~\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the k-th dictionary and $\code_k$ is the sparse code associated with that dictionary, and it has the same dimension size as $\signal$. $K$ is the number of dictionary filters, and $*$ is the convolution operator. The above equations will be applied to all the training images.

The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent. There exists several issues regarding to the model and the frequency solvers.

\begin{itemize}
  \item Though CSC overcomes the independence assumption held in patch-based learning algorithms, far more variables ($K$ times more), as a payback, will be introduced to represent a single image. This brings in more severe memory and computational burden.
  \item The reconstructed sparse codes show that in the case of $K=100$, the majority of the entries (more than $99.5\%$) do not provide valid information to the represented image, which indicates the subproblem for updating $\code$ solves a highly sparse LASSO problem. Transforming the problem into frequency domain imposes restriction on the use of optimization strategies for this very specific problem.
  \item The prior work shows its efficiency of solving the CSC problem in frequency domain, while this is only applicable for updating $\code$, and it does not hold for updating $\filter$. Dictionaries usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$), while in order to tackle the problem in frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
\end{itemize}

### 2018-05-12 nips2018/Introduction.tex
upload draft

\section{Introduction}
Convolutional Sparse Coding (CSC) has been demonstrated to be an effective tool to learn translational invariant dictionaries from a number of training signals, and shows its applications in recent researches obout neural and brain information processing~\cite{jas2017learning,peter2017sparse}, as well as in a variety of image processing tasks, for instance, image inpainting~\cite{heide2015fast}, super-resolution~\cite{gu2015convolutional}, high dynamic range imaging~\cite{serrano2016convolutional}, and high-dimensional signal reconstructions~\cite{choudhury2017consensus,bibi2017high}. CSC differs from conventional sparse coding by formulating the signals as a summation of a set of convolutions on dictionary filters and sparse codes, rather than linearly adding up those filters. Alternatively, sparse coding, as a patch-based approach, learns filters from partitioned local structures, and this partition operation discards inherent correlations between those patches, so as to learns redundant filters (the same or similar ones with translated versions). Owing to the convolutional property, the dictionaries learned from CSC achieves signal global coherence, tending to be more representative. It should be emphasized that the convolutional-based deep learning, evolving from pioneering work~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet}, has shown its extraordinary success in a broad range of high-level image understanding applications. This supervised learning based approach refers to one type of discriminative models, whereas, CSC is a kind of generative model, which, in general, is less task-specific than discriminative models.

To solve the optimization problems formulated in CSC, \cite{zeiler2010deconvolutional} iteratively solves two subproblems (updating sparse coding and updating filters) using gradient decent in the form of convolutional operations, while performing convolution in spatial domain is computationally expensive. Recent algorithms tackles the problem by exploiting Parseval's theorem to express spatial convolution by multiplication in the frequency domain and using Alternating Direction Method of Multipliers (ADMM)~\cite{boyd2011distributed} to separate the non-smooth terms in the optimization problem, and they show tremendous improvements over spatial solvers with respect to running time~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}. Most of the prior work learns the dictionary filters in a batch mode, which indicates that all training signals are involved in every training iteration, and this restricts it from applying to large datasets or streaming data.

In contrast to batch mode learning, online learning~\cite{shalev2012online} is a well established strategy which processes a single or a portion (minibatch) of the whole data at each training step, and incrementally updates model variables. Herein, the required memory and computing sources are only dependent on the sample size in every observation, independent of the training data size. It alleviates the scalability issue arisen in batch approaches, and was firstly synergetic with sparse coding based on stochastic approximation~\cite{bousquet2008tradeoffs}, which was then scaled up to millions of training samples~\cite{mairal2009online,mairal2010online}. More recently, \cite{liu-2018-first} proposed an online learning based CSC algorithm, and analyzed different solvers and strategies when implementing it.

{\bfseries Contributions.} We mainly make three contributions in this work. First of all, we introduce a randomization strategy in the subproblem of updating sparse codes and solve the entire problems in spatial domain. It demonstrates that the proposed spatial solver, with a reasonably selected subsampling probability, outperforms the state-of-the-art frequency solvers with less computation time (per iteration), and also achieves faster convergence (less number of iterations). We then formulate an online-learning version of the proposed algorithm, and it shows dramatic runtime improvement over prior online CSC methods, as well as better learning outcomes. At last, we demonstrate its capability to learn the over-complete dictionary from thousands of images, and analyze the effectiveness of the learned over-complete dictionary, which has not been reported or analyzed by precedent CSC work.

### 2018-05-12 nips2018/Results.tex
upload draft

\section{Results} \label{sec:result}
\subsection{Sub-Sampling Strategy}
We first evaluate the convergence and effectiveness of the proposed sub-sampling strategy, and compare it with state-of-the-art frequency solver~\cite{heide2015fast}. The proposed algorithm, with different sub-sampling factors, was tested on the fruit dataset~\cite{zeiler2010deconvolutional} which contains 10 training images in the size of $100 \times 100$. The dictionary dimension size is set to $11 \times 11 \times 100$.

{\bfseries Convergence.} Comparisons of the convergence between the proposed method and the state-of-the-art are shown in Fig.~\ref{fig:subsampleResult}. A different selection of the subsampling probability reveals that the proposed strategy will slightly influence the convergence and the training objective of the minimization problem. Specifically, the more subsampled, the relatively slower convergence and the higher objective will be obtained. On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solvers for one iteration. We observe that a subsampling rate between $0.1$ and $0.2$ delivers empirically good enough convergence in our settings, as well as achieving at least $3 \times$ speedup. It should be clarified that for a better representation, the cropped objectives are plotted after the first iteration, while all of them have the same initial objective. Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to a optimum with comparable objective after 10 iterations. In summary, comparing to the state-of-the-art frequency solver, the proposed method with a subsampling rate of $10\%$ not only spends two times less processing time per iteration, but also needs fewer iterations to converge.

\begin{figure}[h]
\begin{subfigure}{0.6\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobj.pdf}
\end{subfigure} 
\begin{subfigure}{0.3\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
\end{subfigure}

\begin{subfigure}{0.6\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobj.pdf}
\end{subfigure}
\begin{subfigure}{0.3\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
\end{subfigure}

\caption{Left: Convergence comparison between the-state-of-art method\cite{heide2015fast} and the proposed method with different subsampling probability. Right: Learned filters by the proposed method with $p=0.1$ and the comparable method. In these represented learned filters, our method learns more Gabor-like and less noise-like filters. Beyond this, it runs faster with regard to each iteration and shows better convergence behavior.}
\label{fig:subsampleResult}
\end{figure}

{\bfseries Reconstruction}. The learned filters by the proposed method with subsampling rate $0.1$ are shown on the right hand side of Fig.~\ref{fig:subsampleResult}. For a visual comparison, we also show the filters learned from the competing method. As can be observed, both of them learn some seemingly similar Gabor-like filters. While after zooming, it can be seen that our learned Gabor-like filters have less impure structures. Moreover, the comparable filters contain a number of noise-like dictionaries, which are rarely existed in ours. We then demonstrate the effectiveness of the reconstructed filters in the application of image inpainting, which refers to reconstructing a full image from partial measurements. A numerical comparison of the reconstruction quality is shown in Fig.~\ref{fig:PSNRrecon}. The filters learned by the proposed method not only show more visually decent structures and less specific features, but also demonstrate its capability to better reconstruct partial observed images. In addition to that, the learning process only takes about $40\%$ of the execution time of the comparison.

\begin{figure}[h]
    \includegraphics[width=1\textwidth]{figure/reconImage.pdf}
    \\
    \resizebox{1\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 25.77 & 24.67 & 24.89 & 23.88 & 24.68 & 25.26  & 24.15 & 25.75 & 22.97 & 26.16 \\
            \hline
            PSNR ours & \textbf{25.91} & \textbf{24.72} & \textbf{25.21} & \textbf{24.09} & \textbf{25.00} & \textbf{25.36} & \textbf{24.32} & \textbf{25.80} & \textbf{23.24} & \textbf{26.37} \\
            \hline
        \end{tabular} }
    \caption{Numerical comparisons of the reconstruction quality obtained from the presented filters and its comparison. The reconstructions are performed on $20\%$ randomly observed images, with $\lambda = 0.4$ and $50$ ADMM iterations for both cases. Obtained PSNR values are averaged on 5 trials. Note that none of the testing images are in the training sets.} \label{fig:PSNRrecon}
\end{figure}

\subsection{Online Learning Settings}
We further evaluate the online fashion of the proposed method. To begin with, we validate the proposed algorithm on the city dataset~\citep{zeiler2010deconvolutional}, which has 10 training images and 4 testing images, and all of them has the size of $100 \times 100$. Afterwards, over-complete dictionaries are learned from 1000 images randomly picked up from ImageNet~\cite{deng2009imagenet}.

{\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire
dataset cannot be evaluated since each training step only draws one or a few of the data samples. Otherwise, we can evaluate the learning process on testing images. The loss objectives on testing dataset of the proposed algorithm (SOCSC) and prior published online CSC model solved in frequency domain~\citep{liu-2018-first} (FOCSC), with respect to iterations and time, are shown in Fig.~\ref{fig:onlineConvergence}. The proposed method not only exhibits a better convergence performance, but also takes much less execution time, achieving roughly $5 \times$ speedup for one iteration. A visual comparison of the learned dictionaries also demonstrates that the proposed algorithm delivers better outcomes. Further numerical comparison will be reported in the next section.

\begin{figure}[h]
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobjOnline.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobjOnline.pdf}
\end{subfigure}

\caption{}
\label{fig:onlineConvergence}
\end{figure}

{\bfseries Over-complete dictionaries.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (the number of filters is more than the degrees of freedom). One of the reasons could be that most of the prior work is batch-based approach, thus learning over-complete dictionary from small dataset would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability. The proposed online-based learning strategy can overcome this issue by scaling up to arbitrary sample sizes.

We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.~\ref{fig:overCompleteDic} . As a comparison, 100 learned filters by the same algorithm and its comparable approach are also represented for a visual comparison. As can be observed, both of the approaches learn visually similar under-complete dictionaries, while the proposed method shows a $5 \times$ speedup over the other. Furthermore, the learned over-complete dictionary is composed of the gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries. These additional feature information would play an essential role to better represent the natural images, which can be demonstrated in Fig.~ . There is a bottleneck for under-complete dictionary that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches. However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement with regard to PSNR to have a sparse representation of the testing images.

\begin{figure}[h]
\begin{minipage}{0.4\textwidth}
\begin{subfigure}{1\textwidth}
    \centering
  \includegraphics[width=0.6\linewidth]{figure/liu100-filter.pdf}
  \vspace*{2mm}
\end{subfigure}

\begin{subfigure}{1\textwidth}
    \centering
  \includegraphics[width=0.6\linewidth]{figure/online100-filter.pdf}
\end{subfigure}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\centering
\includegraphics[width=1\linewidth]{figure/online400-filter.pdf}
\end{minipage}

\caption{Filters learned from 1000 images by the proposed method and its comparison. (a) The under-complete dictionary ($11 \times 11 \times 100$) learned by~\cite{liu-2018-first}; (b) The under-complete dictionary ($11 \times 11 \times 100$) learned by the proposed method. (c) The over-complete dictionary ($11 \times 11 \times 400$) learned by the proposed method. These under-complete dictionaries, mainly composed of gabor-like filters, can be seen as a subset of the represented over-complete dictionary, which also contains a number of low contrast image features.}
\label{fig:overCompleteDic}
\end{figure}

### 2018-05-12 nips2018/SCSCmodel.tex
upload draft

\section{Stochastic Convolutional Sparse Coding}
\subsection{The Model}
Since the images are represented by a set of highly sparse codes, we have observed that they can be well reconstructed by a random subset of the sparse codes. Based on this observation, we propose a variant of the $\code$-subproblem using subsampling strategy, and formulate the following modified minimization problem:
\begin{equation} \label{eq:updatingCode}
    \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^T)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
\end{equation}
where $\Filter = [\Filter_1 ... \Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1^T ... \code_K^T]^T \in \mathbb{R}^{DK \times 1}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.  $\mask$ is a randomized sub-sampling diagonal matrix with $1$ on the entries corresponding to the sampled sparse codes, performing the function of choosing a random portion of the sparse codes for reconstruction. Herein, the $\code$-subproblem only computes the sparse codes in the chosen positions. Due to the introduced subsampling matrix, the convolution operator will not hold, hence it cannot be solved in the frequency domain. This subsampling strategy is akin to the dropout technique~\cite{srivastava2014dropout}, which has been widely used to prevent overfitting when training deep neural networks. However, different from dropout that generally needs more time to train a neural network than standard approaches, with a good selection of subsampling probability $p$, the proposed method shows less per iteration running time and faster convergence than state-of-the-arts (see section~\ref{sec:result}).

After obtaining the subsampled codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
\begin{equation} \label{eq:updatingFilter}
    \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2, ~\subjectto ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in {1,...K},
\end{equation}
where $\Code= [\Code_1 ... \Code_K] \in \mathbb{R}^{D \times MK}$ and $\filter= [\filter_1^T ... \filter_K^T]^T \in \mathbb{R}^{MK \times 1}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.

Like the approach in~\cite{heide2015fast}, we interleave on the above two subproblems to tackle the bi-convex problem, and each of them will be solved by ADMM. The jointly optimization framework will be implemented in the fashions of batch mode and online mode.

\begin{minipage}[t]{0.5\textwidth}
\vspace{0pt}
\begin{algorithm}[H]
\caption{SBCSC} \label{algo:SBCSC}
\begin{algorithmic}[1]
\State $\text{Initialize} ~ \filter;$
\While {not converge}
    \State $\Filter \gets \text{constructD}(\filter);$
    \For{i=1 to N}
        \State $ \text{Generate } \mask \text{ given } p;$
        \State $ \text{Update } \code^i \text{ by solving problem~\ref{eq:updatingCode}};$
    \EndFor
    \State $\Code \gets \text{constructZ}(\code^{1,...,N});$
    \State $\text{Update } \filter \text{ by solving problem~\ref{eq:updatingFilter}} ;$
\EndWhile
\end{algorithmic}
\end{algorithm}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{0pt}
\begin{algorithm}[H]
\caption{SOCSC} \label{algo:SOCSC}
\begin{algorithmic}[1]
\State $\text{Initialize} ~ t=0, \filter^t,  \surC^t = 0, \surB^t = 0$
\While {not converge}
    \State $\Filter \gets \text{constructD}(\filter^t);$
    \State $t \gets t+1$
    \State draw($\signal^t$, $\mask$);
    \State $ \text{Compute } \code^t \text{ by solving problem~\ref{eq:updatingCodeOnline}};$
    \State $\Code \gets \text{constructZ}(\code^t)$
    \State Compute $\surC^t$ and $\surB^t$ by eq~\ref{eq:updateSur}
    \State Update $\filter^t$ by solving problem~\ref{eq:updatingFilterOnline}
\EndWhile
\end{algorithmic}
\end{algorithm}
\end{minipage}

\subsection{Stochastic Batch CSC (SBCSC)}
We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the probability for one specific code been selected. Every outer loop involves all of the training images, thus it would be expensive in computing these and also runs out of memory quickly with the increase of the number of images. The batch-based learning algorithm lacks of the capability to scale up to very large datasets or to handle dynamically changed training data.

\subsection{Stochastic Online CSC (SOCSC)}
We can further tackle the proposed problem in online fashion for a gain of scalability. In the online learning setting, each iteration only draws one or a subset (minibatch) of the total training images, hence the complexity per loop is independent of the training sample size. Then, given the sampled image $\signal^t$ at $t$-th iteration, we can compute the corresponding sparse codes $\code^t$ by
\begin{equation} \label{eq:updatingCodeOnline}
    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} \mask^T)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
\end{equation}
where $\Filter^{t-1}$ is constructed from the dictionaries learned by $(t-1)$th iteration. After obtaining the sparse codes, the dictionary is updated by:
\begin{equation}
    \filter^t = \minimize{\filter} \frac{1}{2t}\sum_{i=1}^{t} \|\signal^i - \Code^i \filter \|_2^2, ~\subjectto ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in {1,...K}.
\end{equation}
Notice that updating dictionary involves all the past training images and sparse codes. As shown in~\cite{mairal2009online,mairal2010online}, we can get rid of explicitly storing those data by introducing two surrogate matrices $\surC \in \mathbb{R}^{KM \times KM}$ and $\surB \in \mathbb{R}^{KM \times 1}$, which carry all of the required information for updating $\filter$, and can be iteratively updated by:
\begin{equation} \label{eq:updateSur}
    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^T\Code^t ~~~~~~~~~ \surC^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^T\signal^t
\end{equation}
If so, the updated dictionary can be obtained by solving:
\begin{equation} \label{eq:updatingFilterOnline}
    \filter^t = \minimize{\filter} \frac{1}{2} \filter^T\surC\filter - \filter^T\surB, ~ \subjectto ~ \|\filter_k\|_2^2 \leq 1 ~ \forall k \in {1,...K}
\end{equation}

\subsection{Implementation Details}
Updating $\code$ in Algorithm\ref{algo:SBCSC} (Problem~\ref{eq:updatingCode}) is the standard LASSO, and we solve it by well-known ADMM framework. The data fitting term and the $L_1$ penalty term are split, forming $x$-minimization step and $z$-minimization step, respectively. $x$-minimization step is a quadratic programming (QP) problem, and we cache the matrix factorization by Cholesky decomposition. $z$-minimization step can be solved by a point-wise shrinkage operation. Accordingly, updating $\filter$ (problem~\ref{eq:updatingFilter}) is a quadratic constrained quadratic programming (QCQP) problem, and we solve it using similar splitting and optimization strategies as solving Problem~\ref{eq:updatingCode}, except using Conjugate Gradient (CG) for $x$-minimization step and replacing the shrinkage function by projecting onto the constrained set for $z$-minimization step. The $\filter$-subproblem is warm started with previously computed results and these two subproblems are interleaved on their auxiliary variables. The corresponding subproblems in Algorithm~\ref{algo:SOCSC} are solved following the same optimization strategy as discussed above. We set the hyperparameters $\lambda=1$,  the augmented Lagrangian penalty $\rho_{\code}$ and $\rho_{\filter}$ to $10 \lambda$ and $50 \lambda$, respectively, for $\code$- and $\filter$-subroblem. The ADMM iteration is fixed to 10 for all subroutines, and the over-relaxation strategy within ADMM is applied with $\alpha = 1.8$. The residual tolerance for CG is $1e^{-5}$.

All the training and evaluation processes in this manuscript are performed on contrast normalized images. %We also tried to learning filters from images without pre-processing with little parameters tuning, which successfully learns similar Gabor-like features as learned from contrast normalized images, as well as low frequency filters. The results regarding to this will not be discussed in this work, while it can be applied to other applications where low frequency parts also need to be taken into account. %
It should be noted that matrix $\Code$ needs to be explicitly constructed and it may lead to a considerable computational burden, resulting in a heavy overhead if processed in an inefficient way. In our implementation, the vector-to-matrix mapping information is cached for an efficient indexing. As for matrix $\Filter$, we only explicitly construct matrix $(\Filter \mask^T)$ rather than $\Filter$ and $\mask$ separately for the sake of efficiency, and the similar indexing strategy is applied.

### 2018-05-13 Stochastic Convolutional Sparse Coding/CSCmodel.tex
update draft

--- 2018-05-12 nips2018/CSCmodel.tex
@@
 \end{equation}
-where $\signal \in \mathbb{R}^D$ is a D-dimensional signal or a vectorized image~\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the k-th dictionary and $\code_k$ is the sparse code associated with that dictionary, and it has the same dimension size as $\signal$.
+where $\signal \in \mathbb{R}^D$ is a D-dimensional signal or a vectorized image~\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary and $\code_k$ is the sparse code associated with that dictionary, and it has the same dimension size as $\signal$.
 $K$ is the number of dictionary filters, and $*$ is the convolution operator.
@@
 
-The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent.
-There exists several issues regarding to the model and the frequency solvers.
+The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
+There exists several common issues regarding to the model and the frequency solvers.
 
@@
   \item The prior work shows its efficiency of solving the CSC problem in frequency domain, while this is only applicable for updating $\code$, and it does not hold for updating $\filter$.
-Dictionaries usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$), while in order to tackle the problem in frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
+The dictionary filters usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$), while in order to tackle the problem in frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
 \end{itemize}

### 2018-05-13 Stochastic Convolutional Sparse Coding/Introduction.tex
update draft

\section{Introduction}
Convolutional Sparse Coding (CSC) has been demonstrated to be an effective tool to learn translational invariant dictionary from a number of training signals, and shows its applications in recent researches obout neural and brain information processing~\cite{jas2017learning,peter2017sparse}, as well as in a variety of image processing tasks, for instance, image inpainting~\cite{heide2015fast}, super-resolution~\cite{gu2015convolutional}, high dynamic range imaging~\cite{serrano2016convolutional}, and high-dimensional signal reconstructions~\cite{choudhury2017consensus,bibi2017high}. CSC differs from conventional sparse coding by formulating the signals as a summation of a set of convolutions on dictionary filters and sparse codes, rather than linearly adding up those filters. Alternatively, sparse coding, as a patch-based approach, learns filters from partitioned local structures, and this partition manipulation discards inherent correlations between those patches, so as to learns redundant filters (the same or similar ones with translated versions). Owing to the convolutional property, the dictionary learned from CSC achieves signal global coherence, tending to be more representative. It should be emphasized that the convolutional-based deep learning, evolving from pioneering work~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet}, has shown its extraordinary success in a broad range of high-level image understanding applications. This supervised learning based approach refers to one type of discriminative models, whereas, CSC is a kind of generative model, which, in general, is less task-specific than discriminative models.

To solve the optimization problems formulated in CSC, Zeiler et al.~\cite{zeiler2010deconvolutional} iteratively solves two subproblems (updating sparse codes and updating filters) using gradient decent in the form of convolutional operations, while performing convolution in spatial domain is computationally expensive. Recent algorithms tackles the problem by exploiting Parseval's theorem to express the spatial convolution by multiplication in the frequency domain and using Alternating Direction Method of Multipliers (ADMM)~\cite{boyd2011distributed} to separate the non-smooth terms in the optimization problem, and they show tremendous improvements over spatial solvers with respect to running time~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}. Most of the prior work learns the dictionary filters in a batch mode, which indicates that all training signals are involved in every training iteration, and this restricts it from applying to large datasets or streaming data.

In contrast to batch mode learning, online learning~\cite{shalev2012online} is a well established strategy which processes a single or a portion (mini-batch) of the whole data at each training step, and incrementally updates model variables. Herein, the required memory and computing sources are only dependent on the sample size in every observation, independent of the training data size. It alleviates the scalability issue arisen in batch approaches, and the convergence of the algorithm was firstly analyzed using stochastic approximation tools~\cite{bottou1998online}. Bottou et al.~\cite{bousquet2008tradeoffs} further showed better generalization performance of the stochastic algorithms than standard gradient descent on large scale learning systems. Later on, online learning strategies were synergetic with sparse coding, which was then scaled up to learn dictionary from millions of training samples~\cite{mairal2009online,mairal2010online}. More recently, Liu et al.~\cite{liu-2018-first} proposed an online learning based CSC model, and analyzed different solvers and strategies when implementing it.

{\bfseries Contributions.} We mainly make three contributions in this work. First of all, we introduce a randomization strategy in the subproblem of updating sparse codes and solve the entire problems in spatial domain. It demonstrates that the proposed spatial solver, with a reasonably selected subsampling probability, outperforms the state-of-the-art frequency solvers with less computation time (per iteration), and also achieves faster convergence (less number of iterations). We then formulate an online-learning version of the proposed algorithm, and it shows dramatic runtime improvement over precedent online CSC methods, as well as producing similar outcomes. At last, we demonstrate its capability to learn the over-complete dictionary from thousands of images, and analyze the effectiveness of the learned over-complete dictionary, which has not been reported or analyzed by precedent CSC work.

### 2018-05-13 Stochastic Convolutional Sparse Coding/Results.tex
update draft

--- 2018-05-12 nips2018/Results.tex
@@
 It should be clarified that for a better representation, the cropped objectives are plotted after the first iteration, while all of them have the same initial objective.
-Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to a optimum with comparable objective after 10 iterations.
+Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
 In summary, comparing to the state-of-the-art frequency solver, the proposed method with a subsampling rate of $10\%$ not only spends two times less processing time per iteration, but also needs fewer iterations to converge.
@@
 To begin with, we validate the proposed algorithm on the city dataset~\citep{zeiler2010deconvolutional}, which has 10 training images and 4 testing images, and all of them has the size of $100 \times 100$.
-Afterwards, over-complete dictionaries are learned from 1000 images randomly picked up from ImageNet~\cite{deng2009imagenet}.
+Afterwards, we analyze the effectiveness of over-complete dictionary learned from 1000 images randomly picked up from ImageNet~\cite{deng2009imagenet}.
 
-{\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire
-dataset cannot be evaluated since each training step only draws one or a few of the data samples.
+{\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire dataset cannot be evaluated since each training step only draws one or a few of the data samples.
 Otherwise, we can evaluate the learning process on testing images.
-The loss objectives on testing dataset of the proposed algorithm (SOCSC) and prior published online CSC model solved in frequency domain~\citep{liu-2018-first} (FOCSC), with respect to iterations and time, are shown in Fig.~\ref{fig:onlineConvergence}.
-The proposed method not only exhibits a better convergence performance, but also takes much less execution time, achieving roughly $5 \times$ speedup for one iteration.
+The loss objectives on testing dataset of the proposed algorithm and prior published online CSC model solved in frequency domain~\citep{liu-2018-first}, with respect to iterations, are shown in Fig.~\ref{fig:onlineSmall}.
+In the same figure, we also keep track of the capability of the updated filters in the learning process to sparsely represent the testing images, which are demonstrated by its PSNR.
+These two approaches stop at optimum positions with close testing objective values, though, they exhibit slightly different convergence behaviors with respect to iterations.
+The final testing PSNR values for both methods also reveal the similar reconstruction performance of the learned filters.
+As for the runtime comparison, the proposed method runs at least 5 times faster than its comparative.
+
+%The proposed method not only exhibits a better convergence performance, but also takes much less execution time, achieving roughly $5 \times$ speedup for one iteration.
 A visual comparison of the learned dictionaries also demonstrates that the proposed algorithm delivers better outcomes.
-Further numerical comparison will be reported in the next section.
+% Further numerical comparison will be reported in the next section.
 
 \begin{figure}[h]
+\centering
 \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=1\linewidth]{figure/iteVSobjOnline.pdf}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
 \end{subfigure} 
 \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=1\linewidth]{figure/timeVSobjOnline.pdf}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
 \end{subfigure}
 
-\caption{}
-\label{fig:onlineConvergence}
+\caption{Left: Convergence of the test set objectives for the proposed method and its comparison~\cite{liu-2018-first}.
+Right: Testing PSNR with respect to execution time.
+Our method has the similar outcomes as the comparable method, while it achieves $5 \times$ speedup.
+}
+\label{fig:onlineSmall}
 \end{figure}
@@
 The proposed online-based learning strategy can overcome this issue by scaling up to arbitrary sample sizes.
-
-We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.~\ref{fig:overCompleteDic} .
-As a comparison, 100 learned filters by the same algorithm and its comparable approach are also represented for a visual comparison.
-As can be observed, both of the approaches learn visually similar under-complete dictionaries, while the proposed method shows a $5 \times$ speedup over the other.
-Furthermore, the learned over-complete dictionary is composed of the gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
-These additional feature information would play an essential role to better represent the natural images, which can be demonstrated in Fig.~ .
-There is a bottleneck for under-complete dictionary that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
-However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement with regard to PSNR to have a sparse representation of the testing images.
 
@@
 \end{figure}
+
+We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.~\ref{fig:overCompleteDic} .
+As a comparison, 100 learned filters by the same algorithm and its comparable approach are also represented for a visual comparison.
+As can be observed, both of the approaches learn visually similar under-complete dictionaries, while the proposed method shows a $5 \times$ speedup over the other.
+Furthermore, the learned over-complete dictionary is composed of the gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
+These additional feature information would play an essential role to better represent the natural images, which can be demonstrated in Fig.~\ref{fig:overCompleteDic}.
+
+There is a bottleneck for under-complete dictionary revealed in the left hand side of fig.~\ref{fig:overComDicAndMinibatch}, that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
+However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement with regard to PSNR to have a sparse representation of the testing images.
+
+{\bfseries Mini-batch.} In practice, the mini-batch strategy would be preferred for a gain of convergence speed, rather than drawing a single sample in each training step.
+This is also a standard extension to stochastic algorithms.
+We denote the mini-batch size as $\eta$.
+In the proposed algorithm, the time complexity for one step dictionary update will not increase linearly with the increase of $\eta$.
+Concretely speaking, updating $\code$ is implemented by Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
+Herein, the complexity for updating $\eta$ $\code$s at once is cheaper than $\eta$ times the complexity of updating one $\code$.
+In addition, the time complexity for updating $\filter$ is not affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
+One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this is not dominant in the runtime.
+The results for various mini-batch sizes are shown in Fig.~\ref{fig:overComDicAndMinibatch}.
+The learned filters are examined on the test set every $2^i$ iterations and the last iteration, where $i=0,1,...$.
+Note that larger $\eta$ will result in less number of iterations to process all 1000 images.
+A larger mini-batch size shows a greater progress for first few training steps, though it takes additional running time and memory.
+Overall, mini-batched updates provides a more runtime efficient learning progress in online-based CSC model, and $\eta=20$ achieves one magnitude speedup to reach a condition with same level convergence.
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}{0.4\textwidth}
+  \includegraphics[width=1\linewidth]{figure/overComplete-ite.pdf}
+\end{subfigure} 
+\begin{subfigure}{0.55\textwidth}
+  \includegraphics[width=1\linewidth]{figure/minibatch.pdf}
+\end{subfigure}
+
+\caption{Left: Testing PSNR for the compared method with $K=100$, and the proposed method with $K=100$ and $K=400$, respectively.
+Every iteration draws a single image from the training dataset.
+Right: Testing PSNR for the proposed method ($K=400$) with varying values of $\eta$.}
+\label{fig:overComDicAndMinibatch}
+\end{figure}

### 2018-05-13 Stochastic Convolutional Sparse Coding/SCSCmodel.tex
update draft

--- 2018-05-12 nips2018/SCSCmodel.tex
@@
 \code_K^T]^T \in \mathbb{R}^{DK \times 1}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
-$\mask$ is a randomized sub-sampling diagonal matrix with $1$ on the entries corresponding to the sampled sparse codes, performing the function of choosing a random portion of the sparse codes for reconstruction.
+$\mask$ is a randomized subsampling diagonal matrix with $1$ on the entries corresponding to the sampled sparse codes, performing the function of choosing a random portion of the sparse codes for reconstruction.
 Herein, the $\code$-subproblem only computes the sparse codes in the chosen positions.
@@
 
-After obtaining the subsampled codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
+After obtaining the subsampled sparse codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
 \begin{equation} \label{eq:updatingFilter}
@@
 where $\Code= [\Code_1 ...
-\Code_K] \in \mathbb{R}^{D \times MK}$ and $\filter= [\filter_1^T ...
+\Code_K] \in \mathbb{R}^{D \times MK}$, constructed from computed $\code$, and $\filter= [\filter_1^T ...
 \filter_K^T]^T \in \mathbb{R}^{MK \times 1}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
@@
 Like the approach in~\cite{heide2015fast}, we interleave on the above two subproblems to tackle the bi-convex problem, and each of them will be solved by ADMM.
-The jointly optimization framework will be implemented in the fashions of batch mode and online mode.
+The joint optimization framework will be implemented in the fashions of batch mode and online mode.
 
@@
 \subsection{Stochastic Batch CSC (SBCSC)}
-We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the probability for one specific code been selected.
-Every outer loop involves all of the training images, thus it would be expensive in computing these and also runs out of memory quickly with the increase of the number of images.
+We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the uniform probability for one code been selected.
+Every outer loop involves all of the training images, thus it would be expensive in processing on these simultaneously and also runs out of memory quickly with the increase of the number of images.
 The batch-based learning algorithm lacks of the capability to scale up to very large datasets or to handle dynamically changed training data.
@@
 We can further tackle the proposed problem in online fashion for a gain of scalability.
-In the online learning setting, each iteration only draws one or a subset (minibatch) of the total training images, hence the complexity per loop is independent of the training sample size.
+In the online learning setting, each iteration only draws one or a subset (mini-batch) of the total training images, hence the complexity per loop is independent of the training sample size.
 Then, given the sampled image $\signal^t$ at $t$-th iteration, we can compute the corresponding sparse codes $\code^t$ by
@@
 \end{equation}
-where $\Filter^{t-1}$ is constructed from the dictionaries learned by $(t-1)$th iteration. After obtaining the sparse codes, the dictionary is updated by:
+where $\Filter^{t-1}$ is constructed from the dictionary learned by $(t-1)$th iteration. After obtaining the sparse codes, the dictionary is updated by:
 \begin{equation}
@@
 \end{equation}
-Notice that updating dictionary involves all the past training images and sparse codes.
+Notice that updating dictionary involves all of the past training images and sparse codes.
 As shown in~\cite{mairal2009online,mairal2010online}, we can get rid of explicitly storing those data by introducing two surrogate matrices $\surC \in \mathbb{R}^{KM \times KM}$ and $\surB \in \mathbb{R}^{KM \times 1}$, which carry all of the required information for updating $\filter$, and can be iteratively updated by:
 \begin{equation} \label{eq:updateSur}
-    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^T\Code^t ~~~~~~~~~ \surC^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^T\signal^t
+    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^T\Code^t ~~~~~~~~~ \surB^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^T\signal^t
 \end{equation}
@@
 $z$-minimization step can be solved by a point-wise shrinkage operation.
-Accordingly, updating $\filter$ (problem~\ref{eq:updatingFilter}) is a quadratic constrained quadratic programming (QCQP) problem, and we solve it using similar splitting and optimization strategies as solving Problem~\ref{eq:updatingCode}, except using Conjugate Gradient (CG) for $x$-minimization step and replacing the shrinkage function by projecting onto the constrained set for $z$-minimization step.
+Accordingly, updating $\filter$ (Problem~\ref{eq:updatingFilter}) is a quadratic constrained quadratic programming (QCQP) problem, and we solve it using similar splitting and optimization strategies as solving Problem~\ref{eq:updatingCode}, except using Conjugate Gradient (CG) for $x$-minimization step and replacing the shrinkage function by projecting onto the constrained set for $z$-minimization step.
 The $\filter$-subproblem is warm started with previously computed results and these two subproblems are interleaved on their auxiliary variables.
-The corresponding subproblems in Algorithm~\ref{algo:SOCSC} are solved following the same optimization strategy as discussed above.
+The corresponding subproblems in Algorithm~\ref{algo:SOCSC} are solved following the same optimization strategy as discussed above, and the only exception is for updating $\code$ (Problem~\ref{eq:updatingCodeOnline}), where Cholesky decomposition or conjugate gradient is alternatively chosen depending on the mini-batch size.
 We set the hyperparameters $\lambda=1$,  the augmented Lagrangian penalty $\rho_{\code}$ and $\rho_{\filter}$ to $10 \lambda$ and $50 \lambda$, respectively, for $\code$- and $\filter$-subroblem.
@@
 
-All the training and evaluation processes in this manuscript are performed on contrast normalized images.
+All training and evaluation processes in this manuscript are performed on contrast normalized images.
 %We also tried to learning filters from images without pre-processing with little parameters tuning, which successfully learns similar Gabor-like features as learned from contrast normalized images, as well as low frequency filters.

### 2018-05-13 nips2018/main.tex
update draft

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
\PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2018

% ready for submission
\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
%\usepackage[preprint]{nips_2018}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2018}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2018}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{wrapfig}
\usepackage{subcaption}

\usepackage{caption}
%\captionsetup[table]{position=bottom}

\usepackage{array}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{amsmath}

\input{macro}

\title{Stochastic Convolutional Sparse Coding}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}

\end{abstract}

\input{Introduction}

\input{CSCmodel}

\input{SCSCmodel}

\input{Results}

% \input{Discussions}

{\small
\bibliographystyle{ieeetr}
\bibliography{egbib}
}

\end{document}

### 2018-05-13 StochasticOCSC/batchCSC/BatchStochasticCSC.m

@@ -1,107 +1,0 @@
-%% first code for CSC in spatial domain
-function [ d, z, obj ]  = BatchStochasticCSC(b, test_b, d_ind, z_ind, kernel_size, lambda)
-
-    k = kernel_size(1);           
-    num_kernel  = kernel_size(end);
-
-    n = size(b,1);
-    num_image = size(b,3);
-    
-    b = reshape(b, [], num_image);
-
-    d = randn(k, k, num_kernel);
-    for i=1:num_kernel
-       d(:,:,i) =  d(:,:,i) ./ max( norm( d(:,:,i), 'fro' ), 1);
-    end
-    back_d = d(:);
-    d = back_d;
-    
-    %% parameters
-    outer_ite = 10;
-    max_it_z = 20;
-    max_it_d = 10;
-    
-    batch_size = 10;
-    total_time = 0;
-    rho_d = 10;
-    rho_z = 1;
-    hit_rate = 0.1;    % probability for choosing one specific code 
-    
-    u_d     = zeros( k*k*num_kernel, 1 );
-    x_hat_d = zeros( k*k*num_kernel, 1 );
-    z       = zeros( n*n*num_kernel, batch_size );
-    
-%     ind = 1:1:n*n*num_kernel;
-%     [ind1_all, ind2_all, v_all] = find( d_ind(:,ind) );
-
-%     test_ite = 0;
-    cur_image = 1:num_image; 
-    for ite = 1:outer_ite
-        %% test set objective
-%          if ite==1 || ite==outer_ite || mod(log2(ite),1) == 0
-%           test_ite = test_ite + 1;
-%           [z_test, d_Z, Dz, obj(test_ite)] = lassoFFT(test_b, []      ,...
-%                   [] , d, kernel_size, 1, 1, 50, 1e-3 );
-%            fprintf( 'test objective: %10.4f; non-zero elements: %6d, %6d \n', ...
-%              obj(test_ite), size( find( abs(z_test(:))>0.01),1 ),size( find( abs(z_test(:))>0.1),1 ) );
-%            if ite>30
-%               save(sprintf('filter/d%4d_mini%2d_online%3d_forget%1.1f_P%1.1f_lambda%1.1f_rho%2.1f_ite%2d_rho_%2.1f_%2d.mat',...
-%                   num_image, batch_size, num_kernel, gamma, hit_rate, lambda, ...
-%                   rho_z, max_it_z, rho_d, ite ), 'd'); 
-%            end
-%          end
[…]

### 2018-05-13 StochasticOCSC/batchCSC/CreateImagesJinhui.m

@@ -1,736 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This takes all images from the input folder, converts them to the desired
-% colorspace, removes mean/divides by standard deviations (if desired), and
-% constrast normalizes the image (if desired). If the images are of different
-% sizes, then it will padd them with zeros (after contrast normalizing) to make
-% them square (assumes that they all images have the same maximum dimension).
-% Note that some of the whitening/contrast normalization features are not
-% fully tested for datasets where the images are of variable size so please
-% use with caution in that case. For best result, resize all the images to the
-% same dimensions beforehand.
-%
-% @file
-% @author Matthew Zeiler
-% @date Mar 11, 2010
-%
-% @image_file @copybrief CreateImages.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief CreateImages.m
-%
-% @param imgs_path either 1) a path to a folder contain only image files (or other folders
-% which will be ignored), 2) a variable with the images as xdim x ydim x
-% num_colors x num_images size , 3) a path to a file that contains a variable
-% called I that has images as xdim x ydim x num_colors x num_images, or 4)
-% a path to a folder containing a single .mat file containing a variable called
-% I that has images as xdim x ydim x num_colors x num_images.
-% @param CONTRAST_NORMALIZE [optional] binary value indicating whether to contrast
-% normalize or whiten the images. Defaults to local contrast normalization ('local_cn').
-% Available types are: 'none','local_cn','laplacian_cn','box_cn','PCA_whitening',
-% 'ZCA_image_whitening','ZCA_patch_whitening',and 'inv_f_whitening'
-% @param ZERO_MEAN [optional] binary value indicating whether to subtract the mean and divides by standard deviation (current
-% commented out in the code). Defuaults to 1.
[…]

### 2018-05-13 StochasticOCSC/batchCSC/PSNR.m

@@ -1,99 +1,0 @@
-function PSNR(ref,sig_rec)
-
-% PURPOSE: To find the PSNR (peak signal-to-noise ratio) between two
-%          intensity images A and B, each having values in the interval
-%          [0,1]. The answer is in decibels (dB).
-%
-%          There is also a provision, in EXAMPLE 3 below, for images 
-%          stored in the interval [0,255], i.e. 256 gray levels. 
-%
-% SYNOPSIS: PSNR(A,B)
-%
-% DESCRIPTION: The following is quoted from "Fractal Image Compression",
-%              by Yuval Fisher et al.,(Springer Verlag, 1995),
-%              section 2.4, "Pixelized Data".
-%
-%              "...PSNR is used to measure the difference between two
-%              images. It is defined as
-%
-%                           PSNR = 20 * log10(b/rms)
-%
-%              where b is the largest possible value of the signal
-%              (typically 255 or 1), and rms is the root mean square
-%              difference between two images. The PSNR is given in
-%              decibel units (dB), which measure the ratio of the peak 
-%              signal and the difference between two images. An increase
-%              of 20 dB corresponds to a ten-fold decrease in the rms
-%              difference between two images.
-%              
-%              There are many versions of signal-to-noise ratios, but
-%              the PSNR is very common in image processing, probably
-%              because it gives better-sounding numbers than other
-%              measures."
-%
-% EXAMPLE 1: load clown
-%            A = ind2gray(X,map); % Convert to an intensity image in [0,1].
-%            B = 0.95 * A;        % Make B close to, but different from, A.
-%            PSNR(A,B)            % ---> "PSNR = +33.49 dB"
-%
-% EXAMPLE 2: A = rand(256); % A is a random 256 X 256 matrix in [0,1].
-%            B = 0.9 * A;   % Make B close to, but different from, A.
-%            PSNR(A,B)      % ---> "PSNR = +24.76 dB (approx)"
-%
-% EXAMPLE 3: For images with 256 gray levels: this function PSNR was 
-%            originally written for matrix-values between 0 and 1,
-%            because of MATLAB's preference for that interval.
-%
-%            However, suppose the matrix has values in [0,255]. Taking
-%            Example 1 above, we could change the image to 256 gray levels.
[…]

### 2018-05-13 StochasticOCSC/batchCSC/batchStoCSC.m

@@ -1,43 +1,0 @@
-addpath('../image_helpers');
-CONTRAST_NORMALIZE = 'none'; % 'local_cn'; 
-ZERO_MEAN = 1;   
-COLOR_IMAGES = 'gray'; 
-% read training and testing images
-% [b] = CreateImagesJinhui('../../proposed_CSC/imageNet/training',...
-% CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); 
-[b] = CreateImages('./dataset/fruit_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES);
- train_b = reshape(b, size(b,1), size(b,2), [] );
-
-[b] = CreateImagesJinhui('../../proposed_CSC/imageNet/testing',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-test_b = reshape(b, size(b,1), size(b,2), [] );
-
-%% Define the parameters
-kernel_size = [11, 11, 225];
-lambda = 0.1;
-
-d_ind = constructDicIndex(  kernel_size, size(train_b,1), size(train_b,2) );
-z_ind = constructCodeIndex( kernel_size, size(train_b,1) );
-%% online stochastic CSC
-t_start = tic;
-[ d, z, obj ]  = BatchStochasticCSC(train_b, [], d_ind, z_ind, kernel_size, lambda);
-toc(t_start);
-
-%% visualize dictionary
-s = 15;
-max_d = max(d(:)); min_d = min(d(:));
-dic = reshape( d, 11,11,s*s );
-figure
-sub_dic = cell(size(dic,3),1 );
-for i=1:size(dic,3)
-    sub_dic{i} = dic( :,:,i );
-end
-for i=1:size(dic,3)
-    subplot('Position',[(mod(i-1,s))/s 1-(ceil(i/s))/s 1/s-0.001 1/s-0.001]);
-    imshow( sub_dic{i}, [min_d max_d], 'init', 'fit' );
-end
-
-%% Save
-save(sprintf('d_online10_100_01.mat'), 'd_online10');
-save(sprintf('d_online10_225_01.mat'), 'd_online10_225');
-save(sprintf('d_online50_100_01.mat'), 'd_online50_100');
-save(sprintf('d_online50_225_01.mat'), 'd_online50_225');

### 2018-05-13 StochasticOCSC/batchCSC/constructCodeIndex.m

@@ -1,28 +1,0 @@
-function z_ind = constructCodeIndex( kernel_size, n )
-    
-    k = kernel_size(1);
-    z_ind = cell(n*n, 1);
-    
-    z = (1 : n*n);   
-    M=0;
-    for i=1:n
-        tmp_M = repmat( z( (n*(i-1)+1):n*i ), [k 1] );
-        tmp_M = spdiags(tmp_M, -floor(k/2):n-floor(k/2)-1, k, n);
-        tmp_M = tmp_M';
-        if( i==1 )
-            M = sparse( kron( spdiags(ones(k,1), ...
-                ceil(k/2)-i, n, k), tmp_M) );
-        else
-            M = M + sparse( kron( spdiags(ones(k,1), ...
-                ceil(k/2)-i, n, k), tmp_M) );
-        end
-    end
-    Z_ind = M;
-    
-    for i1 = 1:length(z)
-        [ind1, ind2] = find( Z_ind==z(i1) );
-        z_ind{i1}.ind1 = ind1;
-        z_ind{i1}.ind2 = ind2;
-    end
-
-end

### 2018-05-13 StochasticOCSC/batchCSC/constructDicIndex.m

@@ -1,139 +1,0 @@
-function d_ind = constructDicIndex( kernel_size, col, row, d )
-    
-    k = kernel_size(1);
-    num_kernel = kernel_size(3);
-    m = col; 
-    n = row;
-
-    d_ind = spalloc( m*n, m*n*num_kernel, k*k*m*n*num_kernel );
-    M = spalloc( m*n, m*n, k*k*m*n );
-    
-    if nargin == 3
-        d = [1:prod(kernel_size)]';
-    end
-    
-    for j=1:num_kernel
-        tmp_d = d( (j-1)*k*k+1 : j*k*k )'; 
-        for i=1:k           
-            tmp_M = repmat( tmp_d( k*i:-1:(k*(i-1)+1) ), [m 1] );
-            tmp_M = spdiags(tmp_M, -floor(k/2):floor(k/2), m, m);
-            if( i==1 )
-                M = kron( spdiags(ones(n,1), ...
-                    ceil(k/2)-i, n, n), tmp_M);
-            else
-                M = M + kron( spdiags(ones(n,1), ...
-                    ceil(k/2)-i, n, n), tmp_M);
-            end
-        end
-        d_ind(:, (m*n*(j-1)+1):m*n*j) = M;
-    end
-
-end
-
-
-% function dic_index = constructDicIndex( kernel_size, image_size )
-% 
-%     k = kernel_size(1);
-%     num_kernel = kernel_size(3);
-%     n = image_size;
-% 
-%     D = spalloc( n*n, n*n*num_kernel, k*k*n*n*num_kernel );
-%     M = spalloc( n*n, n*n, k*k*n*n );
-%     
-%     d = [1:prod(kernel_size)]';
-%     
-%     tic;
-%     for j=1:num_kernel
-%         for i=1:k
-% %              tmp_d = reshape( d(:,:,j), 1, [] );
-%             tmp_d = d( (j-1)*k*k+1 : j*k*k )'; 
-%             tmp_M = repmat( tmp_d( k*i:-1:(k*(i-1)+1) ), [n 1] );
-%             tmp_M = spdiags(tmp_M, -floor(k/2):floor(k/2), n, n);
-%             if( i==1 )
-%                 M = kron( spdiags(ones(n,1), ...
-%                     ceil(k/2)-i, n, n), tmp_M);
-%             else
[…]

### 2018-05-13 StochasticOCSC/batchCSC/dicUpdate.m

@@ -1,99 +1,0 @@
-function [z, x_hat, u, history] = dicUpdate(A, Atb, d, x_hat_d, u_d, rho, alpha,...
-                                    k, num_kernel, MAX_ITER)
-t_start = tic;
-
-QUIET    = 0;
-% MAX_ITER = 100;
-ABSTOL   = 1e-4;
-RELTOL   = 1e-2;
-
-[~, n] = size(A);
-
-x = zeros(n,1);
-
-if isempty(d)
-    z = zeros(n,1);
-else
-    z = d;
-end
-
-if isempty(x_hat_d)
-    x_hat_d = zeros(n,1);
-end
-x_hat = x_hat_d;
-
-if isempty(u_d)
-    u_d = zeros(n,1);
-end
-u = u_d;
-
-% [L U] = factor(A, rho);
-A_cal = @(p) A*p + rho.*p;
-
-if ~QUIET
-    fprintf('%3s\t%10s\t%10s\t%10s\t%10s\t%10s\n', 'iter', ...
-      'r norm', 'eps pri', 's norm', 'eps dual', 'objective');
-end
-
-for i = 1:MAX_ITER
-
-    % x-update
-     q = Atb + rho*(z - u);    % temporary value
-
-%     x = U \ (L \ q);
-    x = conj_grad(q, A_cal, x_hat, 100, 1e-5, 2);
-
-    % z-update with relaxation
-    zold = z;
-    x_hat = alpha*x + (1 - alpha)*zold;
-    z = proj_l2(x_hat + u, k, num_kernel);
-    % u-update
-    u = u + (x_hat - z);
-
-    % diagnostics, reporting, termination checks
-%     history.objval(i)  = objective(A, b, beta, x, z);
-
-    history.r_norm(i)  = norm(x - z, 'fro');
-    history.s_norm(i)  = norm(-rho*(z - zold), 'fro');
-
-    history.eps_pri(i) = sqrt(n)*ABSTOL + RELTOL*max(norm(x, 'fro'), norm(-z,'fro'));
-    history.eps_dual(i)= sqrt(n)*ABSTOL + RELTOL*norm(rho*u, 'fro');
-
-    if ~QUIET
-        fprintf('%3d\t%10.4f\t%10.4f\t%10.4f\t%10.4f\n', i, ...
-            history.r_norm(i), history.eps_pri(i), ...
-            history.s_norm(i), history.eps_dual(i));
-    end
-
[…]

### 2018-05-13 StochasticOCSC/batchCSC/l2proj.m

@@ -1,84 +1,0 @@
-function [z, x_hat, u, obj] = l2proj(A, b, d, x_hat_d, u_d, code, beta, rho, alpha,...
-                                    k, num_kernel, MAX_ITER)
-
-QUIET    = 1;
-% MAX_ITER = 100;
-ABSTOL   = 1e-4;
-RELTOL   = 1e-2;
-
-[m, n] = size(A);
-
-% save a matrix-vector multiply
-Atb = A'*b;
-
-x = zeros(n,1);
-% x_hat = zeros(n,1);
-% x = d;
-x_hat = x_hat_d;
-z = d;
-u = u_d;
-
-% cache the factorization
-A_cal = @(p) A'*(A*p) + rho.*p;
-
-if ~QUIET
-    fprintf('%3s\t%10s\t%10s\t%10s\t%10s\t%10s\n', 'iter', ...
-      'r norm', 'eps pri', 's norm', 'eps dual', 'objective');
-end
-
-t_start = tic;
-for i = 1:MAX_ITER
-
-    % x-update
-     q = Atb + rho*(z - u);    % temporary value
-
-    x = conj_grad(q, A_cal, x_hat, 100, 1e-5, 2);
-
-    % z-update with relaxation
-    zold = z;
-    x_hat = alpha*x + (1 - alpha)*zold;
-    z = proj_l2(x_hat + u, k, num_kernel);
-    % u-update
-    u = u + (x_hat - z);
-
-    % diagnostics, reporting, termination checks
-    history.objval(i)  = objective(A, b, beta, code, z);
-
-    history.r_norm(i)  = norm(x - z, 'fro');
-    history.s_norm(i)  = norm(-rho*(z - zold), 'fro');
-
-    history.eps_pri(i) = sqrt(n)*ABSTOL + RELTOL*max(norm(x, 'fro'), norm(-z,'fro'));
-    history.eps_dual(i)= sqrt(n)*ABSTOL + RELTOL*norm(rho*u, 'fro');
-
-    if ~QUIET
-        fprintf('%3d\t%10.4f\t%10.4f\t%10.4f\t%10.4f\t%10.2f\n', i, ...
-            history.r_norm(i), history.eps_pri(i), ...
-            history.s_norm(i), history.eps_dual(i), history.objval(i));
-    end
-
-    if (history.r_norm(i) < history.eps_pri(i) && ...
[…]

### 2018-05-13 StochasticOCSC/batchCSC/lassoFFT.m

@@ -1,160 +1,0 @@
-function [ z, d_Z, Dz, obj ] = lassoFFT(b, z, d_Z, d, kernel_size, lambda_residual, ...
-    lambda_prior, max_it_z, tol )
-       
-    %Timing
-    tstart = tic;
-
-    d = reshape( d, kernel_size );
-    psf_s = kernel_size(1);
-    k = kernel_size(3);
-    n = size(b,3);
-                
-    %PSF estimation
-    psf_radius = floor( psf_s/2 );
-    size_x = [size(b,1) + 2*psf_radius, size(b,2) + 2*psf_radius, n];
-    size_z = [size_x(1), size_x(2), k, n];
-    
-    objective = @(z, dh) objectiveFunction( z, dh, b, lambda_residual, lambda_prior, psf_radius, size_z, size_x );
-    
-    %Prox for masked data
-    [M, Mtb] = precompute_MProx(b, psf_radius); %M is MtM
-    ProxDataMasked = @(u, theta) (Mtb + 1/theta * u ) ./ ( M + 1/theta * ones(size_x) ); 
-    
-    %Prox for sparsity
-    ProxSparse = @(u, theta) max( 0, 1 - theta./ abs(u) ) .* u;
-       
-    %% Pack lambdas and find algorithm params
-    lambda = [lambda_residual, lambda_prior];
-%     gamma_heuristic = 60 * lambda_prior * 1/max(b(:));
-%     gammas_Z = [gamma_heuristic / 1, gamma_heuristic]; %[gamma_heuristic / 500, gamma_heuristic];
-    gammas_Z = [1, 20];
-
-    d = padarray( d, [size_x(1) - kernel_size(1), size_x(2) - kernel_size(2), 0], 0, 'post');
-    d = circshift(d, -[psf_radius, psf_radius, 0] );
-    d_hat = fft2(d);
-    
-    %% Initialize variables for Z
-    varsize_Z = {size_x, size_z};
-    xi_Z = { zeros(varsize_Z{1}), zeros(varsize_Z{2}) };
-    xi_Z_hat = { zeros(varsize_Z{1}), zeros(varsize_Z{2}) };
-    
-    u_Z = { zeros(varsize_Z{1}), zeros(varsize_Z{2}) };
-    v_Z = { zeros(varsize_Z{1}), zeros(varsize_Z{2}) };
-    
-    %Initial iterates
-    if isempty(z)
-        z = zeros(size_z);
-        z_hat = zeros(size_z);
[…]

### 2018-05-13 StochasticOCSC/batchCSC/sparseReconstruction.m

@@ -1,170 +1,0 @@
-function [ z, res] = sparseReconstruction(b, kernels , mask, ...
-                    lambda_residual, lambda_prior, ...
-                    max_it, tol, ...
-                    x_orig, verbose)
-                
-    %Kernel matrix
-    kmat = kernels;             
-    
-    %Precompute spectra for H (assumed to be convolutional)
-    psf_radius = floor( [size(kmat,1)/2, size(kmat,2)/2] );
-    size_x = [size(b,1) + 2*psf_radius(1), size(b,2) + 2*psf_radius(2)];
-    [dhat, dhat_flat, dhatTdhat_flat] = precompute_H_hat(kmat, size_x);
-    dhatT_flat = conj(dhat_flat.');
-    
-    %Size of z is now the padded array
-    size_z = [size_x(1), size_x(2), size(kmat, 3)];
-    
-    % Objective
-    objective = @(v) objectiveFunction( v, dhat, b, mask, lambda_residual, lambda_prior, psf_radius );
-    
-    %Proximal terms
-    conv_term = @(xi_hat, gammas) solve_conv_term(dhat_flat, dhatT_flat, dhatTdhat_flat, xi_hat, gammas, size_z);
-    
-    %Prox for masked data
-    [M, Mtb] = precompute_MProx(b, mask, psf_radius); %M is MtM
-    ProxDataMasked = @(u, theta) (Mtb + 1/theta * u ) ./ ( M + 1/theta * ones(size_x) ); 
-    
-    %Prox for sparsity
-    ProxSparse = @(u, theta) max( 0, 1 - theta./ abs(u) ) .* u;
-    
-    %Pack lambdas and find algorithm params
-    lambda = [lambda_residual, lambda_prior];
-    gamma_heuristic = 60 * lambda_prior * 1/max(b(:));
-    gamma = [gamma_heuristic/100, gamma_heuristic];
-    %gamma = [gamma_heuristic / 100 , gamma_heuristic];
-    
-    %Initialize variables
-    varsize = {size_x, size_z};
-    xi = { zeros(varsize{1}), zeros(varsize{2}) };
-    xi_hat = { zeros(varsize{1}), zeros(varsize{2}) };
-    
-    u = { zeros(varsize{1}), zeros(varsize{2}) };
-    d = { zeros(varsize{1}), zeros(varsize{2}) };
[…]

### 2018-05-13 StochasticOCSC/batchCSC/test.m

@@ -1,211 +1,0 @@
-r%%%%%%%%%%%%%%%%%% 3X3 %%%%%%%%%%%%%%%%%%%% 
-B = repmat((3:-1:1),[6 1])
-A = full(spdiags(B, -1:1, 6,6))
-M1 = kron( spdiags(ones(6,1), 1, 6, 6), A)
-
-B = repmat((6:-1:4),[6 1])
-A = full(spdiags(B, -1:1, 6,6))
-M2 = kron( spdiags(ones(6,1), 0, 6, 6), A)
-
-B = repmat((9:-1:7),[6 1])
-A = full(spdiags(B, -1:1, 6,6))
-M3 = kron( spdiags(ones(6,1), -1, 6, 6), A)
-
-full(M1+M2+M3);
-
-%%%%%%%%%%%%%%%%% nXn %%%%%%%%%%%%%%%%%%%%
-k=5, n=10;
-M = cell(k,1);
-for i=1:k
-    tmp_M = repmat( k*i:-1:(k*(i-1)+1), [n 1] );
-    tmp_M = spdiags(tmp_M, -floor(k/2):floor(k/2), n, n);
-    M{i} = kron( spdiags(ones(n,1), ceil(k/2)-i, n, n), tmp_M);
-end
-
-full_M = M{1};
-for i=2:k
-full_M = full_M + M{i};
-end
-
-%%%%%%%%%%%%%%% general generating D %%%%%%%%%%%%%%%%%%
-z = reshape( PSF{1}(:,:,1), 1, [] );
-k = length( PSF{1}(:,1,1) );
-n = 10;
-
-for i=1:k
-    tmp_M = repmat( z( k*i:-1:(k*(i-1)+1) ), [n 1] );
-    tmp_M = spdiags(tmp_M, -floor(k/2):floor(k/2), n, n);
-    M{i} = kron( spdiags(ones(n,1), ceil(k/2)-i, n, n), tmp_M);
-end
-full_M = M{1};
-for i=2:k
-full_M = full_M + M{i};
-end
-
-%%%%%%%%%%%%%%% general generating Z %%%%%%%%%%%%%%%%%%
-k = 11;
-n = 100;
-
-for i=1:n
-    tmp_M = repmat( ones(k,1), [1 n] );
-    tmp_M = spdiags(tmp_M, floor((k-1)/2)-n+1:floor((k-1)/2), n, k);
[…]

### 2018-05-13 StochasticOCSC/image_helpers/CreateImages.m

@@ -1,725 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This takes all images from the input folder, converts them to the desired
-% colorspace, removes mean/divides by standard deviations (if desired), and
-% constrast normalizes the image (if desired). If the images are of different
-% sizes, then it will padd them with zeros (after contrast normalizing) to make
-% them square (assumes that they all images have the same maximum dimension).
-% Note that some of the whitening/contrast normalization features are not
-% fully tested for datasets where the images are of variable size so please
-% use with caution in that case. For best result, resize all the images to the
-% same dimensions beforehand.
-%
-% @file
-% @author Matthew Zeiler
-% @date Mar 11, 2010
-%
-% @image_file @copybrief CreateImages.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief CreateImages.m
-%
-% @param imgs_path either 1) a path to a folder contain only image files (or other folders
-% which will be ignored), 2) a variable with the images as xdim x ydim x
-% num_colors x num_images size , 3) a path to a file that contains a variable
-% called I that has images as xdim x ydim x num_colors x num_images, or 4)
-% a path to a folder containing a single .mat file containing a variable called
-% I that has images as xdim x ydim x num_colors x num_images.
-% @param CONTRAST_NORMALIZE [optional] binary value indicating whether to contrast
-% normalize or whiten the images. Defaults to local contrast normalization ('local_cn').
-% Available types are: 'none','local_cn','laplacian_cn','box_cn','PCA_whitening',
-% 'ZCA_image_whitening','ZCA_patch_whitening',and 'inv_f_whitening'
-% @param ZERO_MEAN [optional] binary value indicating whether to subtract the mean and divides by standard deviation (current
-% commented out in the code). Defuaults to 1.
[…]

### 2018-05-13 StochasticOCSC/image_helpers/CreateImagesList.m

@@ -1,703 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This takes all images from the input folder, converts them to the desired
-% colorspace, removes mean/divides by standard deviations (if desired), and
-% constrast normalizes the image (if desired). If the images are of different
-% sizes, then it will padd them with zeros (after contrast normalizing) to make
-% them square (assumes that they all images have the same maximum dimension).
-% Note that some of the whitening/contrast normalization features are not
-% fully tested for datasets where the images are of variable size so please
-% use with caution in that case. For best result, resize all the images to the
-% same dimensions beforehand.
-%
-% @file
-% @author Matthew Zeiler
-% @date Mar 11, 2010
-%
-% @image_file @copybrief CreateImages.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief CreateImages.m
-%
-% @param imgs_path either 1) a path to a folder contain only image files (or other folders
-% which will be ignored), 2) a variable with the images as xdim x ydim x
-% num_colors x num_images size , 3) a path to a file that contains a variable
-% called I that has images as xdim x ydim x num_colors x num_images, or 4)
-% a path to a folder containing a single .mat file containing a variable called
-% I that has images as xdim x ydim x num_colors x num_images.
-% @param CONTRAST_NORMALIZE [optional] binary value indicating whether to contrast
-% normalize or whiten the images. Defaults to local contrast normalization ('local_cn').
-% Available types are: 'none','local_cn','laplacian_cn','box_cn','PCA_whitening',
-% 'ZCA_image_whitening','ZCA_patch_whitening',and 'inv_f_whitening'
-% @param ZERO_MEAN [optional] binary value indicating whether to subtract the mean and divides by standard deviation (current
-% commented out in the code). Defuaults to 1.
[…]

### 2018-05-13 StochasticOCSC/image_helpers/check_imgs_path.m

@@ -1,64 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This is a helper function to check that there are valid image files or
-% a .mat in the input path that can be used by CreateImages.m
-%
-% @file
-% @author Matthew Zeiler
-% @date Jun 28, 2011
-%
-% @image_file @copybrief check_imgs_path.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief check_imgs_path.m
-%
-% @param path the path to check
-%
-% @retval valid 1 if the path is valid and 0 if it is no good.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [valid] = check_imgs_path(path)
-
-
-if(strcmp(path(end),'/')==0)
-    path = [path '/'];
-end
-
-valid = 1;
-
-% Make sure the path is a string to continue the checks, otherwise it's fine as a variable.
-if(ischar(path))
-    % As a string it has to be a file or a directory
-    if(~exist(path,'file') || ~exist(path,'dir'))
-        fprintf('Image Path is not a directory or a file\n');
-        valid = 0;
-        return;
-    end
-    
-    
-    % Cell array listing all files and paths.
-    subdir = dir(path);
-    [blah,files] = split_folders_files(subdir);
-    % Empty directory
-    if(exist(path,'dir') && length(files)==0)
-        fprintf('No files in Image directory\n');
-        valid = 0;
-        return;
-    end        
-    
-    if(length(files)==1)% Can be a single image in the directory or a .mat file.
-        if(strcmp(files(1).name(end-3:end),'.mat'))
-            valid = 1; % okay
-            return;
-        else % make sure it is an image
-            try                
-                imread([path files(1).name]);
-            catch
-                fprintf('There is no single .mat file in the directory or the single file is not images.\n');
-                valid = 0; % Not an image
-                return;
-            end
-        end
-    end                    
-else
-    valid = 1;
-end

### 2018-05-13 StochasticOCSC/image_helpers/contrast_normalization/inv_f_dewhiten.m

@@ -1,62 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% The function to dewhiten an image with 1/f whitening.
-%
-% @file
-% @author Matthew Zeiler
-% @date Jun 28, 2010
-%
-% @image_file @copybrief inv_f_dewhiten.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief inf_f_dewhiten.m
-%
-% @param img the image to dewhiten.
-% @param filt the filter to 
-%
-% @retval dewhiten_img the whitened image.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [dewhiten_img] = inv_f_dewhiten(img,filt)
-
-  
-  [imx,imy,imc,M] = size(img);
-  %N=image_size;
-  %M=num_images;
-
-  if nargin==1
-    WHITEN_POWER = 4;
-    WHITEN_SCALE = 0.4;
-    EPSILON = 1e-3;
-    [fx fy]=meshgrid(-imy/2:imy/2-1,-imx/2:imx/2-1);
-    rho=sqrt(fx.*fx+fy.*fy);
-    f_0=WHITEN_SCALE*mean([imx,imy]);
-    filt=rho.*exp(-(rho/f_0).^WHITEN_POWER) + EPSILON;
-  end
-  
-%   img = img(2:end-1,2:end-1,:,:);
-%   filt = filt(2:end-1,2:end-1,:,:);
-  
-    dewhiten_img = zeros(size(img));
-
-
-  for i=1:M
-    for c=1:imc
-      If=fft2(img(:,:,c,i));
-      imagew=real(ifft2(If./fftshift(filt)));
-      dewhiten_img(:,:,c,i) = imagew;
-    end
-
-%    If=fftn(img(:,:,:,i));
-%     imagew = real(ifftn(If./fftshift(filt)));
[…]

### 2018-05-13 StochasticOCSC/image_helpers/contrast_normalization/inv_f_whiten.m

@@ -1,100 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% The function to whiten an image with 1/f whitening.
-%
-% @file
-% @author Matthew Zeiler
-% @date Jun 28, 2010
-%
-% @image_file @copybrief inv_f_whiten.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief inf_f_whiten.m
-%
-% @param img the image to whiten.
-%
-% @retval whiten_img the whitened image.
-% @retval filt the corresponding dwhitening filter that was applied convolutionally.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [whiten_img,filt] = inv_f_whiten(img)
-
-    img = double(img);
-
-  WHITEN_POWER = 4
-  WHITEN_SCALE = 0.4
-  EPSILON = 1e-6
-  
-  [imx1,imy1,imc1,M1] = size(img);
-  %N=image_size;
-  %M=num_images;
-  
-%   
-%   
-%   
-% ly = imy1;
-% lx = imx1;
-% sy = imy1;
-% sx = imx1;
-% 
-% %% These values are the index of the small mtx that falls on the
-% %% border pixel of the large matrix when computing the first
-% %% convolution response sample:
-% ctr=1;
-% sy2 = floor((sy+ctr+1)/2);
-% sx2 = floor((sx+ctr+1)/2);
-% 
-% % pad:
-% img = [ ...
-%     img(ly-sy+sy2+1:ly,lx-sx+sx2+1:lx,:,:),...
-%     img(ly-sy+sy2+1:ly,:,:,:), ...
-% 	img(ly-sy+sy2+1:ly,1:sx2-1,:,:); ...
-%     img(:,lx-sx+sx2+1:lx,:,:), ...
-%     img, ...
[…]

### 2018-05-13 StochasticOCSC/image_helpers/contrast_normalization/region_zca.m

@@ -1,165 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This functin is used to whiten an image with patch based ZCA whitening that is applied
-% convolutionally to the image.
-%
-% @file
-% @author Matthew Zeiler
-% @date Jun 28, 2010
-%
-% @image_file @copybrief region_zca.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief region_zca.m
-%
-% @param img the image to whiten.
-%
-% @retval w_filt the whitening filter to apply convolutionally.
-% @retval d_filt the corresponding de-whitening filter to apply convolutionally.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [w_filt,d_filt] = region_zca(img)
-
-NUM_PATCHES = 1;
-PATCH_SIZE = 19;
-BORDER_SIZE = 4;
-[imx,imy,imc,M] = size(img);
-
-count = 0;
-w_filt = zeros(PATCH_SIZE,PATCH_SIZE,3,3);
-d_filt = zeros(PATCH_SIZE,PATCH_SIZE,3,3);
-
-for i=1:NUM_PATCHES
-    i
-    %% choose start coords of patch
-    r = floor(rand(1,2).*([imy,imx]-PATCH_SIZE)+1);
-    
-    %% grab patches & compute covariance matrix
-    p = img(r(1):r(1)+PATCH_SIZE-1,r(2):r(2)+PATCH_SIZE-1,:,:);
-    m = reshape(p,[3*PATCH_SIZE^2,M]);
-    mu = mean(m,2);
-    cm = double(m) - mu*ones(1,M);
-    CC = cm * cm';
-    
-    %[u,s,v] = svd(CC);
-    [u,s] = eig(CC);
-    
-    q = diag(s);
-    qi = find(q>0);
[…]

### 2018-05-13 StochasticOCSC/image_helpers/contrast_normalization/unwhiten.m

@@ -1,39 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This function is to unwhiten a whitened image in the fourier domain.
-%
-% @file
-% @author Matthew Zeiler
-% @date Jun 28, 2010
-%
-% @image_file @copybrief unwhiten.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% clear all
-%   N=image_size;
-% N=100;
-%   M=num_images;
-%   M=1;
-
-%   [fx fy]=meshgrid(-N/2:N/2-1,-N/2:N/2-1);
-%   rho=sqrt(fx.*fx+fy.*fy);
-%   f_0=0.4*N;
-%   filt=rho.*exp(-(rho/f_0).^4);
-
-for i=1:M
-    imageAll=IMAGES(:,:,:,i);  % you will need to provide get_image
-    for plane=1:3
-        image=imageAll(:,:,plane);
-        If=fft2(image);
-        imagew=real(ifftshift(ifft2(If./filt)));
-        tempIM(:,plane) = reshape(imagew,N^2,1);
-    end
-    IMAGES(:,:,:,i)=reshape(tempIM,N,N,3,1);
-    
-end
-
-%   IMAGES=sqrt(0.1)*IMAGES/sqrt(mean(var(IMAGES)));
-
-IMAGES = reshape(IMAGES,N,N,3,M);
-
-figure(2)
-clf;
-imshow(IMAGES)

### 2018-05-13 StochasticOCSC/image_helpers/contrast_normalization/whiten.m

@@ -1,44 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% This functino is to whiten an image in the fourier domain.
-%
-% @file
-% @author Matthew Zeiler
-% @date Jun 28, 2010
-%
-% @image_file @copybrief whiten.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-clear all
-%   N=image_size;
-N=100;
-%   M=num_images;
-M=1;
-
-[fx fy]=meshgrid(-N/2:N/2-1,-N/2:N/2-1);
-rho=sqrt(fx.*fx+fy.*fy);
-f_0=0.4*N;
-filt=rho.*exp(-(rho/f_0).^4);
-
-for i=1:M
-    imageAll=double(imread('1.jpg'));  % you will need to provide get_image
-    for plane=1:3
-        image=imageAll(:,:,plane);
-        If=fft2(image);
-        imagew=real(ifft2(If.*fftshift(filt)));
-        tempIM(:,plane) = reshape(imagew,N^2,1);
-        %                 tempIM(:,plane)=sqrt(1)*tempIM(:,plane)/sqrt(mean(var(tempIM(:,plane))));
-        
-    end
-    
-    IMAGES(:,i)=reshape(tempIM,N^2*3,1);
-    
-end
-
-IMAGES=sqrt(0.1)*IMAGES/sqrt(mean(var(IMAGES)));
-
-IMAGES = reshape(IMAGES,N,N,3,M);
-
-figure(1)
-clf;
-% sdispims(IMAGES);
-imshow(IMAGES);
-unwhiten

### 2018-05-13 StochasticOCSC/image_helpers/rconv2.m

@@ -1,59 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% Convolution of two matrices, with boundaries handled via reflection
-% about the edge pixels.  Result will be of size of LARGER matrix.
-%
-% Further adapted for speed by Matthew Zeiler.
-%
-% @file
-% @author Matthew Zeiler
-% @author Eero Simonscelli
-% @date Feb 13, 2010
-%
-% @ipp_file @copybrief make_noz.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief make_noz.m
-% @param large the image you want to convolve over.
-% @param small the filter you want to convolve with.
-%
-% @retval c the convolved image.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function c = rconv2(large,small)
-
-ctr = 0;
-
-
-% if (( size(a,1) >= size(b,1) ) & ( size(a,2) >= size(b,2) ))
-%     large = a; small = b;
-% elseif  (( size(a,1) <= size(b,1) ) & ( size(a,2) <= size(b,2) ))
-%     large = b; small = a;
-% else
-%   error('one arg must be larger than the other in both dimensions!');
-% end
-
-ly = size(large,1);
-lx = size(large,2);
-sy = size(small,1);
-sx = size(small,2);
-
-%% These values are one less than the index of the small mtx that falls on 
-%% the border pixel of the large matrix when computing the first 
-%% convolution response sample:
-sy2 = floor((sy+ctr-1)/2);
-sx2 = floor((sx+ctr-1)/2);
-
-% pad with reflected copies
-clarge = [ 
-    large(sy-sy2:-1:2,sx-sx2:-1:2), large(sy-sy2:-1:2,:), ...
[…]

### 2018-05-13 StochasticOCSC/image_helpers/split_folders_files.m

@@ -1,41 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% Return two struct arrays of just the folers and just the files of the input
-% struct array.
-%
-% @file
-% @author Matthew Zeiler
-% @date Mar 11, 2010
-%
-% @fileman_file @copybrief split_folders_files.m
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%>
-% @copybrief split_folders_files.m
-%
-% @param input a struct array of both files and folders combined.
-% @retval folders a struct array of the folders
-% @retval files a struct array of the files
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [folders,files] = split_folders_files(input)
-
-% 
-% folders = input(find(~cellfun(@iszero,{input(:).isdir})));
-% 
-% files = input(find(cellfun(@iszero,{input(:).isdir})));
-% 
-% 
-%     function [result] = iszero(input)
-%         
-%         if(input==0)
-%             result = 1;
-%         else
-%             result = 0;
-%         end
-%     end
-
-B = struct2cell(input); 
-dirs = cell2mat(B(4,:)); 
-folders = input(logical(dirs)); 
-files = input(~logical(dirs));
-
-end

### 2018-05-13 StochasticOCSC/onlineCSC/OnlineStochasticCSC.m

@@ -1,138 +1,0 @@
-%% first code for CSC in spatial domain
-function [ d, z, obj ]  = OnlineStochasticCSC(b, test_b, d_ind, z_ind, kernel_size, lambda)
-
-    k = kernel_size(1);           
-    num_kernel  = kernel_size(end);
-
-    n = size(b,1);
-    num_image = size(b,3);
-    
-    b = reshape(b, [], num_image);
-
-    d = randn(k, k, num_kernel);
-    for i=1:num_kernel
-       d(:,:,i) =  d(:,:,i) ./ max( norm( d(:,:,i), 'fro' ), 1);
-    end
-    back_d = d(:);
-    d = back_d;
-    
-    %% parameters
-    outer_ite = 35; % num_image;
-    max_it_z = 20;
-    max_it_d = 10;
-    
-    batch_size = 10;    % change in batch mode
-    total_time = 0;
-    rho_d = 10;
-    rho_z = 1.5;
-    hit_rate = 0.1;    % probability for choosing one specific code 
-    gamma = 1;       % forget factor
-    
-    u_d     = zeros( k*k*num_kernel, 1 );
-    x_hat_d = zeros( k*k*num_kernel, 1 );
-    z       = zeros( n*n*num_kernel, batch_size );
-    
-%     ind = 1:1:n*n*num_kernel;
-%     [ind1_all, ind2_all, v_all] = find( d_ind(:,ind) );
-
-%     sequence = randperm(outer_ite*batch_size);
-    sequence = [1:350];
-    test_ite = 0;
-    
-    for ite = 1:outer_ite
-        %% test set objective
-%          if ite==1 || ite==outer_ite || mod(log2(ite),1) == 0
-%           test_ite = test_ite + 1;
-%           [z_test, d_Z, Dz, obj(test_ite)] = lassoFFT(test_b, []      ,...
-%                   [] , d, kernel_size, 1, 1, 50, 1e-3 );
-%            fprintf( 'test objective: %10.4f; non-zero elements: %6d, %6d \n', ...
-%              obj(test_ite), size( find( abs(z_test(:))>0.01),1 ),size( find( abs(z_test(:))>0.1),1 ) );
-%            if ite>30
-%               save(sprintf('filter/d%4d_mini%2d_online%3d_forget%1.1f_P%1.1f_lambda%1.1f_rho%2.1f_ite%2d_rho_%2.1f_%2d.mat',...
[…]

### 2018-05-13 StochasticOCSC/onlineCSC/conj_grad.m

@@ -1,66 +1,0 @@
-function x = conj_grad(b, A, x, max_it, tol, choice)
-    
-    if choice == 1
-        % calculate residual vector r assoiated with x
-        r = b - conv2(x,A,'same');
-        p = r;
-        rsold = r'*r;         
-        for i=1:max_it
-            Ap = conv2(p, A, 'same' );
-            % compute the scalar alpha
-            alpha = rsold / (p'*Ap);
-            % update approximation
-            x = x + alpha*p;
-            r = r - alpha*Ap;
-            rsnew = r'*r;
-            % check convergence
-            if abs(rsnew-rsold)<tol
-                break;
-            end
-            p = r+(rsnew/rsold)*p;
-            rsold = rsnew;
-        end
-        
-    elseif choice == 2 
-        r = b - A(x);
-        p = r;
-        rsold = r'*r;
-%         absold = 1e20;
-        for i=1:max_it
-            Ap = A(p);
-            alpha = rsold/(p'*Ap);
-            x = x + alpha*p;
-            r = r - alpha*Ap;
-            rsnew = r'*r;
-%             absnew = abs(rsnew-rsold);
-            if abs(rsnew-rsold)<tol
-                break;
-            end
-%             absold = absnew;
-            p = r+(rsnew/rsold)*p;
-            rsold = rsnew;
-        end
-
-        
-    elseif choice == 3 
-        r = b - A(x);
-        p = r;
-        rsold = sum( r.*r, 1) ;
-%         absold = 1e20;
-        for i=1:max_it
-            Ap = A(p);
-            alpha = rsold ./ sum(p.*Ap, 1);
-            x = x + repmat(alpha, size(p,1),1 ).*p;
-            r = r - repmat(alpha, size(p,1),1 ).*Ap;
-            rsnew = sum(r.*r,1);
-%             absnew = abs(rsnew-rsold);
-            if sum( abs(rsnew-rsold) )<tol
-                break;
-            end
-%             absold = absnew;
-            p = r+ repmat(rsnew./rsold, size(p,1),1 ).*p;
-            rsold = rsnew;
-        end
-    end
-        
-end

### 2018-05-13 StochasticOCSC/onlineCSC/lasso.m

@@ -1,122 +1,0 @@
-function [z, x_hat, u, obj, k] = lasso(A, b, z, x_hat_z, u_z, ...
-    lambda, rho, alpha, MAX_ITER, option, QUIET)
-t_start = tic;
-
-if nargin < 11
-    QUIET    = 0;
-end
-% MAX_ITER = 10;
-ABSTOL   = 1e-4;
-RELTOL   = 1e-2;
-
-[p, n] = size(A);
-[~, m] = size(b);
-
-% save a matrix-vector multiply
-Atb = A'*b;
-
-x = zeros(n,m);
-if isempty(z)
-    z = zeros(n,m);
-end
-
-if isempty(x_hat_z)
-    x_hat_z = zeros(n,m);
-end
-x_hat = x_hat_z;
-
-if isempty(u_z)
-    u_z = zeros(n,m);
-end
-u = u_z;
-
-% cache the factorization
-if option == 1 || isempty( option )
-    [L U] = factor(A, rho);
-elseif option == 2
-    A_cal = @(p) A'*(A*p) + rho.*p;
-end
-
-if ~QUIET
-    fprintf('%3s\t%10s\t%10s\t%10s\t%10s\t%10s\n', 'iter', ...
-      'r norm', 'eps pri', 's norm', 'eps dual', 'objective');
-end
-
-for k = 1:MAX_ITER
-
-    % x-update
-    q = Atb + rho*(z - u);    % temporary value
-
-    for i=1:m
-        if option == 1 || isempty( option )  
-            if( p >= n )    % if skinny
-               x(:,i) = U \ (L \ q(:,i));
-            else            % if fat
-               x(:,i) = q(:,i)/rho - (A'*(U \ ( L \ (A*q(:,i)) )))/rho^2;
-            end
-        elseif option == 2
-            x(:,i) = conj_grad(q(:,i), A_cal, x_hat(:,i), 100, 1e-5, 2);
-        end
-    end
-
-    % faster than iteration
-%      x = conj_grad(q, A_cal, x_hat, 100, 1e-4, 3);
-   
-    % z-update with relaxation
-    zold = z;
-    x_hat = alpha*x + (1 - alpha)*zold;
-    z = shrinkage(x_hat + u, lambda/rho);
-    % u-update
-    u = u + (x_hat - z);
-
-    % diagnostics, reporting, termination checks
-    history.objval(k)  = objective(A, b, lambda, x, z);
-
[…]

### 2018-05-13 StochasticOCSC/onlineCSC/maskReconstruction.m

@@ -1,61 +1,0 @@
-%% test
-% [b] = CreateImages('../../proposed_CSC/imageNet/testing',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-CONTRAST_NORMALIZE = 'local_cn'; 
-% CONTRAST_NORMALIZE = 'none'; 
-ZERO_MEAN = 1;   
-COLOR_IMAGES = 'gray'; 
-% [b] = CreateImagesJinhui('../../proposed_CSC/imageNet/testing',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-[b] = CreateImages('../../CCSC_code_ICCV2017-master/CCSC_code_ICCV2017-master/2D/Poisson_deconv/dataset_norm/1',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES);
-test_b = reshape(b, size(b,1), size(b,2), [] );
-signal = test_b(:,:,1);
-
-D = constructDicIndex( kernel_size, size(test_b,1),size(test_b,2), d(:) );
-
-
-%% Reconstruction from sparse data
-
-%Sampling matrix
-MtM = zeros(size(signal));
-%MtM(1:2:end, 1:2:end) = 1;
-MtM(rand(size(MtM)) < 0.5 ) = 1;
-
-signal_sparse = signal;
-signal_sparse( ~MtM ) = NaN;
-% signal_fill = fillmiss(signal_sparse);
-% offset = signal_fill - localContrast( signal_fill, ZERO_MEAN );
-
-signal_sparse( ~MtM ) = min(signal_sparse(:));
-
-ind = find( MtM(:) );
-M = sparse( 1:numel(ind), ind, 1,  numel(ind),numel(MtM));
-
-% M = spdiags(MtM(:), 0, numel(MtM),numel(MtM));
-
-% [z, ~] = lasso( M*D, M*(signal_sparse(:)-offset(:)), [], [], [], 0.1, 3, 1.8, 50, 1, 0); 
-% sig_rec = reshape( D*z, size(signal) ) + offset;
-% MD = M*D;
-% [z, ~] = lasso( MD, M*signal_sparse(:), [], [], [], 0.1, 3, 1.8, 50, 1, 0); 
-% sig_rec = reshape( D*z, size(signal) );
-
-tic();
-[z, sig_rec] = sparseReconstruction(signal_sparse,...
[…]

### 2018-05-13 StochasticOCSC/onlineCSC/onlineStoCSC.m

@@ -1,42 +1,0 @@
-addpath('../image_helpers');
-CONTRAST_NORMALIZE = 'local_cn'; 
-ZERO_MEAN = 1;   
-COLOR_IMAGES = 'gray'; 
-% read training and testing images
-[b] = CreateImagesJinhui('../../proposed_CSC/imageNet/training',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-train_b = reshape(b, size(b,1), size(b,2), [] );
-
-[b] = CreateImagesJinhui('../../proposed_CSC/imageNet/testing',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-test_b = reshape(b, size(b,1), size(b,2), [] );
-
-%% Define the parameters
-kernel_size = [11, 11, 225];
-lambda = 0.15;
-
-d_ind = constructDicIndex(  kernel_size, size(train_b,1), size(train_b,2) );
-z_ind = constructCodeIndex( kernel_size, size(train_b,1) );
-%% online stochastic CSC
-t_start = tic;
-% [ d, z, obj ]  = OnlineStochasticCSC(train_b, test_b, d_ind, kernel_size, lambda);
-[ d, z, ~ ]  = OnlineStochasticCSC(train_b, [], d_ind, z_ind, kernel_size, lambda);
-toc(t_start);
-
-%% visualize dictionary
-s = 15;
-max_d = max(d(:)); min_d = min(d(:));
-dic = reshape( d, 11,11,s*s );
-figure
-sub_dic = cell(size(dic,3),1 );
-for i=1:size(dic,3)
-    sub_dic{i} = dic( :,:,i );
-end
-for i=1:size(dic,3)
-    subplot('Position',[(mod(i-1,s))/s 1-(ceil(i/s))/s 1/s-0.001 1/s-0.001]);
-    imshow( sub_dic{i}, [min_d max_d], 'init', 'fit' );
-end
-
-%% Save
-save(sprintf('d_online10_100_01.mat'), 'd_online10');
-save(sprintf('d_online10_225_01.mat'), 'd_online10_225');
-save(sprintf('d_online50_100_01.mat'), 'd_online50_100');
-save(sprintf('d_online50_225_01.mat'), 'd_online50_225');

### 2018-05-13 StochasticOCSC/onlineCSC/test.m

@@ -1,64 +1,0 @@
-x = [ 50 70 90 110 130 150 170 190];
-z1 = 1.0e+04 *[ 1.5084    1.3440    1.2855    1.2529    1.2334    1.2211 ...
-    1.2129    1.2069    1.2024    1.1986];
-z2 = 1.0e+04 *[ 1.5237    1.3474    1.2961    1.2709    1.2581    1.2503 ...
-    1.2468    1.2430    1.2382    1.2374];
-z3 = 1.0e+04 *[ 1.5942    1.3897    1.3285    1.2949    1.2783    1.2650 ...
-    1.2596    1.2561    1.2525    1.2504];
-z4 = 1.0e+04 *[ 1.6369    1.4431    1.3863    1.3632    1.3476    1.3336 ...
-    1.3262    1.3213    1.3175    1.3177];
-z5 = 1.0e+04 *[ 1.7171    1.5316    1.4932    1.4697    1.4537    1.4431 ...
-    1.4363    1.4327    1.4263    1.4224];
-z6 = 1.0e+06 *[ 3.4200    0.9877    0.2242    0.0461    0.0225    0.0186 ...
-    0.0201    0.0160    0.0141    0.0133  0.0130    0.0127    0.0127];
-
-figure
-plot( 1:10, z1, '--o','MarkerSize', 12, 'LineWidth',2 );
-hold on
-plot( 1:10, z2, '--d','MarkerSize', 12, 'LineWidth',2);
-hold on
-plot( 1:10, z3, '--^','MarkerSize', 12, 'LineWidth',2 );
-hold on
-plot( 1:10, z4, '--*','MarkerSize', 12, 'LineWidth',2 );
-hold on
-plot( 1:10, z5, '--+','MarkerSize', 12, 'LineWidth',2 );
-hold on
-plot( 1:10, z6(1:10), '--p','MarkerSize', 12, 'LineWidth',2 );
-legend('P=1', 'P=0.5', 'P=0.2', 'P=0.1', 'P=0.05', 'Heide et al' );
-
-set(gca, 'YScale', 'log')
-set(gca, 'XScale', 'log')
-
-set(gca,'fontsize',32)
-set(gca, 'XLim', [10 1300]);
-% set(gca,'xtick',[50 80 110]);
-set(gca, 'YLim', [1.1e4 3e4]);
[…]

### 2018-05-15 Stochastic Convolutional Sparse Coding/CSCmodel.tex
update

@@
 \section{Convolutional Sparse Coding (CSC)}
-Specifically, the CSC problem is trying to minimize
+Specifically, the CSC problem has the form
 \begin{equation}
@@
     \minimize{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
-    \subjectto & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in {1,...K},
+    \text{subjec to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
 \end{split}
 \end{equation}
-where $\signal \in \mathbb{R}^D$ is a D-dimensional signal or a vectorized image~\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary and $\code_k$ is the sparse code associated with that dictionary, and it has the same dimension size as $\signal$.
-$K$ is the number of dictionary filters, and $*$ is the convolution operator.
-The above equations will be applied to all the training images.
+where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a vectorized image\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in \mathbb{R}^D$ is the sparse code associated with that dictionary,  $\lambda>0$ is a sparsity inducing penalty parameter, $K$ is the number of dictionary filters, and $*$ is the convolution operator.
+The above model will be applied to all the training images.
 
 The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
-There exists several common issues regarding to the model and the frequency solvers.
+The model and existing frequency solvers suffer from several issues:
 
 \begin{itemize}
-  \item Though CSC overcomes the independence assumption held in patch-based learning algorithms, far more variables ($K$ times more), as a payback, will be introduced to represent a single image.
-This brings in more severe memory and computational burden.
-  \item The reconstructed sparse codes show that in the case of $K=100$, the majority of the entries (more than $99.5\%$) do not provide valid information to the represented image, which indicates the subproblem for updating $\code$ solves a highly sparse LASSO problem.
+  \item While CSC overcomes the independence assumption held in patch-based learning algorithms, far more variables ($K$ times more) are introduced to represent a single image to compensate for this.
+This creates more severe memory and computational burdens.
+
+  \item We observe through experiments that the vast majority of the entries of the reconstructed sparse codes do not provide useful information about the represented image.
+For $K=100$, 99.5\% entries are not informative.
+This indicates that the subproblem for updating $\code$ solves a highly sparse LASSO problem.
 Transforming the problem into frequency domain imposes restriction on the use of optimization strategies for this very specific problem.
-  \item The prior work shows its efficiency of solving the CSC problem in frequency domain, while this is only applicable for updating $\code$, and it does not hold for updating $\filter$.
-The dictionary filters usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$), while in order to tackle the problem in frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
+
+  \item While prior work shows its efficiency in solving the CSC problem in the frequency domain, this is only applicable for updating $\code$, and does not hold for updating $\filter$.
+The dictionary filters usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$).
+However, in order to tackle the problem in the frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
 \end{itemize}

### 2018-05-15 Stochastic Convolutional Sparse Coding/Conclusion.tex
update

\section{Conclusions}
In this work, we present a novel stochastic subsampling strategy for updating sparse codes and it successfully improves the runtime performance to solve the CSC problem in spatial domain, which applies to both batch mode and online-learning mode, as well as generating effective and proven outcomes. Since the subproblem of updating the codes is a highly sparse Lasso, specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in, which uses coordinate descent and skip unnecessary updates by the method of safe screening. Notice that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies. In addition, we show the capability of the developed online algorithm to learn representative over-complete dictionary from large datasets, and the availability of the dictionary is further verified by the application of image inpainting. It can be foreseen that this capability has widespread applications in the audio and image related tasks, and higher dimensional signal processing.

### 2018-05-15 Stochastic Convolutional Sparse Coding/Results.tex
update

@@
 \section{Results} \label{sec:result}
-\subsection{Sub-Sampling Strategy}
-We first evaluate the convergence and effectiveness of the proposed sub-sampling strategy, and compare it with state-of-the-art frequency solver~\cite{heide2015fast}.
+\subsection{Subsampling Strategy}
+We first evaluate the convergence and effectiveness of the proposed subsampling strategy, and compare it with the state-of-the-art frequency solver~\cite{heide2015fast}.
 The proposed algorithm, with different sub-sampling factors, was tested on the fruit dataset~\cite{zeiler2010deconvolutional} which contains 10 training images in the size of $100 \times 100$.
@@
 Specifically, the more subsampled, the relatively slower convergence and the higher objective will be obtained.
-On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solvers for one iteration.
+On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solver for one iteration.
 We observe that a subsampling rate between $0.1$ and $0.2$ delivers empirically good enough convergence in our settings, as well as achieving at least $3 \times$ speedup.
-It should be clarified that for a better representation, the cropped objectives are plotted after the first iteration, while all of them have the same initial objective.
+In general, the proposed method converges within 10 iterations, while the comparable method requires roughly 13 iterations to reach converge.
 Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
@@
 
-\caption{Left: Convergence comparison between the-state-of-art method\cite{heide2015fast} and the proposed method with different subsampling probability.
+\caption{Left: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling probability.
 Right: Learned filters by the proposed method with $p=0.1$ and the comparable method.
@@
     \\
+    \\
     \resizebox{1\linewidth}{!}{
@@
             \hline
-            PSNR~\cite{heide2015fast} & 25.77 & 24.67 & 24.89 & 23.88 & 24.68 & 25.26  & 24.15 & 25.75 & 22.97 & 26.16 \\
+            PSNR~\cite{heide2015fast} & 29.54 & 28.16 & 29.40 & 29.22 & 28.89 & 29.29 & 28.10  & 29.57 & 27.46 & 30.72 \\
             \hline
-            PSNR ours & \textbf{25.91} & \textbf{24.72} & \textbf{25.21} & \textbf{24.09} & \textbf{25.00} & \textbf{25.36} & \textbf{24.32} & \textbf{25.80} & \textbf{23.24} & \textbf{26.37} \\
+            PSNR ours & \textbf{29.65} & \textbf{28.18} & \textbf{29.52} & \textbf{29.43} & \textbf{28.99} & \textbf{29.38} & \textbf{28.19} & \textbf{29.63} & \textbf{27.62} & \textbf{30.98} \\
             \hline
@@
     \caption{Numerical comparisons of the reconstruction quality obtained from the presented filters and its comparison.
-The reconstructions are performed on $20\%$ randomly observed images, with $\lambda = 0.4$ and $50$ ADMM iterations for both cases.
+The reconstructions are performed on $50\%$ randomly observed images, with $\lambda = 0.4$ and $50$ ADMM iterations for both cases.
 Obtained PSNR values are averaged on 5 trials.
@@
 {\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire dataset cannot be evaluated since each training step only draws one or a few of the data samples.
-Otherwise, we can evaluate the learning process on testing images.
-The loss objectives on testing dataset of the proposed algorithm and prior published online CSC model solved in frequency domain~\citep{liu-2018-first}, with respect to iterations, are shown in Fig.~\ref{fig:onlineSmall}.
-In the same figure, we also keep track of the capability of the updated filters in the learning process to sparsely represent the testing images, which are demonstrated by its PSNR.
+Nevertheless, we can evaluate the learning process on testing images.
+The loss objectives on testing dataset of the proposed online learning algorithm and prior published online CSC model solved in frequency domain~\citep{liu-2018-first}, with respect to iterations, are shown in Fig.~\ref{fig:onlineSmall}.
+In the same figure, we also keep track of the capability of the updated filters in the learning process to sparsely represent the testing images, which are demonstrated by its PSNR with respect to time.
 These two approaches stop at optimum positions with close testing objective values, though, they exhibit slightly different convergence behaviors with respect to iterations.
@@
 
-\caption{Left: Convergence of the test set objectives for the proposed method and its comparison~\cite{liu-2018-first}.
+\caption{Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art approach~\cite{liu-2018-first}.
 Right: Testing PSNR with respect to execution time.
-Our method has the similar outcomes as the comparable method, while it achieves $5 \times$ speedup.
-}
+While the quality of the output is comparable, our method achieves $5 \times$ speedup.
+\peter{Are the colors correct?
+The other method seems to be better!}}
 \label{fig:onlineSmall}
@@
 \end{minipage}
+    \\
+    \\
+    \\
+    \resizebox{1\linewidth}{!}{
+        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
+            \cline{1-11}
+            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+            \hline
+            PSNR by (a) & 29.58 & 28.19 & 29.44 & 29.63 & 28.89 & 29.33 & 28.13  & 30.14 & 27.42 & 30.89 \\
+            \hline
+            PSNR by (b) & 29.63 & 28.22 & 29.57 & 29.90 & 29.12 & 29.59 & 28.05  & 30.17 & 27.53 & 31.08 \\
+            \hline
+            PSNR by (c) & \textbf{30.24} & \textbf{28.34} & \textbf{29.95}  & \textbf{30.30} & \textbf{29.43} & \textbf{29.96} & \textbf{28.24} & \textbf{30.57} & \textbf{27.72} & \textbf{31.67} \\
+            \hline
+        \end{tabular} }
 
-\caption{Filters learned from 1000 images by the proposed method and its comparison.
+\caption{Filters learned from 1000 images by our method and the state of-the-art method~\cite{liu-2018-first}, and their corresponding reconstruction quality.
 (a) The under-complete dictionary ($11 \times 11 \times 100$) learned by~\cite{liu-2018-first}; (b) The under-complete dictionary ($11 \times 11 \times 100$) learned by the proposed method.
 (c) The over-complete dictionary ($11 \times 11 \times 400$) learned by the proposed method.
-These under-complete dictionaries, mainly composed of gabor-like filters, can be seen as a subset of the represented over-complete dictionary, which also contains a number of low contrast image features.}
+These under-complete dictionaries, mainly composed of Gabor-like filters, can be seen as a subset of the represented over-complete dictionary, which also contains a number of low contrast image features.
+\peter{Include these filters in the supplementary, but make them much bigger so that people can see the deltails.}
+}
 \label{fig:overCompleteDic}
@@
 We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.~\ref{fig:overCompleteDic} .
-As a comparison, 100 learned filters by the same algorithm and its comparable approach are also represented for a visual comparison.
-As can be observed, both of the approaches learn visually similar under-complete dictionaries, while the proposed method shows a $5 \times$ speedup over the other.
-Furthermore, the learned over-complete dictionary is composed of the gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
-These additional feature information would play an essential role to better represent the natural images, which can be demonstrated in Fig.~\ref{fig:overCompleteDic}.
+For a visual comparison, 100 learned filters by the same algorithm and its comparable approach are also represented for a visual comparison.
+As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method shows a $5 \times$ speedup over the competitive one.
+Furthermore, the learned over-complete dictionary is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
+These additional feature information would play an essential role to better represent the natural images, which can be demonstrated by the reconstruction quality shown in Fig.~\ref{fig:overCompleteDic}.
 
-There is a bottleneck for under-complete dictionary revealed in the left hand side of fig.~\ref{fig:overComDicAndMinibatch}, that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
-However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement with regard to PSNR to have a sparse representation of the testing images.
-
-{\bfseries Mini-batch.} In practice, the mini-batch strategy would be preferred for a gain of convergence speed, rather than drawing a single sample in each training step.
-This is also a standard extension to stochastic algorithms.
-We denote the mini-batch size as $\eta$.
-In the proposed algorithm, the time complexity for one step dictionary update will not increase linearly with the increase of $\eta$.
-Concretely speaking, updating $\code$ is implemented by Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
-Herein, the complexity for updating $\eta$ $\code$s at once is cheaper than $\eta$ times the complexity of updating one $\code$.
-In addition, the time complexity for updating $\filter$ is not affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
-One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this is not dominant in the runtime.
-The results for various mini-batch sizes are shown in Fig.~\ref{fig:overComDicAndMinibatch}.
-The learned filters are examined on the test set every $2^i$ iterations and the last iteration, where $i=0,1,...$.
-Note that larger $\eta$ will result in less number of iterations to process all 1000 images.
-A larger mini-batch size shows a greater progress for first few training steps, though it takes additional running time and memory.
-Overall, mini-batched updates provides a more runtime efficient learning progress in online-based CSC model, and $\eta=20$ achieves one magnitude speedup to reach a condition with same level convergence.
+We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
+The left hand side of Fig.~\ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
+However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement with regard to PSNR to have a sparse representation of the testing images during the learning process.
+This is also verified by applying these learned dictionaries to the image inpainting applications as discussed above.
 
@@
 \end{figure}
+
+{\bfseries Mini-batching.} In practice, a mini-batching strategy would be preferred in order to gain advantage from modern parallel computing architectures.
+This is also a standard extension to stochastic optimization algorithms \cite{Takac2013, PCDM, SCSG}.
+We denote the mini-batch size as $\eta$.
+In the proposed algorithm, the time complexity for one step dictionary update will not increase linearly with the increase of $\eta$.
+Concretely speaking, updating $\code$ is implemented by Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
+Herein, the complexity for doing updating $\code$ $\eta$ times all together is cheaper than $\eta$ times the complexity of updating one $\code$.
+In addition, the time complexity for updating $\filter$ is not affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
+One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this is not dominant in the runtime.
+The learned filters are examined on the test sets every $2^i$ iterations and the last iteration, where $i=0,1,...$.
+Note that larger $\eta$ will result in less number of iterations to process all 1000 images.
+The results for various mini-batch sizes are shown in Fig.~\ref{fig:overComDicAndMinibatch}.
+A larger mini-batch size shows a greater progress for first few training steps, though it takes additional running time and memory.
+Overall, mini-batched updates provides a more runtime efficient learning progress in online-based CSC model, and in the test examples, $\eta=20$ achieves one magnitude speedup over $\eta=1$ to reach a condition with the same level convergence.

### 2018-05-15 Stochastic Convolutional Sparse Coding/SCSCmodel.tex
update

@@
 \begin{equation} \label{eq:updatingCode}
-    \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^T)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
+    \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^\top)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
 \end{equation}
-where $\Filter = [\Filter_1 ...
-\Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1^T ...
-\code_K^T]^T \in \mathbb{R}^{DK \times 1}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
-$\mask$ is a randomized subsampling diagonal matrix with $1$ on the entries corresponding to the sampled sparse codes, performing the function of choosing a random portion of the sparse codes for reconstruction.
+where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
+Matrix $\mask$ is a random diagonal subsampling  matrix with ones on the entries corresponding to the sampled sparse codes and zeros elswhere, performing the function of choosing a random portion of the sparse codes for reconstruction.
 Herein, the $\code$-subproblem only computes the sparse codes in the chosen positions.
 Due to the introduced subsampling matrix, the convolution operator will not hold, hence it cannot be solved in the frequency domain.
-This subsampling strategy is akin to the dropout technique~\cite{srivastava2014dropout}, which has been widely used to prevent overfitting when training deep neural networks.
-However, different from dropout that generally needs more time to train a neural network than standard approaches, with a good selection of subsampling probability $p$, the proposed method shows less per iteration running time and faster convergence than state-of-the-arts (see section~\ref{sec:result}).
+This stochastic subsampling strategy is akin to the dropout technique~\cite{srivastava2014dropout}, which has been widely used to prevent overfitting when training deep neural networks.
+However, different from dropout that generally needs more time to train a neural network than standard approaches, with a good selection of subsampling probability $p$, the proposed method shows less per iteration running time and faster convergence than state-of-the-arts (see Section~\ref{sec:result}).
 
@@
 \begin{equation} \label{eq:updatingFilter}
-    \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2, ~\subjectto ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in {1,...K},
+    \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2 \quad \text{subject to} \quad \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\},
 \end{equation}
-where $\Code= [\Code_1 ...
-\Code_K] \in \mathbb{R}^{D \times MK}$, constructed from computed $\code$, and $\filter= [\filter_1^T ...
-\filter_K^T]^T \in \mathbb{R}^{MK \times 1}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
+where $\Code= [\Code_1, \dots, \Code_K] \in \mathbb{R}^{D \times MK}$, constructed from computed $\code$, and $\filter= [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
 
-Like the approach in~\cite{heide2015fast}, we interleave on the above two subproblems to tackle the bi-convex problem, and each of them will be solved by ADMM.
-The joint optimization framework will be implemented in the fashions of batch mode and online mode.
+Similarly to the approach in~\cite{heide2015fast}, we alternate the above two subproblems to tackle the bi-convex problem, and each of them will be solved by ADMM.
+The joint optimization framework will be implemented in the fashions of {\em batch mode} (stochastic batch CSC) and {\em online mode} (stochastic online CSC).
 
@@
 
-\subsection{Stochastic Batch CSC (SBCSC)}
+\subsection{Stochastic Batch CSC}
 We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the uniform probability for one code been selected.
@@
 
-\subsection{Stochastic Online CSC (SOCSC)}
+\subsection{Stochastic Online CSC}
 We can further tackle the proposed problem in online fashion for a gain of scalability.
@@
 \begin{equation} \label{eq:updatingCodeOnline}
-    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} \mask^T)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
+    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} \mask^\top)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
 \end{equation}
@@
 \begin{equation}
-    \filter^t = \minimize{\filter} \frac{1}{2t}\sum_{i=1}^{t} \|\signal^i - \Code^i \filter \|_2^2, ~\subjectto ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in {1,...K}.
+    \filter^t = \minimize{\filter} \frac{1}{2t}\sum_{i=1}^{t} \|\signal^i - \Code^i \filter \|_2^2 \quad \text{subject to} \quad \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\}.
 \end{equation}
@@
 \begin{equation} \label{eq:updateSur}
-    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^T\Code^t ~~~~~~~~~ \surB^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^T\signal^t
+    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^\top \Code^t ~~~~~~~~~ \surB^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^\top \signal^t
 \end{equation}
@@
 \begin{equation} \label{eq:updatingFilterOnline}
-    \filter^t = \minimize{\filter} \frac{1}{2} \filter^T\surC\filter - \filter^T\surB, ~ \subjectto ~ \|\filter_k\|_2^2 \leq 1 ~ \forall k \in {1,...K}
+    \filter^t = \minimize{\filter} \frac{1}{2} \filter^t \surC\filter - \filter^t\surB \quad \text{subject to} \quad \|\filter_k\|_2^2 \leq 1 ~ \forall k \in \{1,\dots,K\}.
 \end{equation}
+
+\peter{The above equations has issues.}
 
@@
 In our implementation, the vector-to-matrix mapping information is cached for an efficient indexing.
-As for matrix $\Filter$, we only explicitly construct matrix $(\Filter \mask^T)$ rather than $\Filter$ and $\mask$ separately for the sake of efficiency, and the similar indexing strategy is applied.
+As for matrix $\Filter$, we only explicitly construct matrix $(\Filter \mask^\top)$ rather than $\Filter$ and $\mask$ separately for the sake of efficiency, and the similar indexing strategy is applied.

### 2018-05-15 nips2018/nips_2018.tex
update

--- 2018-05-13 nips2018/main.tex
@@
 \usepackage{amsmath}
+
+% Commenting
+\usepackage[colorinlistoftodos,bordercolor=orange,backgroundcolor=orange!20,linecolor=orange,textsize=scriptsize]{todonotes}
+\newcommand{\peter}[1]{\todo[inline]{\textbf{Peter: }#1}} 
+\newcommand{\yinhui}[1]{\todo[inline]{\textbf{Yu: }#1}}
 
@@
 
+% snr onlineVSbatch online400Small
+
 \begin{abstract}
-
+The minimization problems formulated in Convolutional Sparse Coding (CSC) have been solved in frequency domain by modern approaches owing to the improved computing efficiency, while it automatically assumes circular boundary conditions.
+In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes.
+The proposed method experimentally shows a faster convergence rate compared to the state-of-the-art, and with a reasonable selection for the subsampling probability, it also achieves a better runtime efficiency.
+Moreover, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes.
+This combination leads to a significant speedup over the online CSC algorithm solved in frequency domain.
+We then learn the over-complete dictionary from thousand of images, which demonstrates a better sparse representation of the natural images on account of more abundant filters.
 \end{abstract}
@@
 
-% \input{Discussions}
+\input{Conclusion}
 
@@
 
+\clearpage
+\appendix
+\section{More Experiments}
+
+\peter{Include more experiments here}
+
 \end{document}

### 2018-05-15 nips2018/main.tex
Update main.tex

@@
 \input{macro}
+
+% Commenting
+\usepackage[colorinlistoftodos,bordercolor=orange,backgroundcolor=orange!20,linecolor=orange,textsize=scriptsize]{todonotes}
+\newcommand{\peter}[1]{\todo[inline]{\textbf{Peter: }#1}}
 
@@
 \begin{abstract}
-
+The minimization problems formulated in Convolutional Sparse Coding (CSC) have been solved in frequency domain by modern approaches owing to the improved computing efficiency, while it automatically assumes circular boundary conditions.
+In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes.
+The proposed method experimentally shows a faster convergence rate compared to the state-of-the-art, and with a reasonable selection for the subsampling probability, it also achieves a better runtime efficiency.
+Moreover, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes.
+This combination leads to a significant speedup over the online CSC algorithm solved in frequency domain.
+We then learn the over-complete dictionary from thousand of images, which demonstrates a better sparse representation of the natural images on account of more abundant filters.
 \end{abstract}

### 2018-05-18 nips2018/CSCmodel.tex
submiited version

@@
     \minimize{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
-    \subjectto & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in {1,...K},
+    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
 \end{split}
 \end{equation}
-where $\signal \in \mathbb{R}^D$ is a D-dimensional signal or a vectorized image~\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the k-th dictionary and $\code_k$ is the sparse code associated with that dictionary, and it has the same dimension size as $\signal$.
-$K$ is the number of dictionary filters, and $*$ is the convolution operator.
-The above equations will be applied to all the training images.
+where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a vectorized image\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in \mathbb{R}^D$ is the sparse code associated with that dictionary,  $\lambda>0$ is a sparsity inducing penalty parameter, $K$ is the number of dictionary filters, and $*$ is the convolution operator.
+The above model will be applied to all the training images.
 
-The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent.
-There exists several issues regarding to the model and the frequency solvers.
+The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
+The model and existing frequency solvers suffer from several issues:
 
 \begin{itemize}
-  \item Though CSC overcomes the independence assumption held in patch-based learning algorithms, far more variables ($K$ times more), as a payback, will be introduced to represent a single image.
-This brings in more severe memory and computational burden.
-  \item The reconstructed sparse codes show that in the case of $K=100$, the majority of the entries (more than $99.5\%$) do not provide valid information to the represented image, which indicates the subproblem for updating $\code$ solves a highly sparse LASSO problem.
+  \item While CSC overcomes the independence assumption held in patch-based learning algorithms, far more variables ($K$ times more) are introduced to represent a single image to compensate for this.
+This creates more severe memory and computational burdens.
+
+  \item We observe through experiments that the vast majority of the entries of the reconstructed sparse codes do not provide useful information about the represented image.
+For $K=100$, 99.5\% entries are not informative.
+This indicates that the subproblem for updating $\code$ solves a highly sparse LASSO problem.
 Transforming the problem into frequency domain imposes restriction on the use of optimization strategies for this very specific problem.
-  \item The prior work shows its efficiency of solving the CSC problem in frequency domain, while this is only applicable for updating $\code$, and it does not hold for updating $\filter$.
-Dictionaries usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$), while in order to tackle the problem in frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
+
+  \item While prior work shows its efficiency in solving the CSC problem in the frequency domain, this is only applicable for updating $\code$, and does not hold for updating $\filter$.
+The dictionary filters usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$).
+However, in order to tackle the problem in the frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
 \end{itemize}

### 2018-05-18 nips2018/Conclusion.tex
submiited version

\section{Conclusions}
In this work, we present a novel stochastic subsampling strategy for updating sparse codes and it significantly improves the runtime performance to solve the CSC problem in spatial domain, which applies to both batch mode and online-learning mode, as well as generating effective and proven outcomes. Since the subproblem of updating the code is a highly sparse LASSO, other specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in~\cite{johnson2017stingycd}, which solves the LASSO problem by coordinate descent and skips unnecessary updates by the method of safe screening~\cite{ghaoui2012Swfe}. Moreover, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the images and the sparse codes. Notice that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies. In addition, we have shown the capability of the developed online algorithm to learn representative over-complete dictionary from large datasets, and the availability of the dictionary is further verified by the application of image inpainting. It can be foreseen that this capability has widespread applications in the audio and image related tasks, and higher dimensional signal processing.

### 2018-05-18 nips2018/Introduction.tex
submiited version

@@
 \section{Introduction}
-Convolutional Sparse Coding (CSC) has been demonstrated to be an effective tool to learn translational invariant dictionaries from a number of training signals, and shows its applications in recent researches obout neural and brain information processing~\cite{jas2017learning,peter2017sparse}, as well as in a variety of image processing tasks, for instance, image inpainting~\cite{heide2015fast}, super-resolution~\cite{gu2015convolutional}, high dynamic range imaging~\cite{serrano2016convolutional}, and high-dimensional signal reconstructions~\cite{choudhury2017consensus,bibi2017high}.
+Convolutional Sparse Coding (CSC) has been demonstrated to be an effective tool to learn translational invariant dictionary from a number of training signals, and shows its applications in recent researches about neural and brain information processing~\cite{jas2017learning,peter2017sparse}, as well as in a variety of image processing tasks, for instance, image inpainting~\cite{heide2015fast}, super-resolution~\cite{gu2015convolutional}, high dynamic range imaging~\cite{serrano2016convolutional}, and high-dimensional signal reconstructions~\cite{choudhury2017consensus,bibi2017high}.
 CSC differs from conventional sparse coding by formulating the signals as a summation of a set of convolutions on dictionary filters and sparse codes, rather than linearly adding up those filters.
-Alternatively, sparse coding, as a patch-based approach, learns filters from partitioned local structures, and this partition operation discards inherent correlations between those patches, so as to learns redundant filters (the same or similar ones with translated versions).
-Owing to the convolutional property, the dictionaries learned from CSC achieves signal global coherence, tending to be more representative.
+Alternatively, sparse coding, as a patch-based approach, learns filters from partitioned local structures, and this partition manipulation discards inherent correlations between those patches, so as to learns redundant filters (the same or similar ones with translated versions).
+Owing to the convolutional property, the dictionary learned from CSC achieves signal global coherence, tending to be more representative.
 It should be emphasized that the convolutional-based deep learning, evolving from pioneering work~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet}, has shown its extraordinary success in a broad range of high-level image understanding applications.
@@
 
-To solve the optimization problems formulated in CSC, \cite{zeiler2010deconvolutional} iteratively solves two subproblems (updating sparse coding and updating filters) using gradient decent in the form of convolutional operations, while performing convolution in spatial domain is computationally expensive.
-Recent algorithms tackles the problem by exploiting Parseval's theorem to express spatial convolution by multiplication in the frequency domain and using Alternating Direction Method of Multipliers (ADMM)~\cite{boyd2011distributed} to separate the non-smooth terms in the optimization problem, and they show tremendous improvements over spatial solvers with respect to running time~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
+To solve the optimization problems formulated in CSC, Zeiler et al.~\cite{zeiler2010deconvolutional} iteratively solves two subproblems (updating sparse codes and updating filters) using gradient decent in the form of convolutional operations, while performing convolution in spatial domain is computationally expensive.
+Recent algorithms tackles the problem by exploiting Parseval's theorem to express the spatial convolution by multiplication in the frequency domain and using Alternating Direction Method of Multipliers (ADMM)~\cite{boyd2011distributed} to separate the non-smooth terms in the optimization problem, and they show tremendous improvements over prior spatial-domain solvers with respect to running time~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
 Most of the prior work learns the dictionary filters in a batch mode, which indicates that all training signals are involved in every training iteration, and this restricts it from applying to large datasets or streaming data.
 
-In contrast to batch mode learning, online learning~\cite{shalev2012online} is a well established strategy which processes a single or a portion (minibatch) of the whole data at each training step, and incrementally updates model variables.
+In contrast to batch mode learning, online learning~\cite{shalev2012online} is a well established strategy which processes a single or a portion (mini-batch) of the whole data at each training step, and incrementally updates model variables.
 Herein, the required memory and computing sources are only dependent on the sample size in every observation, independent of the training data size.
-It alleviates the scalability issue arisen in batch approaches, and was firstly synergetic with sparse coding based on stochastic approximation~\cite{bousquet2008tradeoffs}, which was then scaled up to millions of training samples~\cite{mairal2009online,mairal2010online}.
-More recently, \cite{liu-2018-first} proposed an online learning based CSC algorithm, and analyzed different solvers and strategies when implementing it.
+It alleviates the scalability issue arisen in batch approaches, and the convergence of the algorithm was firstly analyzed using stochastic approximation tools~\cite{bottou1998online}.
+Bottou et al.~\cite{bousquet2008tradeoffs} further showed better generalization performance of the stochastic algorithms than standard gradient descent on large scale learning systems.
+Later on, online learning strategies were synergetic with sparse coding, which was then scaled up to learn dictionary from millions of training samples~\cite{mairal2009online,mairal2010online}.
+More recently, Liu et al.~\cite{liu-2018-first} proposed an online learning based CSC model, and analyzed different solvers and strategies when implementing it.
 
@@
 First of all, we introduce a randomization strategy in the subproblem of updating sparse codes and solve the entire problems in spatial domain.
-It demonstrates that the proposed spatial solver, with a reasonably selected subsampling probability, outperforms the state-of-the-art frequency solvers with less computation time (per iteration), and also achieves faster convergence (less number of iterations).
-We then formulate an online-learning version of the proposed algorithm, and it shows dramatic runtime improvement over prior online CSC methods, as well as better learning outcomes.
+It demonstrates that the proposed stochastic spatial-domain solver, with a reasonably selected subsampling probability, outperforms the state-of-the-art frequency-domain solvers with less computation time (per iteration), and also achieves faster convergence (less number of iterations).
+We then formulate an online-learning version of the proposed algorithm, and it shows dramatic runtime improvement over precedent online CSC methods, as well as producing comparable outcomes.
 At last, we demonstrate its capability to learn the over-complete dictionary from thousands of images, and analyze the effectiveness of the learned over-complete dictionary, which has not been reported or analyzed by precedent CSC work.

### 2018-05-18 nips2018/Results.tex
submiited version

@@
 \section{Results} \label{sec:result}
-\subsection{Sub-Sampling Strategy}
-We first evaluate the convergence and effectiveness of the proposed sub-sampling strategy, and compare it with state-of-the-art frequency solver~\cite{heide2015fast}.
-The proposed algorithm, with different sub-sampling factors, was tested on the fruit dataset~\cite{zeiler2010deconvolutional} which contains 10 training images in the size of $100 \times 100$.
-The dictionary dimension size is set to $11 \times 11 \times 100$.
+We first validate the proposed algorithms on fruit and city datasets~\cite{zeiler2010deconvolutional}, both of which contain 10 training images in the size of $100 \times 100$.
+The online-mode algorithms are then adapted to one thousand $100 \times 100$ image patches randomly picked up from ImageNet~\cite{deng2009imagenet}.
+The dictionary dimension size is set to $11 \times 11 \times 100$ in all experiments except for over-complete dictionary.
+All training and evaluation processes in this manuscript are performed on contrast normalized images~\cite{zeiler2010deconvolutional,heide2015fast}.
 
-{\bfseries Convergence.} Comparisons of the convergence between the proposed method and the state-of-the-art are shown in Fig.~\ref{fig:subsampleResult}.
+\subsection{Subsampling Strategy}
+
+{\bfseries Convergence.} Comparisons of the convergence between the proposed method (SBCSC) and the state-of-the-art batch-mode algorithm~\cite{heide2015fast} are shown in Fig.\ \ref{fig:subsampleResult}.
 A different selection of the subsampling probability reveals that the proposed strategy will slightly influence the convergence and the training objective of the minimization problem.
-Specifically, the more subsampled, the relatively slower convergence and the higher objective will be obtained.
-On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solvers for one iteration.
+Specifically, the less subsampled, the relatively slower convergence and the higher objective will be obtained.
+On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solver for one iteration.
 We observe that a subsampling rate between $0.1$ and $0.2$ delivers empirically good enough convergence in our settings, as well as achieving at least $3 \times$ speedup.
-It should be clarified that for a better representation, the cropped objectives are plotted after the first iteration, while all of them have the same initial objective.
-Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to a optimum with comparable objective after 10 iterations.
-In summary, comparing to the state-of-the-art frequency solver, the proposed method with a subsampling rate of $10\%$ not only spends two times less processing time per iteration, but also needs fewer iterations to converge.
+In general, the proposed method converges within 10 iterations, while the comparable method requires roughly 13 iterations to reach convergence.
+Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
+In summary, comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate of $10\%$ not only spends two times less processing time per iteration, but also needs fewer iterations to converge.
+Please see supplementary materials for additional experimental results.
 
 \begin{figure}[h]
+\centering
 \begin{subfigure}{0.6\textwidth}
@@
 
-\caption{Left: Convergence comparison between the-state-of-art method\cite{heide2015fast} and the proposed method with different subsampling probability.
+\caption{Left: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling probability, all of which are performed on the fruit dataset.
 Right: Learned filters by the proposed method with $p=0.1$ and the comparable method.
-In these represented learned filters, our method learns more Gabor-like and less noise-like filters.
+In these represented learned filters, our method learns more smooth Gabor-like filters and less number of noise-like filters.
 Beyond this, it runs faster with regard to each iteration and shows better convergence behavior.}
@@
 {\bfseries Reconstruction}.
-The learned filters by the proposed method with subsampling rate $0.1$ are shown on the right hand side of Fig.~\ref{fig:subsampleResult}.
+The learned filters by SBCSC with subsampling rate $0.1$ are shown on the right hand side of Fig.\ \ref{fig:subsampleResult}.
 For a visual comparison, we also show the filters learned from the competing method.
@@
 While after zooming, it can be seen that our learned Gabor-like filters have less impure structures.
-Moreover, the comparable filters contain a number of noise-like dictionaries, which are rarely existed in ours.
+Moreover, the comparable dictionary contains a number of noise-like filters, which are rarely existed in ours.
 We then demonstrate the effectiveness of the reconstructed filters in the application of image inpainting, which refers to reconstructing a full image from partial measurements.
-A numerical comparison of the reconstruction quality is shown in Fig.~\ref{fig:PSNRrecon}.
+A numerical comparison of the reconstruction quality is shown in Fig.\ \ref{fig:PSNRrecon}.
 The filters learned by the proposed method not only show more visually decent structures and less specific features, but also demonstrate its capability to better reconstruct partial observed images.
@@
 \subsection{Online Learning Settings}
-We further evaluate the online fashion of the proposed method.
-To begin with, we validate the proposed algorithm on the city dataset~\citep{zeiler2010deconvolutional}, which has 10 training images and 4 testing images, and all of them has the size of $100 \times 100$.
-Afterwards, over-complete dictionaries are learned from 1000 images randomly picked up from ImageNet~\cite{deng2009imagenet}.
 
-{\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire
-dataset cannot be evaluated since each training step only draws one or a few of the data samples.
-Otherwise, we can evaluate the learning process on testing images.
-The loss objectives on testing dataset of the proposed algorithm (SOCSC) and prior published online CSC model solved in frequency domain~\citep{liu-2018-first} (FOCSC), with respect to iterations and time, are shown in Fig.~\ref{fig:onlineConvergence}.
-The proposed method not only exhibits a better convergence performance, but also takes much less execution time, achieving roughly $5 \times$ speedup for one iteration.
+{\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire dataset cannot be evaluated during the online learning processes,since each training step only draws one or a few of the data samples.
+Nevertheless, we can evaluate the learning process on testing images.
+The testing objectives of the proposed method (SOCSC) and prior published online frequency-domain CSC method~\cite{liu-2018-first}, with respect to iterations, are shown in Fig.\ \ref{fig:onlineSmall}.
+In the same figure, we also keep track of the capability of the updated filters during the process of learning to sparsely represent the testing images, which is demonstrated by the time evolution of PSNR.
+These two approaches stop at optimum positions with close testing objective values, though, they exhibit slightly different convergence behaviors with respect to iterations.
+The final testing PSNR values for both methods also reveal the similar reconstruction performance of the learned filters.
+As for the runtime comparison, the proposed method runs at least 5 times faster than the comparable method.
+Supplement shows additional comparisons for different datasets.
+
+%The proposed method not only exhibits a better convergence performance, but also takes much less execution time, achieving roughly $5 \times$ speedup for one iteration.
 A visual comparison of the learned dictionaries also demonstrates that the proposed algorithm delivers better outcomes.
-Further numerical comparison will be reported in the next section.
+% Further numerical comparison will be reported in the next section.
 
 \begin{figure}[h]
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=1\linewidth]{figure/iteVSobjOnline.pdf}
+\centering
+\begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite-fruit.pdf}
 \end{subfigure} 
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=1\linewidth]{figure/timeVSobjOnline.pdf}
+\begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time-fruit.pdf}
 \end{subfigure}
 
-\caption{}
-\label{fig:onlineConvergence}
+\caption{The experiments are performed on fruit dataset, and each iteration randomly choose one image from the training sets.
+Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
+Right: Testing PSNR with respect to execution time.
+While the quality of the output is comparable, our method achieves $5 \times$ speedup.}
+\label{fig:onlineSmall}
 \end{figure}
 
-{\bfseries Over-complete dictionaries.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (the number of filters is more than the degrees of freedom).
-One of the reasons could be that most of the prior work is batch-based approach, thus learning over-complete dictionary from small dataset would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability.
-The proposed online-based learning strategy can overcome this issue by scaling up to arbitrary sample sizes.
+{\bfseries Over-complete dictionary.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (the number of filters is more than the degrees of freedom).
+One of the reasons could be that most of the prior work is batch-based, thus learning over-complete dictionary from small datasets would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability (we verify this explanation in supplement).
+The proposed online-based learning strategy (SOCSC) can overcome this issue by scaling the model up to arbitrary sample sizes.
 
-We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.~\ref{fig:overCompleteDic} .
-As a comparison, 100 learned filters by the same algorithm and its comparable approach are also represented for a visual comparison.
-As can be observed, both of the approaches learn visually similar under-complete dictionaries, while the proposed method shows a $5 \times$ speedup over the other.
-Furthermore, the learned over-complete dictionary is composed of the gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
-These additional feature information would play an essential role to better represent the natural images, which can be demonstrated in Fig.~ .
-There is a bottleneck for under-complete dictionary that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
-However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement with regard to PSNR to have a sparse representation of the testing images.
+We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.\ \ref{fig:overCompleteDic} .
+For a visual comparison, 100 learned filters by the same algorithm and its comparable approach~\cite{liu-2018-first} are also represented.
+As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method takes $5 \times$ less training time than the competitive one.
+As for the learned over-complete dictionary, it is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
+This additional feature information would play an essential role to better reconstruct the natural images, which can be demonstrated by the results of reconstruction quality shown in the same figure.
 
@@
     \centering
-  \includegraphics[width=0.6\linewidth]{figure/liu100-filter.pdf}
+  \includegraphics[width=0.75\linewidth]{figure/liu100-filter.pdf}
   \vspace*{2mm}
@@
     \centering
-  \includegraphics[width=0.6\linewidth]{figure/online100-filter.pdf}
+  \includegraphics[width=0.75\linewidth]{figure/online100-filter.pdf}
 \end{subfigure}
 \end{minipage}
-\begin{minipage}{0.5\textwidth}
+\begin{minipage}{0.6\textwidth}
 \centering
-\includegraphics[width=1\linewidth]{figure/online400-filter.pdf}
+\includegraphics[width=0.97\linewidth]{figure/online400-filter.pdf}
 \end{minipage}
+    \\
+    \\
+    \\
+    \resizebox{1\linewidth}{!}{
+        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
+            \cline{1-11}
+            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+            \hline
+            PSNR by (a) & 29.58 & 28.19 & 29.44 & 29.63 & 28.89 & 29.33 & 28.13  & 30.14 & 27.42 & 30.89 \\
+            \hline
+            PSNR by (b) & 29.63 & 28.22 & 29.57 & 29.90 & 29.12 & 29.59 & 28.05  & 30.17 & 27.53 & 31.08 \\
+            \hline
+            PSNR by (c) & \textbf{30.24} & \textbf{28.34} & \textbf{29.95}  & \textbf{30.30} & \textbf{29.43} & \textbf{29.96} & \textbf{28.24} & \textbf{30.57} & \textbf{27.72} & \textbf{31.67} \\
+            \hline
+        \end{tabular} }
 
-\caption{Filters learned from 1000 images by the proposed method and its comparison.
-(a) The under-complete dictionary ($11 \times 11 \times 100$) learned by~\cite{liu-2018-first}; (b) The under-complete dictionary ($11 \times 11 \times 100$) learned by the proposed method.
-(c) The over-complete dictionary ($11 \times 11 \times 400$) learned by the proposed method.
-These under-complete dictionaries, mainly composed of gabor-like filters, can be seen as a subset of the represented over-complete dictionary, which also contains a number of low contrast image features.}
+\caption{Filters learned from 1000 images by our method (SOCSC) and the state-of-the-art online method~\cite{liu-2018-first}, and their corresponding reconstruction quality using the same hyperparameter settings as in Fig.\ \ref{fig:PSNRrecon}.
+(a) The under-complete dictionary ($11 \times 11 \times 100$) learned by~\cite{liu-2018-first}; (b) The under-complete dictionary ($11 \times 11 \times 100$) learned by SOCSC.
+(c) The over-complete dictionary ($11 \times 11 \times 400$) learned by SOCSC.
+These under-complete dictionaries, mainly composed of Gabor-like filters, can be seen as a subset of the represented over-complete dictionary, which contains a number of extra low contrast image features.}
 \label{fig:overCompleteDic}
 \end{figure}
+
+We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
+The left hand side of Fig.\ \ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
+However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement, with regard to PSNR, to have a sparse representation of the testing images during the learning process.
+This is also verified by applying these learned dictionaries to the image inpainting application as discussed above.
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}{0.41\textwidth}
+  \includegraphics[width=1\linewidth]{figure/overComplete-ite.pdf}
+\end{subfigure} 
+\begin{subfigure}{0.58\textwidth}
+  \includegraphics[width=1\linewidth]{figure/minibatch.pdf}
+\end{subfigure}
+
+\caption{Left: Testing PSNR for the comparable method~\cite{liu-2018-first} with $K=100$, and our method (SOCSC) with $K=100$ and $K=400$, respectively.
+Every iteration draws a single image from those 1000 image patches.
+Right: Testing PSNR for SOCSC ($K=400$) with varying values of $\eta$.
+The learned filters are examined on the test sets every $2^i$ iterations and also at the last iteration, where $i=0,1,\dots$.
+Note that all the results are generated by a single-core program.}
+\label{fig:overComDicAndMinibatch}
+\end{figure}
+
+{\bfseries Mini-batching.} In practice, a mini-batching strategy would be preferred in order to gain advantages from modern parallel computing architectures.
+This is also a standard extension to stochastic optimization algorithms~\cite{Takac2013, PCDM, SCSG}.
+We denote the mini-batch size as $\eta$.
+In the proposed online algorithm (SOCSC), the time complexity for one step dictionary update will not increase linearly with the increase of $\eta$.
+Concretely speaking, updating $\code$ is implemented by Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
+Herein, the complexity for doing updating $\code$ $\eta$ times all together is cheaper than $\eta$ times the complexity of updating one $\code$.
+In addition, the time complexity for updating $\filter$ is not affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
+One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this is not dominant in the runtime.
+The runtime comparisons for various mini-batch sizes are shown in Fig.\ \ref{fig:overComDicAndMinibatch}.
+Note that larger $\eta$ will result in less number of iterations to process all 1000 images.
+The plots show that a larger mini-batch size will generally lead to a greater progress in first few training steps, though it takes additional running time and memory.
+Overall, mini-batched updates provides a more runtime efficient learning process in the online-based CSC model, and according to the obtained experimental results, $\eta=20$ achieves one magnitude speedup over $\eta=1$ to reach a condition with the same level convergence on a single-core program.
+Since computing sparse codes is a data-independent process, this mini-batched approach can be further accelerated by a distributed computing system.

### 2018-05-18 nips2018/SCSCmodel.tex
submiited version

@@
 \begin{equation} \label{eq:updatingCode}
-    \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^T)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
+    \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^\top)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
 \end{equation}
-where $\Filter = [\Filter_1 ...
-\Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1^T ...
-\code_K^T]^T \in \mathbb{R}^{DK \times 1}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
-$\mask$ is a randomized sub-sampling diagonal matrix with $1$ on the entries corresponding to the sampled sparse codes, performing the function of choosing a random portion of the sparse codes for reconstruction.
+where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
+Matrix $\mask$ is a random diagonal subsampling matrix with ones on the entries corresponding to the sampled sparse codes and zeros elsewhere, performing the function of choosing a random portion of the sparse codes for reconstruction.
 Herein, the $\code$-subproblem only computes the sparse codes in the chosen positions.
 Due to the introduced subsampling matrix, the convolution operator will not hold, hence it cannot be solved in the frequency domain.
-This subsampling strategy is akin to the dropout technique~\cite{srivastava2014dropout}, which has been widely used to prevent overfitting when training deep neural networks.
-However, different from dropout that generally needs more time to train a neural network than standard approaches, with a good selection of subsampling probability $p$, the proposed method shows less per iteration running time and faster convergence than state-of-the-arts (see section~\ref{sec:result}).
+This stochastic subsampling strategy is akin to the dropout technique~\cite{srivastava2014dropout}, which has been widely used to prevent overfitting when training deep neural networks.
+However, different from dropout that generally needs more time to train a neural network than standard approaches, with a good selection of subsampling probability $p$, the proposed method shows less per iteration running time and faster convergence than state-of-the-arts (see Section~\ref{sec:result}).
 
-After obtaining the subsampled codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
+After obtaining the subsampled sparse codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
 \begin{equation} \label{eq:updatingFilter}
-    \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2, ~\subjectto ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in {1,...K},
+    \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2 \quad \text{subject to} \quad \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\},
 \end{equation}
-where $\Code= [\Code_1 ...
-\Code_K] \in \mathbb{R}^{D \times MK}$ and $\filter= [\filter_1^T ...
-\filter_K^T]^T \in \mathbb{R}^{MK \times 1}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
+where $\Code= [\Code_1, \dots, \Code_K] \in \mathbb{R}^{D \times MK}$ is a concatenated matrix, where $\Code_k$ is constructed from the associated $\code_k$, $\filter= [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
 
-Like the approach in~\cite{heide2015fast}, we interleave on the above two subproblems to tackle the bi-convex problem, and each of them will be solved by ADMM.
-The jointly optimization framework will be implemented in the fashions of batch mode and online mode.
+Similar to the approach in~\cite{heide2015fast}, we alternate the above two subproblems to tackle the bi-convex problem, and each of them will be solved by ADMM.
+The joint optimization framework will be implemented in the fashions of {\em batch mode} (stochastic batch CSC) and {\em online mode} (stochastic online CSC).
 
@@
 \begin{algorithmic}[1]
-\State $\text{Initialize} ~ \filter;$
+\State $\text{Initialize} ~ \filter, p$
 \While {not converge}
-    \State $\Filter \gets \text{constructD}(\filter);$
+    \State $ \text{Generate } \mask $
+    \State $\Filter \gets \text{constructD}(\filter)$
     \For{i=1 to N}
-        \State $ \text{Generate } \mask \text{ given } p;$
-        \State $ \text{Update } \code^i \text{ by solving problem~\ref{eq:updatingCode}};$
+        \State $ \text{Update } \code^i \text{ by solving problem~(\ref{eq:updatingCode}})$
     \EndFor
-    \State $\Code \gets \text{constructZ}(\code^{1,...,N});$
-    \State $\text{Update } \filter \text{ by solving problem~\ref{eq:updatingFilter}} ;$
+    \State $\Code \gets \text{constructZ}(\code^{1,\dots,N})$
+    \State $\text{Update } \filter \text{ by solving problem~(\ref{eq:updatingFilter}})$
 \EndWhile
@@
 \While {not converge}
-    \State $\Filter \gets \text{constructD}(\filter^t);$
     \State $t \gets t+1$
-    \State draw($\signal^t$, $\mask$);
-    \State $ \text{Compute } \code^t \text{ by solving problem~\ref{eq:updatingCodeOnline}};$
-    \State $\Code \gets \text{constructZ}(\code^t)$
-    \State Compute $\surC^t$ and $\surB^t$ by eq~\ref{eq:updateSur}
-    \State Update $\filter^t$ by solving problem~\ref{eq:updatingFilterOnline}
+    \State draw($\signal^t$, $\mask$)
+    \State $\Filter^{t-1} \gets \text{constructD}(\filter^{t-1})$
+    \State $ \text{Compute } \code^t \text{ by solving problem~(\ref{eq:updatingCodeOnline})}$
+    \State $\Code^t \gets \text{constructZ}(\code^t)$
+    \State Compute $\surC^t$ and $\surB^t$ by eq~(\ref{eq:updateSur})
+    \State Compute $\filter^t$ by solving problem~(\ref{eq:updatingFilterOnline})
 \EndWhile
@@
 \subsection{Stochastic Batch CSC (SBCSC)}
-We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the probability for one specific code been selected.
-Every outer loop involves all of the training images, thus it would be expensive in computing these and also runs out of memory quickly with the increase of the number of images.
+We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $\code^{1,\dots,N}$ denotes the stack of all the sparse codes, $p$ is the uniform probability for one code been selected.
+We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this work, where $p=1$ indicates no subsampling, and $p=0.05$ indicates a subsampling rate of $5\%$.
+The matrix $\Code$ needs to be explicitly constructed and it may lead to a considerable computational burden, resulting in a heavy overhead if processed in an inefficient way.
+In our implementation, the vector-to-matrix mapping information is cached for an efficient indexing.
+As for matrix $\Filter$, we only explicitly construct matrix $(\Filter \mask^\top)$ rather than $\Filter$ and $\mask$ separately for the sake of efficiency, and the similar indexing strategy is applied (line 3 and 4 are practically merged by a single operation, but for an intuitive understanding of the algorithm, we split them in the pseudo code).
+Every outer loop involves all of the training images, thus it would be computationally expensive to process them simultaneously and also runs out of memory quickly with the increase of the number of images.
 The batch-based learning algorithm lacks of the capability to scale up to very large datasets or to handle dynamically changed training data.
@@
 \subsection{Stochastic Online CSC (SOCSC)}
-We can further tackle the proposed problem in online fashion for a gain of scalability.
-In the online learning setting, each iteration only draws one or a subset (minibatch) of the total training images, hence the complexity per loop is independent of the training sample size.
+We can further tackle the proposed problem in the online fashion for a gain of scalability.
+In the online learning setting as shown in Algorithm~\ref{algo:SOCSC}, each iteration only draws one or a subset (mini-batch) of the total training images and the corresponding subsampling diagonal matrix $\mask$, denoted as draw($\signal^t$, $\mask$), hence the complexity per loop is independent of the training sample size.
 Then, given the sampled image $\signal^t$ at $t$-th iteration, we can compute the corresponding sparse codes $\code^t$ by
 \begin{equation} \label{eq:updatingCodeOnline}
-    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} \mask^T)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
+    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} \mask^\top)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
 \end{equation}
-where $\Filter^{t-1}$ is constructed from the dictionaries learned by $(t-1)$th iteration. After obtaining the sparse codes, the dictionary is updated by:
+where $\Filter^{t-1}$ is constructed from the dictionary learned by $(t-1)$th iteration. After obtaining the sparse codes, the dictionary is updated by:
 \begin{equation}
-    \filter^t = \minimize{\filter} \frac{1}{2t}\sum_{i=1}^{t} \|\signal^i - \Code^i \filter \|_2^2, ~\subjectto ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in {1,...K}.
+    \filter^t = \minimize{\filter} \frac{1}{2t}\sum_{i=1}^{t} \|\signal^i - \Code^i \filter \|_2^2 \quad \text{subject to} \quad \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\}.
 \end{equation}
-Notice that updating dictionary involves all the past training images and sparse codes.
+Notice that updating dictionary involves all of the past training images and sparse codes.
 As shown in~\cite{mairal2009online,mairal2010online}, we can get rid of explicitly storing those data by introducing two surrogate matrices $\surC \in \mathbb{R}^{KM \times KM}$ and $\surB \in \mathbb{R}^{KM \times 1}$, which carry all of the required information for updating $\filter$, and can be iteratively updated by:
 \begin{equation} \label{eq:updateSur}
-    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^T\Code^t ~~~~~~~~~ \surC^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^T\signal^t
+    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^\top \Code^t ~~~~~~~~~ \surB^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^\top \signal^t
 \end{equation}
@@
 \begin{equation} \label{eq:updatingFilterOnline}
-    \filter^t = \minimize{\filter} \frac{1}{2} \filter^T\surC\filter - \filter^T\surB, ~ \subjectto ~ \|\filter_k\|_2^2 \leq 1 ~ \forall k \in {1,...K}
+    \filter^t = \minimize{\filter} \frac{1}{2} \filter^\top \surC^t\filter - \filter^\top \surB^t \quad \text{subject to} \quad \|\filter_k\|_2^2 \leq 1 ~ \forall k \in \{1,\dots,K\}.
 \end{equation}
@@
 The data fitting term and the $L_1$ penalty term are split, forming $x$-minimization step and $z$-minimization step, respectively.
-$x$-minimization step is a quadratic programming (QP) problem, and we cache the matrix factorization by Cholesky decomposition.
-$z$-minimization step can be solved by a point-wise shrinkage operation.
-Accordingly, updating $\filter$ (problem~\ref{eq:updatingFilter}) is a quadratic constrained quadratic programming (QCQP) problem, and we solve it using similar splitting and optimization strategies as solving Problem~\ref{eq:updatingCode}, except using Conjugate Gradient (CG) for $x$-minimization step and replacing the shrinkage function by projecting onto the constrained set for $z$-minimization step.
+The $x$-minimization step is a quadratic programming (QP) problem, and we cache the matrix factorization by Cholesky decomposition.
+The $z$-minimization step can be solved by a point-wise shrinkage operation.
+Accordingly, updating $\filter$ (Problem~\ref{eq:updatingFilter}) is a quadratic constrained quadratic programming (QCQP) problem, and we solve it using similar splitting and optimization strategies as solving Problem~\ref{eq:updatingCode}, except using Conjugate Gradient (CG) for $x$-minimization step and replacing the shrinkage function by projecting onto the constrained set for $z$-minimization step.
 The $\filter$-subproblem is warm started with previously computed results and these two subproblems are interleaved on their auxiliary variables.
-The corresponding subproblems in Algorithm~\ref{algo:SOCSC} are solved following the same optimization strategy as discussed above.
-We set the hyperparameters $\lambda=1$,  the augmented Lagrangian penalty $\rho_{\code}$ and $\rho_{\filter}$ to $10 \lambda$ and $50 \lambda$, respectively, for $\code$- and $\filter$-subroblem.
+The corresponding subproblems in Algorithm~\ref{algo:SOCSC} are solved following the same optimization strategy as discussed above, and the only exception is for updating $\code$ (Problem~\ref{eq:updatingCodeOnline}), where Cholesky decomposition or conjugate gradient is alternatively chosen depending on the mini-batch size.
+We set the hyperparameters $\lambda=1$,  the augmented Lagrangian penalty $\rho_{\code}$ and $\rho_{\filter}$ to $10 \lambda$ and $50 \lambda$, respectively, for $\code$- and $\filter$-subproblem.
 The ADMM iteration is fixed to 10 for all subroutines, and the over-relaxation strategy within ADMM is applied with $\alpha = 1.8$.
 The residual tolerance for CG is $1e^{-5}$.
-
-All the training and evaluation processes in this manuscript are performed on contrast normalized images.
-%We also tried to learning filters from images without pre-processing with little parameters tuning, which successfully learns similar Gabor-like features as learned from contrast normalized images, as well as low frequency filters.
-The results regarding to this will not be discussed in this work, while it can be applied to other applications where low frequency parts also need to be taken into account.
-%
-It should be noted that matrix $\Code$ needs to be explicitly constructed and it may lead to a considerable computational burden, resulting in a heavy overhead if processed in an inefficient way.
-In our implementation, the vector-to-matrix mapping information is cached for an efficient indexing.
-As for matrix $\Filter$, we only explicitly construct matrix $(\Filter \mask^T)$ rather than $\Filter$ and $\mask$ separately for the sake of efficiency, and the similar indexing strategy is applied.

### 2018-05-18 nips2018/supplement.tex
submiited version

%\part*{Supplementary Material\\ Stochastic Convolutional Sparse Coding}

\section{Zooming in on the Filters}

Here we zoom in on the filters from Fig.\ \ref{fig:subsampleResult}. Notice that our filters look more smooth for those Gabor-like filters and also contains less number of noise-like filters.

\begin{figure}[h]
\centering
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
  \end{subfigure}
\caption{Zoom-in view of the filters from Figure~\ref{fig:subsampleResult}.}
\end{figure}

\section{Additional Experiments}
In order to show the robustness of the proposed algorithms, We also conduct experiments on city dataset. We first compare SBCSC with the state-of-the-art batch-mode algorithm~\cite{heide2015fast}, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}. Similar to the results shown in Fig.\ \ref{fig:subsampleResult}, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm with better outcomes and runtime performance. Since the learning is performed on handful datasets, both of them learn quite a few data-specific image features. The reconstruction quality also shows a shortage of the generalization ability. For example, the eighth image, which contains a large portion of texture information existed in the filters learned from city dataset, can be significantly better reconstructed by such filters compared to those learned from fruit dataset, while it may have poorer performance on other types of images. Furthermore, compared with the over-complete dictionary, we can observe that the presented over-complete dictionary contains both of the image features (superficially similar) appeared in the filters learned from fruit and city dataset, even though they use totally different training images. It also experimentally shows a better reconstruction performance on all kinds of testing images.

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobj-city.pdf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobj-city.pdf}
\end{subfigure}

\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchCity100.pdf}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideCity100.pdf}
\end{subfigure}
\vspace{0.2cm}

    \resizebox{1\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
            \hline
            PSNR ours & \textbf{29.78} & \textbf{28.14} & \textbf{29.67}  & \textbf{29.85} & \textbf{28.88} & \textbf{29.95} & \textbf{27.97} & \textbf{30.37} & \textbf{27.14} & \textbf{30.89} \\
            \hline
        \end{tabular} }

\caption{Experimental results obtained on the city dataset. Top: Convergence comparison between the-state-of-art batch method~\cite{heide2015fast} and SBCSC with different subsampling probability. Middle: Learned filters by SBCSC with $p=0.1$ and the comparable method. Even though these dictionaries look similar, our method learns more smooth filters. Compared to the learned filters in Fig.\ \ref{fig:subsampleResult}, they have different representations of the dictionaries, where data-specific features are learned from handful training images. Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters.}
\label{fig:subsampleResult-city}
\end{figure}

We then compare SOCSC with the state-of-the-art online algorithm~\cite{liu-2018-first} on city dataset, the results of which are shown in Fig.\ \ref{fig:onlineSmall-city}. Similar to the results presented in Fig.\ \ref{fig:onlineSmall}, our method obtains comparable outcomes, meanwhile, achieves roughly $5 \times$ speedup.

\begin{figure}[h]
\centering
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
\end{subfigure}

\caption{Experimental results obtained on city dataset. Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}. Right: Testing PSNR with respect to execution time.}
\label{fig:onlineSmall-city}
\end{figure}

\section{Over-complete Dictionary and Large Datasets}
In this section, we verify the importance of a large dataset when learning the over-complete dictionary. in Fig.~\ref{fig:overCompleteDic-dataset}, we show a visual and quantitative comparisons between the over-complete dictionaries respectively learned by batch-mode algorithm on small dataset (the fruit dataset) and online-mode algorithm on large dataset (1000 images). Most of the filters learned from small dataset have poor structures and reveal very limited representative ability. The numerical results also demonstrate that it even shows a degraded reconstruction performance compared to the under-complete dictionary. Owing to plentiful training samples, our over-complete dictionary not only shows visually decent structures and more representative image features, but also leads to a significant improvement on image reconstruction. Based on all experimental results, it implies that the number of filters and number of training samples are both essential in the CSC model, therefore, the proposed algorithm has prominent advantages over the existing approaches.

\begin{figure}[h]
\centering
  \includegraphics[width=0.7\linewidth]{figure/heide400-supple.pdf}
  \includegraphics[width=0.7\linewidth]{figure/online400-supple.pdf}
  \vspace{0.2cm}

    \resizebox{1\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 29.60 & 28.11 & 29.47 & 28.98 & 28.79 & 29.21 & 28.03  & 29.31 & 27.42 & 30.52 \\
            \hline
            PSNR ours & \textbf{30.24} & \textbf{28.34} & \textbf{29.95}  & \textbf{30.30} & \textbf{29.43} & \textbf{29.96} & \textbf{28.24} & \textbf{30.57} & \textbf{27.72} & \textbf{31.67} \\
            \hline
        \end{tabular} }
  \caption{ Visual and numerical comparisons between the learned over-complete dictionaries by batch-mode algorithm and by online-mode algorithm. Top: Over-complete dictionary learned by batch CSC model~\cite{heide2015fast} on small dataset, and proposed online CSC model (SOCSC) on large dataset. Bottom: Respective reconstruction quality for these two over-complete dictionaries.}
  \label{fig:overCompleteDic-dataset}
\end{figure}

### 2018-05-18 code/SBCSC/BatchStochasticCSC.m

@@ -1,0 +1,88 @@
+%% first code for CSC in spatial domain
+function [ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
+
+    k = kernel_size(1);           
+    num_kernel  = kernel_size(end);
+
+    n = size(b,1);
+    num_image = size(b,3);
+    
+    b = reshape(b, [], num_image);
+
+    d = randn(k, k, num_kernel);
+    % normalize the initialization. Not necessary but suggested.
+    for i=1:num_kernel
+       d(:,:,i) =  d(:,:,i) ./ max( norm( d(:,:,i), 'fro' ), 1);
+    end
+    d = d(:);
+    
+    %% parameters
+    outer_ite = 10;
+    max_it_z = 10;
+    max_it_d = 10;
+    
+    batch_size = num_image;   
+    rho_d = 50*lambda;
+    rho_z = 10*lambda;
+    hit_rate = 0.1;    % probability for choosing one specific code 
+    total_time = 0;
+    
+    u_d     = zeros( k*k*num_kernel, 1 );
+    x_hat_d = zeros( k*k*num_kernel, 1 );
+    z       = zeros( n*n*num_kernel, batch_size );
+
+    cur_image = 1:num_image; 
+    for ite = 1:outer_ite
+
+        %% compute codes
+        t_train = tic;
+        
+        % randomly pick the sparse code for reconstruction                  
+        ind = randperm( n*n*num_kernel, hit_rate*n*n*num_kernel );
+        
+        % construct (DM^T)
+        [ind1, ind2, v] = find( d_ind(:,ind) );
+        D = sparse( ind1, ind2, d(v), n*n, numel(ind) );
+        
+        z_tmp = lasso(D, b(:,cur_image), lambda, rho_z, 1.8, max_it_z, 1);
+        
+        % project the results onto its original domain
+        z = zeros(n*n*num_kernel, batch_size);
+        z(ind,:) = z_tmp;
+        
+        %% update dictionary      
+        Z = constructZ( z, z_ind, n, batch_size, k, num_kernel );
+                 
+        d_old = d;
+        d = l2proj(Z, b(:), d_old, rho_d, 1.8, k*k, num_kernel, max_it_d);
+    
+        fprintf('ite: %3d - dictionary updates: %10.4f\n', ite, norm( d-d_old ) );
[…]

### 2018-05-18 code/SBCSC/conj_grad.m

@@ -1,0 +1,44 @@
+function x = conj_grad(b, A, x, max_it, tol, choice)
+    
+    if choice == 1
+        % calculate residual vector r assoiated with x
+        r = b - conv2(x,A,'same');
+        p = r;
+        rsold = r'*r;         
+        for i=1:max_it
+            Ap = conv2(p, A, 'same' );
+            % compute the scalar alpha
+            alpha = rsold / (p'*Ap);
+            % update approximation
+            x = x + alpha*p;
+            r = r - alpha*Ap;
+            rsnew = r'*r;
+            % check convergence
+            if abs(rsnew-rsold)<tol
+                break;
+            end
+            p = r+(rsnew/rsold)*p;
+            rsold = rsnew;
+        end
+        
+    elseif choice == 2 
+        r = b - A(x);
+        p = r;
+        rsold = r'*r;
+        for i=1:max_it
+            Ap = A(p);
+            alpha = rsold/(p'*Ap);
+            x = x + alpha*p;
+            r = r - alpha*Ap;
+            rsnew = r'*r;
+%             absnew = abs(rsnew-rsold);
+            if abs(rsnew-rsold)<tol
+                break;
+            end
+%             absold = absnew;
+            p = r+(rsnew/rsold)*p;
+            rsold = rsnew;
+        end
+        
+    end      
+end

### 2018-05-18 code/SBCSC/constructCodeIndex.m

@@ -1,0 +1,28 @@
+function z_ind = constructCodeIndex( kernel_size, n )
+    
+    k = kernel_size(1);
+    z_ind = cell(n*n, 1);
+    
+    z = (1 : n*n);   
+    M=0;
+    for i=1:n
+        tmp_M = repmat( z( (n*(i-1)+1):n*i ), [k 1] );
+        tmp_M = spdiags(tmp_M, -floor(k/2):n-floor(k/2)-1, k, n);
+        tmp_M = tmp_M';
+        if( i==1 )
+            M = sparse( kron( spdiags(ones(k,1), ...
+                ceil(k/2)-i, n, k), tmp_M) );
+        else
+            M = M + sparse( kron( spdiags(ones(k,1), ...
+                ceil(k/2)-i, n, k), tmp_M) );
+        end
+    end
+    Z_ind = M;
+    
+    for i1 = 1:length(z)
+        [ind1, ind2] = find( Z_ind==z(i1) );
+        z_ind{i1}.ind1 = ind1;
+        z_ind{i1}.ind2 = ind2;
+    end
+
+end

### 2018-05-18 code/SBCSC/constructDicIndex.m

@@ -1,0 +1,31 @@
+function d_ind = constructDicIndex( kernel_size, col, row, d )
+    
+    k = kernel_size(1);
+    num_kernel = kernel_size(3);
+    m = col; 
+    n = row;
+
+    d_ind = spalloc( m*n, m*n*num_kernel, k*k*m*n*num_kernel );
+    M = spalloc( m*n, m*n, k*k*m*n );
+    
+    if nargin == 3
+        d = [1:prod(kernel_size)]';
+    end
+    
+    for j=1:num_kernel
+        tmp_d = d( (j-1)*k*k+1 : j*k*k )'; 
+        for i=1:k           
+            tmp_M = repmat( tmp_d( k*i:-1:(k*(i-1)+1) ), [m 1] );
+            tmp_M = spdiags(tmp_M, -floor(k/2):floor(k/2), m, m);
+            if( i==1 )
+                M = kron( spdiags(ones(n,1), ...
+                    ceil(k/2)-i, n, n), tmp_M);
+            else
+                M = M + kron( spdiags(ones(n,1), ...
+                    ceil(k/2)-i, n, n), tmp_M);
+            end
+        end
+        d_ind(:, (m*n*(j-1)+1):m*n*j) = M;
+    end
+
+end

### 2018-05-18 code/SBCSC/l2proj.m

@@ -1,0 +1,58 @@
+function z = l2proj(A, b, d, rho, alpha, k, num_kernel, MAX_ITER)
+
+ABSTOL   = 1e-4;
+RELTOL   = 1e-2;
+
+[m, n] = size(A);
+
+% save a matrix-vector multiply
+Atb = A'*b;
+
+if isempty(d)
+    z = zeros(n,1);
+else
+    z = d;
+end
+
+x_hat = zeros(n,1);
+u = zeros(n,1);
+
+% cache the factorization
+A_cal = @(p) A'*(A*p) + rho.*p;
+
+for i = 1:MAX_ITER
+
+    % x-update
+    q = Atb + rho*(z - u);    % temporary value
+
+    x = conj_grad(q, A_cal, x_hat, 100, 1e-5, 2);
+
+    % z-update with relaxation
+    zold = z;
+    x_hat = alpha*x + (1 - alpha)*zold;
+    z = proj_l2(x_hat + u, k, num_kernel);
+    % u-update
+    u = u + (x_hat - z);
+
+
+    history.r_norm(i)  = norm(x - z, 'fro');
+    history.s_norm(i)  = norm(-rho*(z - zold), 'fro');
+
+    history.eps_pri(i) = sqrt(n)*ABSTOL + RELTOL*max(norm(x, 'fro'), norm(-z,'fro'));
+    history.eps_dual(i)= sqrt(n)*ABSTOL + RELTOL*norm(rho*u, 'fro');
+
+    if (history.r_norm(i) < history.eps_pri(i) && ...
+       history.s_norm(i) < history.eps_dual(i))
+         break;
+    end
+
+end
+
+end
+
+function z = proj_l2(x, k, num_kernel)
+    z = zeros(size(x));
+    for i=1:num_kernel
+       z((i-1)*k+1:i*k) =  x((i-1)*k+1:i*k) ./ max( norm(x((i-1)*k+1:i*k)), 1);
+    end
+end

### 2018-05-18 code/SBCSC/lasso.m

@@ -1,0 +1,65 @@
+function z = lasso(A, b, lambda, rho, alpha, MAX_ITER, option)
+
+[p, n] = size(A);
+[~, m] = size(b);
+
+% save a matrix-vector multiply
+Atb = A'*b;
+
+x = zeros(n,m);
+z = zeros(n,m);
+x_hat = zeros(n,m);
+u = zeros(n,m);
+
+% cache the factorization
+if option == 1 || isempty( option )
+    [L U] = factor(A, rho);
+elseif option == 2
+    A_cal = @(p) A'*(A*p) + rho.*p;
+end
+
+
+for k = 1:MAX_ITER
+    
+    % x-update
+    q = Atb + rho*(z - u);    % temporary value
+    
+    for i=1:m
+        if option == 1 || isempty( option )
+            if( p >= n )    % if skinny
+                x(:,i) = U \ (L \ q(:,i));
+            else            % if fat
+                x(:,i) = q(:,i)/rho - (A'*(U \ ( L \ (A*q(:,i)) )))/rho^2;
+            end
+        elseif option == 2
+            x(:,i) = conj_grad(q(:,i), A_cal, x_hat(:,i), 100, 1e-5, 2);
+        end
+    end
+
+    % z-update with relaxation
+    zold = z;
+    x_hat = alpha*x + (1 - alpha)*zold;
+    z = shrinkage(x_hat + u, lambda/rho);
+    % u-update
+    u = u + (x_hat - z);
+    
+end
+
+end
+
+function z = shrinkage(x, kappa)
+    z = max( 0, x - kappa ) - max( 0, -x - kappa );
+end
+
+function [L U] = factor(A, rho)
+    [m, n] = size(A);
+    if ( m >= n )    % if skinny
+       L = chol( A'*A + rho*speye(n), 'lower' );
+    else            % if fat
+       L = chol( speye(m) + 1/rho*(A*A'), 'lower' );
+    end
+
+    % force matlab to recognize the upper / lower triangular structure
+    L = sparse(L);
+    U = sparse(L');
+end

### 2018-05-18 code/SBCSC/main.m

@@ -1,0 +1,25 @@
+addpath('../image_helpers');
+CONTRAST_NORMALIZE = 'local_cn'; 
+ZERO_MEAN = 1;   
+COLOR_IMAGES = 'gray'; 
+
+% read images
+% we suggest to work on 100*100 (square) image patches (avoid working on large images and
+% large number of filters at the same time)
+[b] = CreateImages('../datasets/city_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
+b = reshape(b, size(b,1), size(b,2), [] );
+
+%% Define the parameters
+kernel_size = [11, 11, 100];
+lambda = 1;
+
+%% cache the vector to matrix info for efficient indexing
+% It may take some time (roughly 40s), while you only need to compute it once and store it
+d_ind = constructDicIndex(  kernel_size, size(b,1), size(b,2) );
+z_ind = constructCodeIndex( kernel_size, size(b,1) );
+
+%% Batch stochastic CSC
+[ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, lambda);
+
+%% visualize dictionary
+plotDic( d, 10, max(d(:)), min(d(:)) );

### 2018-05-18 code/SBCSC/plotDic.m

@@ -1,0 +1,15 @@
+%% online code for CSC in spatial domain
+function plotDic(d, s, max_d, min_d)
+
+    dic = reshape( d, 11,11,s*s );
+    figure
+    sub_dic = cell(size(dic,3),1 );
+    for i=1:size(dic,3)
+        sub_dic{i} = dic( :,:,i );
+    end
+    for i=1:size(dic,3)
+        subplot('Position',[(mod(i-1,s))/s 1-(ceil(i/s))/s 1/s-0.001 1/s-0.001]);
+        imshow( sub_dic{i}, [min_d max_d], 'init', 'fit' );
+    end
+    
+end

### 2018-05-18 code/SOCSC/OnlineStochasticCSC.m

@@ -1,0 +1,108 @@
+%% online code for CSC in spatial domain
+function [ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
+
+    k = kernel_size(1);           
+    num_kernel  = kernel_size(end);
+
+    n = size(b,1);
+    num_image = size(b,3);
+    
+    b = reshape(b, [], num_image);
+
+    d = randn(k, k, num_kernel);
+    % normalize the initialization. Not necessary but suggested.
+    for i=1:num_kernel
+       d(:,:,i) =  d(:,:,i) ./ max( norm( d(:,:,i), 'fro' ), 1);
+    end
+    d = d(:);
+    
+    %% set up parameters
+    outer_ite = 10;  % num_image;
+    max_it_z = 10;
+    max_it_d = 10;
+    
+    batch_size = 1;
+    rho_d = 50*lambda;
+    rho_z = 10*lambda;
+    hit_rate = 0.1;    % probability for choosing one specific code 
+    gamma = 1;         % forget factor
+    total_time = 0;
+    
+    % make sure outer_ite*batch_size not exceed the number of images
+    sequence = randperm(outer_ite*batch_size);
+    
+    for ite = 1:outer_ite
+
+        %% compute sparse codes
+        t_train = tic;
+        
+        cur_image = sequence((ite-1)*batch_size+1:ite*batch_size);
+        
+        % randomly pick the sparse code for reconstruction
+        ind = randperm( n*n*num_kernel, hit_rate*n*n*num_kernel );
+        
+        % construct (DM^T)
+        [ind1, ind2, v] = find( d_ind(:,ind) );        
+        D = sparse( ind1, ind2, d(v), n*n, numel(ind) );
+        
+        % if batch_size is large, use Cholesky decomposition
+        % otherwise use conjugate gradient.
+        % this is important for an efficient compute especially when
+        % batch_size is large.
+        z_tmp = lasso(D, b(:,cur_image), lambda, rho_z, 1.8, max_it_z, 2);
+        
+        % project the results onto its original domain
+        z = zeros(n*n*num_kernel, batch_size);
+        z(ind,:) = z_tmp;
+        
+        %% update dictionary       
+        Z = constructZ( z, z_ind, n, batch_size, k, num_kernel );
+           
[…]

### 2018-05-18 code/SOCSC/dicUpdate.m

@@ -1,0 +1,55 @@
+function z = dicUpdate(A, Atb, d, rho, alpha, k, num_kernel, MAX_ITER)
+
+ABSTOL   = 1e-4;
+RELTOL   = 1e-2;
+
+[~, n] = size(A);
+
+if isempty(d)
+    z = zeros(n,1);
+else
+    z = d;
+end
+
+x_hat = zeros(n,1);
+u = zeros(n,1);
+
+% [L U] = factor(A, rho);
+A_cal = @(p) A*p + rho.*p;
+
+for i = 1:MAX_ITER
+
+    % x-update
+    q = Atb + rho*(z - u);    % temporary value
+
+%     x = U \ (L \ q);
+    x = conj_grad(q, A_cal, x_hat, 100, 1e-5, 2);
+
+    % z-update with relaxation
+    zold = z;
+    x_hat = alpha*x + (1 - alpha)*zold;
+    z = proj_l2(x_hat + u, k, num_kernel);
+    % u-update
+    u = u + (x_hat - z);
+
+    history.r_norm(i)  = norm(x - z, 'fro');
+    history.s_norm(i)  = norm(-rho*(z - zold), 'fro');
+
+    history.eps_pri(i) = sqrt(n)*ABSTOL + RELTOL*max(norm(x, 'fro'), norm(-z,'fro'));
+    history.eps_dual(i)= sqrt(n)*ABSTOL + RELTOL*norm(rho*u, 'fro');
+
+    if (history.r_norm(i) < history.eps_pri(i) && ...
+       history.s_norm(i) < history.eps_dual(i))
+         break;
+    end
+
+end
+
+end
+
+function z = proj_l2(x, k, num_kernel)
+    z = zeros(size(x));
+    for i=1:num_kernel
+       z((i-1)*k+1:i*k) =  x((i-1)*k+1:i*k) ./ max( norm(x((i-1)*k+1:i*k)), 1);
+    end
+end

### 2018-05-18 code/SOCSC/main.m

@@ -1,0 +1,24 @@
+addpath('../image_helpers');
+CONTRAST_NORMALIZE = 'local_cn'; 
+ZERO_MEAN = 1;   
+COLOR_IMAGES = 'gray'; 
+% read images
+% we suggest to work on 100*100 (square) image patches (avoid working on large images and
+% large number of filters at the same time)
+[b] = CreateImages('../datasets/city_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
+b = reshape(b, size(b,1), size(b,2), [] );
+
+%% Define the parameters
+kernel_size = [11, 11, 100];
+lambda = 1;
+
+%% cache the vector to matrix info for efficient indexing
+% It may take some time (roughly 40s), while you only need to compute it once and store it
+d_ind = constructDicIndex(  kernel_size, size(b,1), size(b,2) );
+z_ind = constructCodeIndex( kernel_size, size(b,1) );
+
+%% online stochastic CSC
+[ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda);
+
+%% visualize dictionary
+plotDic( d, 10, max(d(:)), min(d(:)) );

### 2018-05-18 nips2018/main.tex
submiited version

@@
 \input{macro}
-
-% Commenting
-\usepackage[colorinlistoftodos,bordercolor=orange,backgroundcolor=orange!20,linecolor=orange,textsize=scriptsize]{todonotes}
-\newcommand{\peter}[1]{\todo[inline]{\textbf{Peter: }#1}}
 
@@
 Moreover, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes.
-This combination leads to a significant speedup over the online CSC algorithm solved in frequency domain.
-We then learn the over-complete dictionary from thousand of images, which demonstrates a better sparse representation of the natural images on account of more abundant filters.
+This combination leads to a significant speedup over the online frequency-domain CSC algorithm.
+We then learn the over-complete dictionary from large datasets, which demonstrates a better sparse representation of the natural images on account of more abundant filters.
 \end{abstract}
@@
 
+%\clearpage
 {\small
@@
 
+\clearpage
+\appendix
+
+\input{supplement.tex}
+
 \end{document}

### 2018-10-25 cvpr2019/Conclusion.tex
add paper

--- 2018-05-18 nips2018/Conclusion.tex
@@
 \section{Conclusions}
-In this work, we present a novel stochastic subsampling strategy for updating sparse codes and it significantly improves the runtime performance to solve the CSC problem in spatial domain, which applies to both batch mode and online-learning mode, as well as generating effective and proven outcomes.
+In this work, we present a novel stochastic subsampling strategy for solving the CSC problem in spatial domain.
+This method significantly improves the runtime performance over the prior frequency-domain solvers, which applies to both batch mode and online-learning mode, as well as generating effective and proven outcomes.
+The proposed algorithm, for the first time, demonstrates the feasibility that tackling the CSC problem in spatial domain while still holding the runtime efficiency.
 Since the subproblem of updating the code is a highly sparse LASSO, other specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in~\cite{johnson2017stingycd}, which solves the LASSO problem by coordinate descent and skips unnecessary updates by the method of safe screening~\cite{ghaoui2012Swfe}.
 Moreover, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the images and the sparse codes.
-Notice that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies.
+Notice that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies (including the proposed one).
 In addition, we have shown the capability of the developed online algorithm to learn representative over-complete dictionary from large datasets, and the availability of the dictionary is further verified by the application of image inpainting.

### 2018-10-25 cvpr2019/Introduction.tex
add paper

--- 2018-05-18 nips2018/Introduction.tex
@@
 Bottou et al.~\cite{bousquet2008tradeoffs} further showed better generalization performance of the stochastic algorithms than standard gradient descent on large scale learning systems.
-Later on, online learning strategies were synergetic with sparse coding, which was then scaled up to learn dictionary from millions of training samples~\cite{mairal2009online,mairal2010online}.
-More recently, Liu et al.~\cite{liu-2018-first} proposed an online learning based CSC model, and analyzed different solvers and strategies when implementing it.
+Later on, online learning strategies were synergetic with sparse coding, which was then scaled up for learning dictionary from millions of training samples~\cite{mairal2009online,mairal2010online}, and for large-scale matrix factorization with an additionally introduced subsampling strategy~\cite{mensch2016dictionary}.
+More recently, Liu et al.~\cite{liu-2018-first} and Wang et al.~\cite{wang2018scalable} separately proposed similar online learning frameworks for the CSC model, alleviating the memory issues arise in batch-based CSC model on large datasets.
 
 {\bfseries Contributions.} We mainly make three contributions in this work.
-First of all, we introduce a randomization strategy in the subproblem of updating sparse codes and solve the entire problems in spatial domain.
-It demonstrates that the proposed stochastic spatial-domain solver, with a reasonably selected subsampling probability, outperforms the state-of-the-art frequency-domain solvers with less computation time (per iteration), and also achieves faster convergence (less number of iterations).
+First of all, we introduce a randomization strategy for the CSC model and solve the entire problems in spatial domain.
+It demonstrates that the proposed stochastic spatial-domain solver, with a reasonably selected subsampling rate, outperforms the state-of-the-art frequency-domain solvers with regard to computing efficiency.
 We then formulate an online-learning version of the proposed algorithm, and it shows dramatic runtime improvement over precedent online CSC methods, as well as producing comparable outcomes.

### 2018-10-25 cvpr2019/Results.tex
add paper

--- 2018-05-18 nips2018/Results.tex
@@
 The online-mode algorithms are then adapted to one thousand $100 \times 100$ image patches randomly picked up from ImageNet~\cite{deng2009imagenet}.
+Note that batch-based CSC commonly can only handle less than 100 images simultaneously.
 The dictionary dimension size is set to $11 \times 11 \times 100$ in all experiments except for over-complete dictionary.
@@
 
-\subsection{Subsampling Strategy}
-
-{\bfseries Convergence.} Comparisons of the convergence between the proposed method (SBCSC) and the state-of-the-art batch-mode algorithm~\cite{heide2015fast} are shown in Fig.\ \ref{fig:subsampleResult}.
-A different selection of the subsampling probability reveals that the proposed strategy will slightly influence the convergence and the training objective of the minimization problem.
-Specifically, the less subsampled, the relatively slower convergence and the higher objective will be obtained.
-On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solver for one iteration.
-We observe that a subsampling rate between $0.1$ and $0.2$ delivers empirically good enough convergence in our settings, as well as achieving at least $3 \times$ speedup.
-In general, the proposed method converges within 10 iterations, while the comparable method requires roughly 13 iterations to reach convergence.
-Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
-In summary, comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate of $10\%$ not only spends two times less processing time per iteration, but also needs fewer iterations to converge.
-Please see supplementary materials for additional experimental results.
-
 \begin{figure}[h]
 \centering
-\begin{subfigure}{0.6\textwidth}
+\begin{subfigure}{0.5\textwidth}
   \includegraphics[width=1\linewidth]{figure/iteVSobj.pdf}
 \end{subfigure}
-\begin{subfigure}{0.3\textwidth}
+
+\begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/timeVSobj.pdf}
+\end{subfigure}
+
+\begin{subfigure}{0.23\textwidth}
   \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
 \end{subfigure}
-
-\begin{subfigure}{0.6\textwidth}
-  \includegraphics[width=1\linewidth]{figure/timeVSobj.pdf}
-\end{subfigure}
-\begin{subfigure}{0.3\textwidth}
+\begin{subfigure}{0.23\textwidth}
   \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
@@
 
-\caption{Left: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling probability, all of which are performed on the fruit dataset.
-Right: Learned filters by the proposed method with $p=0.1$ and the comparable method.
-In these represented learned filters, our method learns more smooth Gabor-like filters and less number of noise-like filters.
+\caption{Top: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling rate, all of which on performed on fruit dataset.
+Convergence is evaluated by monitoring the objective value of eq.~\ref{eq:CSCmodel} on training images versus iterations and time, respectively.
+Bottom: Learned filters by the proposed method with $p=0.1$ and the comparable method.
+In these represented learned filters, our method learns more smooth Gabor-like filters and less number of noise-like filters with the same $\lambda$.
 Beyond this, it runs faster with regard to each iteration and shows better convergence behavior.}
@@
 
-{\bfseries Reconstruction}.
-The learned filters by SBCSC with subsampling rate $0.1$ are shown on the right hand side of Fig.\ \ref{fig:subsampleResult}.
-For a visual comparison, we also show the filters learned from the competing method.
-As can be observed, both of them learn some seemingly similar Gabor-like filters.
-While after zooming, it can be seen that our learned Gabor-like filters have less impure structures.
-Moreover, the comparable dictionary contains a number of noise-like filters, which are rarely existed in ours.
-We then demonstrate the effectiveness of the reconstructed filters in the application of image inpainting, which refers to reconstructing a full image from partial measurements.
-A numerical comparison of the reconstruction quality is shown in Fig.\ \ref{fig:PSNRrecon}.
-The filters learned by the proposed method not only show more visually decent structures and less specific features, but also demonstrate its capability to better reconstruct partial observed images.
-In addition to that, the learning process only takes about $40\%$ of the execution time of the comparison.
-
-\begin{figure}[h]
+\begin{figure*}[h]
+    \centering
     \includegraphics[width=1\textwidth]{figure/reconImage.pdf}
-    \\
-    \\
-    \resizebox{1\linewidth}{!}{
+    \resizebox{0.9\linewidth}{!}{
         \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
@@
 Note that none of the testing images are in the training sets.} \label{fig:PSNRrecon}
-\end{figure}
+\end{figure*}
+
+\subsection{Subsampling Strategy}
+
+{\bfseries Convergence.} Comparisons of the convergence between the proposed method (SBCSC) and the state-of-the-art batch-mode algorithm~\cite{heide2015fast} are shown in Fig.\ \ref{fig:subsampleResult}.
+A different selection of the subsampling rate reveals that the proposed strategy will slightly influence the convergence and the training objective of the minimization problem.
+Specifically, the more subsampled, the relatively slower convergence and the higher objective will be obtained.
+On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solver for one iteration.
+We observe that a subsampling rate between $0.1$ and $0.2$ delivers empirically good enough convergence in our settings, as well as achieving at least $3 \times$ speedup.
+In general, the proposed method with various subsampling rates converges at around 10-12 iterations in all testing cases, acting similar to the competing methods.
+Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
+In summary, comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate $10\%$ reduces the computation time by a factor of two for the tested example.
+Please see supplementary materials for additional experimental results.
+
+{\bfseries Reconstruction}.
+The learned filters by SBCSC with subsampling rate $0.1$ are shown in the bottom of Fig.\ \ref{fig:subsampleResult}.
+For a visual comparison, we also show the filters learned from the competing method (bottom left of Figure 3 in~\cite{heide2015fast}.
+As can be observed, both of them learn some seemingly similar Gabor-like filters.
+While after zooming (we also show zoom-in comparisons in supplement), it can be seen that our learned Gabor-like filters have less impure structures.
+Moreover, the compared dictionary contains a number of noise-like filters, which are rarely existed in ours.
+We then demonstrate the effectiveness of the reconstructed filters in the application of image inpainting, which refers to reconstructing a full image from partial measurements.
+A numerical comparison of the reconstruction quality is shown in Fig.\ \ref{fig:PSNRrecon}.
+The filters learned by the proposed method not only show more visually decent structures and less specific features, but also demonstrate its capability to better reconstruct partial observed images with respect to the PSNR value.
+In addition to that, the learning process only takes about $50\%$ of the execution time than the comparison.
 
@@
 
-{\bfseries Convergence.} Unlike the batch-based learning approaches, the training loss objective of the entire dataset cannot be evaluated during the online learning processes,since each training step only draws one or a few of the data samples.
-Nevertheless, we can evaluate the learning process on testing images.
+{\bfseries Convergence.} Unlike the batch-based learning approaches which evaluate its convergence by monitoring the objective value on training datasets, a common way to evaluate the learning process of online learning model is to monitor its objective value on testing images.
 The testing objectives of the proposed method (SOCSC) and prior published online frequency-domain CSC method~\cite{liu-2018-first}, with respect to iterations, are shown in Fig.\ \ref{fig:onlineSmall}.
-In the same figure, we also keep track of the capability of the updated filters during the process of learning to sparsely represent the testing images, which is demonstrated by the time evolution of PSNR.
+In the same figure, we also keep track of the capability of the updated filters during the learning process to sparsely represent the testing images, which is demonstrated by the time evolution of PSNR.
 These two approaches stop at optimum positions with close testing objective values, though, they exhibit slightly different convergence behaviors with respect to iterations.
-The final testing PSNR values for both methods also reveal the similar reconstruction performance of the learned filters.
+The final testing PSNR values for both methods also reveal a similar reconstruction performance of the learned filters.
 As for the runtime comparison, the proposed method runs at least 5 times faster than the comparable method.
@@
 % Further numerical comparison will be reported in the next section.
+
+{\bfseries Over-complete dictionary.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (the number of filters is more than the degrees of freedom).
+One of the reasons could be that most of the prior work is batch-based, thus learning over-complete dictionary from small datasets would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability (we verify this explanation in supplement).
+The proposed online-based learning strategy (SOCSC) can overcome this issue by scaling the model up to arbitrary sample sizes.
+
+We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.\ \ref{fig:overCompleteDic} .
+For a visual comparison, 100 learned filters by the same algorithm and its comparable approach~\cite{liu-2018-first} are also represented.
+As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method takes $5 \times$ less training time than the competitive one.
+As for the learned over-complete dictionary, it is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
+This additional feature information would play an essential role to better reconstruct the natural images, which can be demonstrated by the results of reconstruction quality shown in the same figure.
+
+We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
+The top of Fig.\ \ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches ($K=100$).
+However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement, with regard to PSNR, to have a sparse representation of the testing images during the learning process.
+This is also verified by applying these learned dictionaries to the image inpainting application as discussed above.
 
@@
 \caption{The experiments are performed on fruit dataset, and each iteration randomly choose one image from the training sets.
-Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
-Right: Testing PSNR with respect to execution time.
+Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
+Bottom: Testing PSNR with respect to execution time.
 While the quality of the output is comparable, our method achieves $5 \times$ speedup.}
@@
 
-{\bfseries Over-complete dictionary.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (the number of filters is more than the degrees of freedom).
-One of the reasons could be that most of the prior work is batch-based, thus learning over-complete dictionary from small datasets would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability (we verify this explanation in supplement).
-The proposed online-based learning strategy (SOCSC) can overcome this issue by scaling the model up to arbitrary sample sizes.
-
-We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.\ \ref{fig:overCompleteDic} .
-For a visual comparison, 100 learned filters by the same algorithm and its comparable approach~\cite{liu-2018-first} are also represented.
-As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method takes $5 \times$ less training time than the competitive one.
-As for the learned over-complete dictionary, it is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
-This additional feature information would play an essential role to better reconstruct the natural images, which can be demonstrated by the results of reconstruction quality shown in the same figure.
-
-\begin{figure}[h]
+\begin{figure*}[h]
 \begin{minipage}{0.4\textwidth}
@@
 \includegraphics[width=0.97\linewidth]{figure/online400-filter.pdf}
+\vspace*{2mm}
 \end{minipage}
-    \\
-    \\
-    \\
-    \resizebox{1\linewidth}{!}{
+\begin{minipage}{1\textwidth}
+    \centering
+    \resizebox{0.8\linewidth}{!}{
         \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
@@
         \end{tabular} }
-
+\end{minipage}
 \caption{Filters learned from 1000 images by our method (SOCSC) and the state-of-the-art online method~\cite{liu-2018-first}, and their corresponding reconstruction quality using the same hyperparameter settings as in Fig.\ \ref{fig:PSNRrecon}.
@@
 \label{fig:overCompleteDic}
-\end{figure}
-
-We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
-The left hand side of Fig.\ \ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches.
-However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement, with regard to PSNR, to have a sparse representation of the testing images during the learning process.
-This is also verified by applying these learned dictionaries to the image inpainting application as discussed above.
-
-\begin{figure}[h]
-\centering
-\begin{subfigure}{0.41\textwidth}
-  \includegraphics[width=1\linewidth]{figure/overComplete-ite.pdf}
-\end{subfigure} 
-\begin{subfigure}{0.58\textwidth}
-  \includegraphics[width=1\linewidth]{figure/minibatch.pdf}
-\end{subfigure}
-
-\caption{Left: Testing PSNR for the comparable method~\cite{liu-2018-first} with $K=100$, and our method (SOCSC) with $K=100$ and $K=400$, respectively.
-Every iteration draws a single image from those 1000 image patches.
-Right: Testing PSNR for SOCSC ($K=400$) with varying values of $\eta$.
-The learned filters are examined on the test sets every $2^i$ iterations and also at the last iteration, where $i=0,1,\dots$.
-Note that all the results are generated by a single-core program.}
-\label{fig:overComDicAndMinibatch}
-\end{figure}
+\end{figure*}
 
@@
 Since computing sparse codes is a data-independent process, this mini-batched approach can be further accelerated by a distributed computing system.
+\begin{figure}[h]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/overComplete-ite.pdf}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/minibatch.pdf}
+\end{subfigure}
+
+\caption{Top: Testing PSNR for the comparable method~\cite{liu-2018-first} with $K=100$, and our method (SOCSC) with $K=100$ and $K=400$, respectively.
+Every iteration draws a single image from those 1000 image patches.
+Bottom: Testing PSNR for SOCSC ($K=400$) with varying values of $\eta$.
+The learned filters are examined on the test sets every $2^i$ iterations and also at the last iteration, where $i=0,1,\dots$.
+Note that all the results are generated by a single-core program.}
+\label{fig:overComDicAndMinibatch}
+\end{figure}

### 2018-10-25 cvpr2019/SCSCmodel.tex
add paper

\section{Stochastic Convolutional Sparse Coding}
\subsection{The Model}
Based on the specific sparsity property of the codes, we propose a variant of the CSC model using subsampling strategy,
and formulate the following modified minimization problem:
\begin{align}
    &\minimize{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k(\code_k) \|_1  \nonumber \\
    &\text{subject to} ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
\end{align}
where $\mathcal{M}_k(\code_k)$ is the operation to subsample the corresponding code $\code_k$ following a Bernoulli distribution with probability $p$. The probability $p$ controls the fraction of the sparse codes that will be considered by the solver, and in the case of $p=1$, the proposed model is identical with the classical CSC model. If $p<1$, the algorithm only solves the sparse codes at chosen positions in each iteration, and accordingly, the update of dictionary $d$ is based on the selected portion of the sparse codes. Similar to solving the classical CSC problem, we can apply coordinate descent algorithm, alternating on subproblems of $\mathcal{M}(\code)$ and $\filter$, to solve the above optimization problem. Specifically, the modified minimization problem for $\code$ can be formulated as:
\begin{equation} \label{eq:updatingCode}
    \code_{opt} = \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^\top)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
\end{equation}
where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.  Matrix $\mask$ is a $\mathbb{R}^{pDk \times DK}$ random diagonal matrix with ones on the entries corresponding to the sampled sparse codes and zeros elsewhere, performing the function of $\mathcal{M}(\code)$. Due to the introduced subsampling matrix, the convolution operator will not hold, hence it cannot be directly solved in the frequency domain. Owing to the subsampling strategy, the number of variables that needs to be computed for this subproblem is $pDK$ instead of $DK$, and this can lead to a reduction of the computation time up to a factor of $\frac{1}{p}$ when solving it in spatial domain.

After obtaining the subsampled sparse codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
\begin{equation} \label{eq:updatingFilter}
\begin{split}
   & \filter_{opt} = \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2 \\
   & \text{subject to}  ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\},
\end{split}
\end{equation}
where $\Code= [\Code_1, \dots, \Code_K] \in \mathbb{R}^{D \times MK}$ is a concatenated matrix, and $\Code_k$ is constructed from the associated $\code_k$, $\filter= [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$. In the common settings for CSC problem, $M \ll D$, hence there is no need to perform subsampling on dictionary.

The work of~\cite{mensch2016dictionary} also applies the stochastic subsampling strategy for dictionary learning, while the subsampling is randomly performed on the observed data, differing from that of our proposed. One can think of our proposed randomization approach as a variant of the stochastic Frank-Wolfe algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which a subset of the variables are randomly extracted based on a certain probability distribution at each iteration. For the proposed algorithm, each iteration extracts ($pDK+MK$) variables, where $pDK$ variables are randomly picked out from $DK$ variables with identical probability and the rest remain unchanged. Owing to the highly sparse codes, the original signals can still be represented by a portion of the codes with a reasonable subsampling rate. Herein, unlike the stochastic Frank-Wolfe algorithm that generally requires more iterations to reach convergence, the convergence of the proposed algorithm will not be significantly affected by the subsampling manipulation. This will be experimentally verified in Section~\ref{sec:result}.

The proposed subsampling strategy will be implemented in the fashions of {\em batch mode} (stochastic batch CSC) and {\em online mode} (stochastic online CSC).

\subsection{Stochastic Batch CSC (SBCSC)}
We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the uniform probability for one code been selected. We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this work, where $p=1$ indicates no subsampling, and $p=0.05$ indicates a subsampling rate of $5\%$. Problem~\ref{eq:updatingCode} is the standard LASSO, which can be solved by plenty of optimization frameworks. We found that solving it by ADMM delivers a good balance for computation time and convergence within a moderate number of iterations. Specifically, the data fitting term and the $L_1$ penalty term are split, forming two separate substeps. The first substep is a quadratic programming (QP) problem, and we can either cache the matrix factorization by Cholesky decomposition (when $N$ is relatively large), or solve it by Conjugate Gradient (when $N$ is relatively small). The second substep can be solved by a point-wise shrinkage operation. Problem~\ref{eq:updatingFilter} is a quadratic constrained quadratic programming (QCQP) problem, and it can be efficiently solved by projected block coordinate decent. Empirically, a single iteration is enough with $\filter$ computed in previous iteration as a warm start. We set the hyperparameters $\lambda=1$, the ADMM iteration fixed to 10, the augmented Lagrangian penalty $\rho$ to $10 \lambda$, and the over-relaxation strategy within ADMM is applied with $\alpha = 1.8$. For a detailed description of the above two solvers, please refer to the supplement.

Every outer loop of SBCSC involves all of the training images, thus it would be computationally expensive to process them simultaneously and also runs out of memory quickly with the increase of the number of images. The batch-based learning algorithm lacks of the capability to scale up to very large datasets or to handle dynamically changed training data.

\begin{algorithm}[H]
\caption{SBCSC} \label{algo:SBCSC}
\begin{algorithmic}[1]
\State $\text{Initialize } \filter, ~p$
\While {not converge}
    \State $ \text{Randomly sample }\code \text{ with rate } p $
    \For{i=1 to N}
        \State $ \text{Update } \code^i \text{ by solving problem~(\ref{eq:updatingCode}})$
    \EndFor
    \State $\text{Update } \filter \text{ by solving problem~(\ref{eq:updatingFilter}})$
\EndWhile
\end{algorithmic}
\end{algorithm}

\subsection{Stochastic Online CSC (SOCSC)}
We can further tackle the proposed problem in the online fashion for a gain of scalability. In the online learning setting as shown in Algorithm~\ref{algo:SOCSC}, each iteration only draws one or a subset (mini-batch) of the total training images, hence the complexity per loop is independent of the training sample size. Then, given the sampled image $\signal^t$ at $t$-th iteration, we can compute the corresponding subsampled sparse codes $\code^t$ by
\begin{equation} \label{eq:updatingCodeOnline}
    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} (\mask^t)^\top)(\mask^t \code) \|_2^2 + \lambda \|\mask^t \code\|_1,
\end{equation}
where $\Filter^{t-1}$ is constructed from the dictionary learned by $(t-1)$th iteration, and $\mask^t$ is the subsample matrix at current iteration. After obtaining the sparse codes, the dictionary is updated by:
\begin{equation}
\begin{split}
    &\filter^t = \minimize{\filter} \frac{1}{2t}\sum_{i=1}^{t} \|\signal^i - \Code^i \filter \|_2^2 \\
    &\text{subject to} \quad \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\}.
\end{split}
\end{equation}
Notice that updating dictionary involves all of the past training images and sparse codes. As shown in~\cite{mairal2009online,mairal2010online}, we can get rid of explicitly storing those data by introducing two surrogate matrices $\surC \in \mathbb{R}^{KM \times KM}$ and $\surB \in \mathbb{R}^{KM \times 1}$, which carry all of the required information for updating $\filter$, and can be iteratively updated by:
\begin{equation} \label{eq:updateSur}
\begin{split}
    \surC^t  = \frac{t-1}{t} \surC^{t-1} + \frac{1}{t}(\Code^t)^\top \Code^t \\
    \surB^t  = \frac{t-1}{t} \surB^{t-1} + \frac{1}{t}(\Code^t)^\top \signal^t
\end{split}
\end{equation}
If so, the updated dictionary can be obtained by solving:
\begin{equation} \label{eq:updatingFilterOnline}
\begin{split}
    & \filter^t = \minimize{\filter} \frac{1}{2} \filter^\top \surC^t\filter - \filter^\top \surB^t \\& \text{subject to} \quad \|\filter_k\|_2^2 \leq 1 ~ \forall k \in \{1,\dots,K\}.
\end{split}
\end{equation}
Problem~\ref{eq:updatingCodeOnline} and problem~\ref{eq:updatingFilterOnline} are solved in the same way as that for SBCSC.

\begin{algorithm}[H]
\caption{SOCSC} \label{algo:SOCSC}
\begin{algorithmic}[1]
\State $\text{Initialize} ~ t=0, ~\filter^t, ~p, ~\surC^t = 0, ~\surB^t = 0$
\While {not converge}
    \State $t \gets t+1$
    \State $ \text{draw } \signal^t \text{ from training images} $
    \State $ \text{Randomly sample }\code^t \text{ with rate } p $
    \State $ \text{Compute } \code^t \text{ by solving problem~(\ref{eq:updatingCodeOnline}) using } \filter^{t-1}$
    \State Compute $\surC^t$ and $\surB^t$ by eq~(\ref{eq:updateSur})
    \State Compute $\filter^t$ by solving problem~(\ref{eq:updatingFilterOnline})
\EndWhile
\end{algorithmic}
\end{algorithm}

\subsection{Complexity Analysis}
Recall that $D$ is the number of pixels for a single image, $K$ is the number of filters, and $M$ is the size of the filter support. For the state-of-the-art frequency-domain solvers, it has the time complexity $\mathcal{O}(K^2D + KDlog(D))$ for a single data pass.

Compared with SBCSC, updating $\code$ (suppose we solve it by Conjugate Gradient) has the time complexity of $\mathcal{O}(pKMD \sqrt{\tau})$ where $pKMD$ is the number of non-zero elements in $(\Filter \mask^\top)$ and $\tau$ is the condition number of $(A^\top A + \rho I)$ where $A = \Filter \mask^\top$. With a reasonable selection of the subsampling rate, this time complexity is comparable with that of frequency-domain solvers. As for updating $\filter$, it takes $\mathcal{O}(K^2M^2)$ time. This is comparable to $\mathcal{O}(K^2D)$ in common CSC settings ($M \ll D$), while it requires multiple iterations in frequency domain and only one pass required by the proposed method, which greatly saves the time. Overall, the proposed method has the time complexity of $\mathcal{O}(pKMD \sqrt{\tau} + K^2M^2)$.

The time complexity of SOCSC is similar to that of SBCSC, apart from two additional steps to update the surrogate matrices. Updating $\surC$ and $\surB$ involves computing $\Code^\top\Code$ and $\Code^\top x$. Though $\Code$ has the dimensions of $D \times KM$, it is a highly sparse matrix with only $\mathcal{O}(D)$ non-zero elements. Therefore, the total time complexity will not be obviously affected.

### 2018-10-25 cvpr2019/egpaper_for_review.tex
add paper

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{wrapfig}
\usepackage{subcaption}

\usepackage{caption}
\captionsetup[table]{position=bottom}

\usepackage{array}
\usepackage{epstopdf}
\usepackage{cuted}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\input{macro}
\begin{document}

%%%%%%%%% TITLE
\title{Stochastic Convolutional Sparse Coding}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
The minimization problems formulated in Convolutional Sparse Coding (CSC) have been solved in frequency domain by modern approaches owing to the improved computing efficiency. However, solving the problem in frequency domain automatically assumes circular boundary conditions, and also it is restricted by imposing modern optimization strategies for this specific problem. In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes. Afterwards, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes. In both cases, we show experimentally that the proposed method outperforms the state-of-the-art frequency-domain solvers with a reasonable selection of the subsampling rate. At last, we learn the over-complete dictionary from large-scale datasets, which demonstrates a better sparse representation of the natural images on account of more abundant learned image features.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{Introduction}

\input{CSCmodel}

\input{SCSCmodel}

\input{Results}

\input{Conclusion}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\clearpage
\appendix

\input{supplement}

\end{document}

### 2018-10-25 cvpr2019/supplement.tex
add paper

--- 2018-05-18 nips2018/supplement.tex
@@
-%\part*{Supplementary Material\\ Stochastic Convolutional Sparse Coding}
+\begin{strip}
+\begin{center}
+{\Large \bf Stochastic Convolutional Sparse Coding \\ Supplementary Material }
+\end{center}
+\end{strip}
+
+\section{Solvers for LASSO and QCQP}
+Algorithm~\ref{algo:ADMMLasso} is used to optimize a LASSO problem in the following form:
+\begin{equation}
+    \minimize{\code} \frac{1}{2}\|\signal - \Filter \code \|_2^2 + \lambda\| \code \|_1
+\end{equation}
+
+\begin{algorithm}
+\caption{ADMM framework for solving LASSO} \label{algo:ADMMLasso}
+\begin{algorithmic}[1]
+    \For{$s=1$ to $S$}
+        \State // z-update step (quadratic programming)
+        \State $\code^{s+1} \gets (\Filter ^ \top \Filter + \rho \Id )^{-1}(\Filter^\top \signal + \rho(\Vector{y}^s - \Vector{q}^s ) )$
+        \State // y-update step (soft thresholding)
+        \State $\Vector{y}^{s+1} \gets (\code^{s+1}+\Vector{q}^{s} - \frac{\lambda}{\rho})_{+} ~ - ~ (-\code^{s+1}-\Vector{q}^{s} - \frac{\lambda}{\rho})_{+}$
+        \State // scaled dual variables update
+        \State $\Vector{q}^{s+1} \gets \bold{q}^{s}+\code^{s+1}-\Vector{y}^{s+1}$
+    \EndFor
+\end{algorithmic}
+\end{algorithm}
+$S$ is the total number of ADMM iteration. $\Vector{y}$ is the introduced slack variable, $\Vector{q}$ is the scaled dual variable, and $\rho$ is the augmented Lagrangian penalty.
+
+Algorithm~\ref{algo:BCDQCQP} is used to optimize a QCQP problem in the following form:
+\begin{equation}
+\begin{split}
+    \minimize{\filter} & \frac{1}{2}\|\signal - \Code \filter \|_2^2 \\
+    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
+\end{split}
+\end{equation}
+
+\begin{algorithm}
+\caption{Projected Block Coordinate Descent for solving QCQP} \label{algo:BCDQCQP}
+\begin{algorithmic}[1]
+\State $\Vector{r} \gets \signal - \Code \filter $
+\While {not converge}
+    \For{$k=1$ to $K$}
+        \State $ \filter^{\ast}_k \gets \filter_k + \Code_k ^ \top \Vector{r} ~ / ~ L_k $
+        \State $ \filter^{\ast}_k \gets \filter^{\ast}_k ~ / ~ \text{max}( \|\filter^{\ast}_k\|,1 ) $
+        \State $ \Vector{r} ~~ \gets \Vector{r} + \Code_k( \filter_k - \filter^{\ast}_k ) $
+    \EndFor
+    \State  $ \filter \gets \filter^{\ast} $
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+$L_k$ is the Lipschitz constant of $\Code_k^\top \Code_k$.
 
@@
 \begin{figure}[h]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
+\end{subfigure}
+
+\caption{Experimental results obtained on city dataset.
+Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
+Bottom: Testing PSNR with respect to execution time.}
+\label{fig:onlineSmall-city}
+\end{figure}
+
+\begin{figure*}[h]
 \begin{subfigure}{0.5\textwidth}
@@
 
-\begin{subfigure}{0.48\textwidth}
+\centering
+\begin{subfigure}{0.49\textwidth}
   \includegraphics[width=1\linewidth]{figure/batchCity100.pdf}
 \end{subfigure}
-\begin{subfigure}{0.48\textwidth}
+\begin{subfigure}{0.49\textwidth}
   \includegraphics[width=1\linewidth]{figure/heideCity100.pdf}
@@
 
-    \resizebox{1\linewidth}{!}{
+    \resizebox{0.8\linewidth}{!}{
         \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
@@
 \label{fig:subsampleResult-city}
-\end{figure}
+\end{figure*}
 
@@
 Similar to the results presented in Fig.\ \ref{fig:onlineSmall}, our method obtains comparable outcomes, meanwhile, achieves roughly $5 \times$ speedup.
-
-\begin{figure}[h]
-\centering
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
-\end{subfigure}
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
-\end{subfigure}
-
-\caption{Experimental results obtained on city dataset.
-Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
-Right: Testing PSNR with respect to execution time.}
-\label{fig:onlineSmall-city}
-\end{figure}
 
@@
 
-\begin{figure}[h]
+\begin{figure*}[h]
 \centering
-  \includegraphics[width=0.7\linewidth]{figure/heide400-supple.pdf}
-  \includegraphics[width=0.7\linewidth]{figure/online400-supple.pdf}
+  \begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/heide400-supple.pdf}
+  \end{subfigure}
+  \vspace{0.2cm}
+  \begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=1\linewidth]{figure/online400-supple.pdf}
+  \end{subfigure}
   \vspace{0.2cm}
 
-    \resizebox{1\linewidth}{!}{
+    \resizebox{0.8\linewidth}{!}{
         \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
@@
   \label{fig:overCompleteDic-dataset}
-\end{figure}
+\end{figure*}

### 2018-10-28 cvpr2019/Conclusion.tex
minor edits

@@
 Since the subproblem of updating the code is a highly sparse LASSO, other specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in~\cite{johnson2017stingycd}, which solves the LASSO problem by coordinate descent and skips unnecessary updates by the method of safe screening~\cite{ghaoui2012Swfe}.
-Moreover, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the images and the sparse codes.
+
+Furthermore, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the images and the sparse codes.
 Notice that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies (including the proposed one).
-In addition, we have shown the capability of the developed online algorithm to learn representative over-complete dictionary from large datasets, and the availability of the dictionary is further verified by the application of image inpainting.
+
+We have also shown the capability of the developed online algorithm to learn representative and meaningful over-complete dictionary from arbitrary large datasets, and the availability of the dictionary is further verified by the application of image inpainting.
 It can be foreseen that this capability has widespread applications in the audio and image related tasks, and higher dimensional signal processing.
+The source code for SBCSC and SOCSC is attached in the supplement for reference.

### 2018-10-28 cvpr2019/Results.tex
minor edits

@@
   \includegraphics[width=1\linewidth]{figure/timeVSobj.pdf}
+  \vspace*{1mm}
 \end{subfigure}
@@
 \caption{Top: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling rate, all of which on performed on fruit dataset.
-Convergence is evaluated by monitoring the objective value of eq.~\ref{eq:CSCmodel} on training images versus iterations and time, respectively.
+Convergence is evaluated by monitoring the objective value of Eq.~\ref{eq:CSCmodel} on training images versus iterations and time, respectively.
 Bottom: Learned filters by the proposed method with $p=0.1$ and the comparable method.
@@
 Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
-In summary, comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate $10\%$ reduces the computation time by a factor of two for the tested example.
+In summary, the convergence behaviors of the proposed algorithm is only slightly influenced by the subsampling strategy within the testing subsampling rates.
+Comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate of $0.1$ reduces the computation time by a factor of two for the tested example.
 Please see supplementary materials for additional experimental results.
@@
 The learned filters by SBCSC with subsampling rate $0.1$ are shown in the bottom of Fig.\ \ref{fig:subsampleResult}.
-For a visual comparison, we also show the filters learned from the competing method (bottom left of Figure 3 in~\cite{heide2015fast}.
+For a visual comparison, we also show the filters learned from the competing method (bottom left of Figure 3 in~\cite{heide2015fast}).
 As can be observed, both of them learn some seemingly similar Gabor-like filters.
@@
 
-{\bfseries Convergence.} Unlike the batch-based learning approaches which evaluate its convergence by monitoring the objective value on training datasets, a common way to evaluate the learning process of online learning model is to monitor its objective value on testing images.
+{\bfseries Convergence.} Unlike the batch-based learning approaches which evaluate its convergence by monitoring the objective value on training datasets, a common way to evaluate the learning process of online learning model is to monitor its objective value on testing datasets.
 The testing objectives of the proposed method (SOCSC) and prior published online frequency-domain CSC method~\cite{liu-2018-first}, with respect to iterations, are shown in Fig.\ \ref{fig:onlineSmall}.
@@
 As for the runtime comparison, the proposed method runs at least 5 times faster than the comparable method.
-Supplement shows additional comparisons for different datasets.
+Supplement shows additional comparisons for the other dataset.
 
@@
 
-{\bfseries Over-complete dictionary.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (the number of filters is more than the degrees of freedom).
+{\bfseries Over-complete dictionary.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (number of the dictionary is more than its degrees of freedom).
 One of the reasons could be that most of the prior work is batch-based, thus learning over-complete dictionary from small datasets would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability (we verify this explanation in supplement).
 The proposed online-based learning strategy (SOCSC) can overcome this issue by scaling the model up to arbitrary sample sizes.
-
-We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.\ \ref{fig:overCompleteDic} .
-For a visual comparison, 100 learned filters by the same algorithm and its comparable approach~\cite{liu-2018-first} are also represented.
-As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method takes $5 \times$ less training time than the competitive one.
-As for the learned over-complete dictionary, it is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
-This additional feature information would play an essential role to better reconstruct the natural images, which can be demonstrated by the results of reconstruction quality shown in the same figure.
-
-We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
-The top of Fig.\ \ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches ($K=100$).
-However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement, with regard to PSNR, to have a sparse representation of the testing images during the learning process.
-This is also verified by applying these learned dictionaries to the image inpainting application as discussed above.
 
@@
 
-\caption{The experiments are performed on fruit dataset, and each iteration randomly choose one image from the training sets.
-Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
+\caption{The experiments are performed on fruit dataset, and each iteration randomly choose one samples from the training datasets.
+Top: Convergence of the test set objectives (objective value of Eq.~\ref{eq:CSCmodel} on testing datasets) for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
 Bottom: Testing PSNR with respect to execution time.
@@
 
+We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.\ \ref{fig:overCompleteDic} .
+For a visual comparison, 100 learned filters by the same algorithm and its comparable approach~\cite{liu-2018-first} are also represented.
+As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method takes $5 \times$ less training time than the competitive one.
+As for the learned over-complete dictionary, it is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
+This additional feature information would play an essential role to better reconstruct the natural images, which can be demonstrated by the results of reconstruction quality shown at the bottom of the same figure.
+
+We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
+The top of Fig.\ \ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches ($K=100$).
+However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement, with regard to PSNR, to have a sparse representation of the testing images during the learning process.
+This is also verified by applying these learned dictionaries to the image inpainting application as discussed above.
+
 {\bfseries Mini-batching.} In practice, a mini-batching strategy would be preferred in order to gain advantages from modern parallel computing architectures.
@@
 In the proposed online algorithm (SOCSC), the time complexity for one step dictionary update will not increase linearly with the increase of $\eta$.
-Concretely speaking, updating $\code$ is implemented by Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
+Concretely speaking, updating $\code$ can be implemented by caching the Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
 Herein, the complexity for doing updating $\code$ $\eta$ times all together is cheaper than $\eta$ times the complexity of updating one $\code$.
-In addition, the time complexity for updating $\filter$ is not affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
-One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this is not dominant in the runtime.
-The runtime comparisons for various mini-batch sizes are shown in Fig.\ \ref{fig:overComDicAndMinibatch}.
-Note that larger $\eta$ will result in less number of iterations to process all 1000 images.
+In addition, the time complexity for updating $\filter$ is not linearly affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
+One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this step is not dominant in the runtime.
+
+The runtime comparisons for various mini-batch sizes are shown in the bottom of Fig.\ \ref{fig:overComDicAndMinibatch}.
+Note that larger $\eta$ will result in less number of iterations to process all 1000 samples.
 The plots show that a larger mini-batch size will generally lead to a greater progress in first few training steps, though it takes additional running time and memory.
 Overall, mini-batched updates provides a more runtime efficient learning process in the online-based CSC model, and according to the obtained experimental results, $\eta=20$ achieves one magnitude speedup over $\eta=1$ to reach a condition with the same level convergence on a single-core program.
-Since computing sparse codes is a data-independent process, this mini-batched approach can be further accelerated by a distributed computing system.
+Since computing sparse codes is a data-independent process, this mini-batched approach can be further accelerated in a distributed-computing system.
 \begin{figure}[h]

### 2018-10-28 cvpr2019/SCSCmodel.tex
minor edits

@@
 \subsection{The Model}
-Based on the specific sparsity property of the codes, we propose a variant of the CSC model using subsampling strategy,
+Based on the specific sparsity property of the codes, we propose a variant of the CSC model applying subsampling strategy on the codes,
 and formulate the following modified minimization problem:
@@
 where $\mathcal{M}_k(\code_k)$ is the operation to subsample the corresponding code $\code_k$ following a Bernoulli distribution with probability $p$.
-The probability $p$ controls the fraction of the sparse codes that will be considered by the solver, and in the case of $p=1$, the proposed model is identical with the classical CSC model.
-If $p<1$, the algorithm only solves the sparse codes at chosen positions in each iteration, and accordingly, the update of dictionary $d$ is based on the selected portion of the sparse codes.
-Similar to solving the classical CSC problem, we can apply coordinate descent algorithm, alternating on subproblems of $\mathcal{M}(\code)$ and $\filter$, to solve the above optimization problem.
+The probability value $p$ controls the percentage of the sparse codes that will be considered by the solver.
+Basically, in the case of $p=1$, the proposed model is identical with the classical CSC model.
+When $p<1$, otherwise, the algorithm only solves a subset of the sparse codes at chosen positions in each iteration, and accordingly, the update of dictionary $d$ is based on the selected portion of the sparse codes.
+Similar to solving the classical CSC problem, we can apply coordinate descent algorithm, alternating on subproblems of $\mathcal{M}(\code)$ and $\filter$, to solve the above bi-convex optimization problem.
 Specifically, the modified minimization problem for $\code$ can be formulated as:
@@
 where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
-Matrix $\mask$ is a $\mathbb{R}^{pDk \times DK}$ random diagonal matrix with ones on the entries corresponding to the sampled sparse codes and zeros elsewhere, performing the function of $\mathcal{M}(\code)$.
-Due to the introduced subsampling matrix, the convolution operator will not hold, hence it cannot be directly solved in the frequency domain.
-Owing to the subsampling strategy, the number of variables that needs to be computed for this subproblem is $pDK$ instead of $DK$, and this can lead to a reduction of the computation time up to a factor of $\frac{1}{p}$ when solving it in spatial domain.
+Therefore, each part of $\Filter$ is a Toeplitz matrix.
+Matrix $\mask$
+is a $\mathbb{R}^{pDk \times DK}$ random diagonal matrix with ones on the entries corresponding to the sampled sparse codes and zeros elsewhere, performing the function of 
+$\mathcal{M}(\code)$. Matrix $\mask$ will be redrawn at each iteration. It is worth pointing out that $(\Filter \mask^\top)$ is not performing the subsampling operation on 
+dictionary, which is essentially to remove the columns in $\Filter$ those are filtered out by $\mathcal{M}(\code)$. Due to the introduced subsampling matrix, the convolution 
+operator will not hold, hence it cannot be directly solved in the frequency domain. On the other hand, owing to the subsampling strategy, the number of variables that needs 
+to be computed for this subproblem is $pDK$ instead of $DK$, and this can lead to a reduction of the computation time up to a factor of $\frac{1}{p}$ when solving it in spatial domain.
 
@@
 \end{equation}
-where $\Code= [\Code_1, \dots, \Code_K] \in \mathbb{R}^{D \times MK}$ is a concatenated matrix, and $\Code_k$ is constructed from the associated $\code_k$, $\filter= [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
-In the common settings for CSC problem, $M \ll D$, hence there is no need to perform subsampling on dictionary.
+where $\Code= [\Code_1, \dots, \Code_K] \in \mathbb{R}^{D \times MK}$ is a concatenation of Toeplitz matrices, and $\Code_k$ is constructed from the associated $\code_k$, $\filter= [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
+In the common settings of CSC problem, $M \ll D$, hence there is no need to perform subsampling on dictionary.
 
-The work of~\cite{mensch2016dictionary} also applies the stochastic subsampling strategy for dictionary learning, while the subsampling is randomly performed on the observed data, differing from that of our proposed.
-One can think of our proposed randomization approach as a variant of the stochastic Frank-Wolfe algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which a subset of the variables are randomly extracted based on a certain probability distribution at each iteration.
+The work of~\cite{mensch2016dictionary} also applies a so-called stochastic subsampling strategy for dictionary learning, while the subsampling is randomly performed on the observed data, differing from that of our proposed.
+One can think of our proposed randomization approach as a variant of the stochastic Frank-Wolfe algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which the optimization are performed on a subset of the variables which are randomly extracted based on a certain probability distribution at each iteration.
 For the proposed algorithm, each iteration extracts ($pDK+MK$) variables, where $pDK$ variables are randomly picked out from $DK$ variables with identical probability and the rest remain unchanged.
-Owing to the highly sparse codes, the original signals can still be represented by a portion of the codes with a reasonable subsampling rate.
+Owing to the fact that the codes are highly sparse, the original signals can still be represented by a portion of the codes with a reasonable subsampling rate.
 Herein, unlike the stochastic Frank-Wolfe algorithm that generally requires more iterations to reach convergence, the convergence of the proposed algorithm will not be significantly affected by the subsampling manipulation.
@@
 We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this work, where $p=1$ indicates no subsampling, and $p=0.05$ indicates a subsampling rate of $5\%$.
-Problem~\ref{eq:updatingCode} is the standard LASSO, which can be solved by plenty of optimization frameworks.
-We found that solving it by ADMM delivers a good balance for computation time and convergence within a moderate number of iterations.
-Specifically, the data fitting term and the $L_1$ penalty term are split, forming two separate substeps.
-The first substep is a quadratic programming (QP) problem, and we can either cache the matrix factorization by Cholesky decomposition (when $N$ is relatively large), or solve it by Conjugate Gradient (when $N$ is relatively small).
-The second substep can be solved by a point-wise shrinkage operation.
-Problem~\ref{eq:updatingFilter} is a quadratic constrained quadratic programming (QCQP) problem, and it can be efficiently solved by projected block coordinate decent.
+
+Problem~\ref{eq:updatingCode} is the standard LASSO, which can be solved by plenty of optimization frameworks. We found that solving it by ADMM delivers a good balance 
+between computation time and convergence within a moderate number of iterations. Specifically, the data fitting term and the $L_1$ penalty term are split, forming two 
+separate substeps. The first substep is a quadratic programming (QP) problem, and we can either cache the matrix factorization by Cholesky decomposition 
+(when $N$ is relatively large), or solve it iteratively by Conjugate Gradient (when $N$ is relatively small). The second substep can be solved by a point-wise
+ shrinkage operation. The above two substeps alternatively solved within the ADMM iterations. Problem~\ref{eq:updatingFilter} is a quadratic 
+constrained quadratic programming (QCQP) problem, and it can be efficiently solved by projected block coordinate decent.
 Empirically, a single iteration is enough with $\filter$ computed in previous iteration as a warm start.
@@
 \end{equation}
-where $\Filter^{t-1}$ is constructed from the dictionary learned by $(t-1)$th iteration, and $\mask^t$ is the subsample matrix at current iteration.
-After obtaining the sparse codes, the dictionary is updated by:
+where $\Filter^{t-1}$ is constructed from the dictionary learned by $(t-1)$th iteration, and $\mask^t$ is the subsample matrix at current iteration, which is iteratively 
+redrawn as in SBCSC. After obtaining the sparse codes, the dictionary is updated by:
 \begin{equation}
@@
     \State $ \text{Compute } \code^t \text{ by solving problem~(\ref{eq:updatingCodeOnline}) using } \filter^{t-1}$
-    \State Compute $\surC^t$ and $\surB^t$ by eq~(\ref{eq:updateSur})
+    \State Compute $\surC^t$ and $\surB^t$ by Eq.~\ref{eq:updateSur}
     \State Compute $\filter^t$ by solving problem~(\ref{eq:updatingFilterOnline})
@@
 \subsection{Complexity Analysis}
-Recall that $D$ is the number of pixels for a single image, $K$ is the number of filters, and $M$ is the size of the filter support.
-For the state-of-the-art frequency-domain solvers, it has the time complexity $\mathcal{O}(K^2D + KDlog(D))$ for a single data pass.
+Recall that $D$ is the number of pixels for a single image, $K$ is the number of filters, and $M$ is the size of the filter support. Commonly, we can assume
+$K \approx M$. For the state-of-the-art frequency-domain solvers, it has the time complexity $\mathcal{O}(K^2D + KDlog(D))$ for a single data pass.
 
@@
 As for updating $\filter$, it takes $\mathcal{O}(K^2M^2)$ time.
-This is comparable to $\mathcal{O}(K^2D)$ in common CSC settings ($M \ll D$), while it requires multiple iterations in frequency domain and only one pass required by the proposed method, which greatly saves the time.
+This is comparable to $\mathcal{O}(K^2D)$ in common CSC settings ($M \ll D$), while it requires multiple iterations (ADMM iterations) in frequency domain to compute $\filter$ and only a single pass required by the proposed method, which greatly reduces the computation time.
 Overall, the proposed method has the time complexity of $\mathcal{O}(pKMD \sqrt{\tau} + K^2M^2)$.

### 2018-10-30 cvpr2019/Conclusion.tex
minor edits

@@
 This method significantly improves the runtime performance over the prior frequency-domain solvers, which applies to both batch mode and online-learning mode, as well as generating effective and proven outcomes.
-The proposed algorithm, for the first time, demonstrates the feasibility that tackling the CSC problem in spatial domain while still holding the runtime efficiency.
-Since the subproblem of updating the code is a highly sparse LASSO, other specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in~\cite{johnson2017stingycd}, which solves the LASSO problem by coordinate descent and skips unnecessary updates by the method of safe screening~\cite{ghaoui2012Swfe}.
-
-Furthermore, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the images and the sparse codes.
-Notice that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies (including the proposed one).
+The proposed algorithm, for the first time, demonstrates the feasibility that tackling the CSC problem in spatial domain while still holding, or even improving the runtime efficiency.
+Since the subproblem of updating the code is a highly sparse LASSO, other specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in~\cite{johnson2017stingycd}, which solves the LASSO problem by coordinate descent and skips unnecessary updates using the method of safe screening~\cite{ghaoui2012Swfe}.
+It would be worthy to emphasize that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies (including the proposed one).
+Furthermore, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the signals and the sparse codes.
 

### 2018-10-30 cvpr2019/Results.tex
minor edits

@@
 Comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate of $0.1$ reduces the computation time by a factor of two for the tested example.
-Please see supplementary materials for additional experimental results.
+The robustness of the proposed algorithm is evaluated by additional experiments.
+Please see supplementary materials for reference.
 
@@
 As for the runtime comparison, the proposed method runs at least 5 times faster than the comparable method.
-Supplement shows additional comparisons for the other dataset.
+Supplement shows additional comparisons for the other datasets.
 

### 2018-10-30 cvpr2019/SCSCmodel.tex
minor edits

@@
 
-The work of~\cite{mensch2016dictionary} also applies a so-called stochastic subsampling strategy for dictionary learning, while the subsampling is randomly performed on the observed data, differing from that of our proposed.
+The work of~\cite{mensch2016dictionary} also applies a so-called stochastic subsampling strategy for dictionary learning, while the subsampling is randomly performed on the
+observed signals, differing from that of our proposed. In addition, it is basically applied for factorizing matrix that is large in both dimensions. Even though CSC can be 
+expressed in a similar mathematical formula as matrix factorization, they are essential different due to the convolution properties in CSC model.
 One can think of our proposed randomization approach as a variant of the stochastic Frank-Wolfe algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which the optimization are performed on a subset of the variables which are randomly extracted based on a certain probability distribution at each iteration.

### 2018-10-30 cvpr2019/main.tex
minor edits

--- 2018-10-25 cvpr2019/egpaper_for_review.tex
@@
 However, solving the problem in frequency domain automatically assumes circular boundary conditions, and also it is restricted by imposing modern optimization strategies for this specific problem.
-In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes.
+In this work, we propose a novel stochastic spatial-domain solver, in which a randomized subsampling strategy is introduced in the subproblem of computing sparse codes.
 Afterwards, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes.
-In both cases, we show experimentally that the proposed method outperforms the state-of-the-art frequency-domain solvers with a reasonable selection of the subsampling rate.
-At last, we learn the over-complete dictionary from large-scale datasets, which demonstrates a better sparse representation of the natural images on account of more abundant learned image features.
+In both cases, we show experimentally that the proposed method, with a reasonable selection of the subsampling rate, outperforms the state-of-the-art frequency-domain solvers in terms of execution time without losing the learning quality.
+At last, we evaluate the effectiveness of the over-complete dictionary learned from large-scale datasets that has not been studied by precedent CSC work, which demonstrates an improved sparse representation of the natural images on account of more abundant learned image features.
 \end{abstract}

### 2018-11-08 cvpr2019/CSCmodel.tex
add paper
WH edits on full text

--- 2018-05-18 nips2018/CSCmodel.tex
@@
 \section{Convolutional Sparse Coding (CSC)}
-Specifically, the CSC problem has the form
-\begin{equation}
+The dictionary learning problem for CSC problem has the form
+\begin{equation}\label{eq:CSCmodel}
 \begin{split}
-    \minimize{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
+    \mini{\filter,\code} & \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \code_k \|_2^2 + \lambda \sum_{k=1}^{K}\| \code_k \|_1 \\
     \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
@@
 \end{equation}
-where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a vectorized image\footnote{In this manuscript, we work on 2D images.}, $\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in \mathbb{R}^D$ is the sparse code associated with that dictionary,  $\lambda>0$ is a sparsity inducing penalty parameter, $K$ is the number of dictionary filters, and $*$ is the convolution operator.
-The above model will be applied to all the training images.
+where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a
+vectorized image\footnote{In this manuscript, we work on 2D images.},
+$\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in
+\mathbb{R}^D$ is the sparse code associated with that dictionary,
+$\lambda>0$ is a sparsity inducing penalty parameter, $K$ is the
+number of dictionary filters, and $*$ is the convolution operator. The
+above model will be applied to all the training images
+$\signal\in\mathbb{X}$.
 
-The modern approaches exploit Parseval's theorem and introduce two slack variables to separate the non-smooth $L_1$ penalty term and the $L_2$ constraints, making it feasible to be efficiently computed in frequency domain, and to apply splitting strategy to formulate the problem into ADMM framework, where the two subproblems (updating $\code$ and updating $\filter$) are jointly solved by coordinate descent~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
-The model and existing frequency solvers suffer from several issues:
+Most recent CSC algorithms exploit Parseval's theorem and introduce
+two slack variables to separate the non-smooth $L_1$ penalty term and
+the $L_2$ constraints, making it feasible to efficiently compute the
+latter in the frequency domain. Furthermore, the whole
+Problem~\eqref{eq:CSCmodel} can be split into alternating subproblems
+for updating $\code$ and $\filter$, which are jointly solved by
+coordinate
+descent~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}. This
+approach suffers from several issues:
 
 \begin{itemize}
-  \item While CSC overcomes the independence assumption held in patch-based learning algorithms, far more variables ($K$ times more) are introduced to represent a single image to compensate for this.
-This creates more severe memory and computational burdens.
+  \item While CSC overcomes the independence assumption held in
+    patch-based learning algorithms, far more variables ($K$ times
+    more) are introduced to represent a single image to compensate for
+    this. This creates more severe memory and computational burdens.
 
-  \item We observe through experiments that the vast majority of the entries of the reconstructed sparse codes do not provide useful information about the represented image.
-For $K=100$, 99.5\% entries are not informative.
-This indicates that the subproblem for updating $\code$ solves a highly sparse LASSO problem.
-Transforming the problem into frequency domain imposes restriction on the use of optimization strategies for this very specific problem.
+  \item We observe through experiments that the vast majority of the
+    entries of the reconstructed sparse codes do not provide useful
+    information about the represented image. For $K=100$, 99.5\%
+    entries are not informative. This indicates that the subproblem
+    for updating $\code$ solves a highly sparse LASSO
+    problem. Transforming the problem into frequency domain imposes
+    restrictions on exploiting this sparsity.
 
-  \item While prior work shows its efficiency in solving the CSC problem in the frequency domain, this is only applicable for updating $\code$, and does not hold for updating $\filter$.
-The dictionary filters usually have much smaller spatial support than the dimension size of the sparse codes ($M \ll D$).
-However, in order to tackle the problem in the frequency domain, it requires to process the $\filter$-subproblem in the same dimensions as the sparse codes, and then project the results onto its small spatial support.
+  \item While prior work shows its efficiency in solving the CSC
+    problem in the frequency domain, this is only applicable for
+    updating $\code$, and does not hold for updating $\filter$. The
+    dictionary filters usually have much smaller spatial support than
+    the dimension size of the sparse codes ($M \ll D$). However, in
+    order to tackle the problem in the frequency domain, it is
+    necessary to process the $\filter$-subproblem over the full
+    support of the sparse codes, and then project the results onto the
+    much smaller spatial support of the filters.
 \end{itemize}
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2018-11-08 cvpr2019/Conclusion.tex
WH edits on full text

@@
 \section{Conclusions}
-In this work, we present a novel stochastic subsampling strategy for solving the CSC problem in spatial domain.
-This method significantly improves the runtime performance over the prior frequency-domain solvers, which applies to both batch mode and online-learning mode, as well as generating effective and proven outcomes.
-The proposed algorithm, for the first time, demonstrates the feasibility that tackling the CSC problem in spatial domain while still holding, or even improving the runtime efficiency.
-Since the subproblem of updating the code is a highly sparse LASSO, other specific optimization strategies can be applied to further accelerate the computation, for instance the idea proposed in~\cite{johnson2017stingycd}, which solves the LASSO problem by coordinate descent and skips unnecessary updates using the method of safe screening~\cite{ghaoui2012Swfe}.
-It would be worthy to emphasize that transforming the problem into Fourier domain cannot benefit from these kinds of speedup strategies (including the proposed one).
-Furthermore, instead of employing uniform subsampling strategy, alternative subsampling strategies can be studied in the future for a gain of learning efficiency, for instance an importance or correlation based sampling strategy which considers the dependency relationship between the signals and the sparse codes.
+In this work, we present a novel stochastic subsampling strategy for
+solving the CSC problem in the spatial domain. This method
+significantly improves the runtime performance over the prior
+frequency-domain solvers, which applies to both batch mode and
+online-learning mode.  The proposed algorithm, for the first time,
+demonstrates the feasibility that tackling the CSC problem in spatial
+domain while still holding, or even improving the runtime
+efficiency. Since the subproblem of updating the code is a highly
+sparse LASSO, other specific optimization strategies can be applied to
+further accelerate the computation, for instance the idea proposed
+in~\cite{johnson2017stingycd}, which solves the LASSO problem by
+coordinate descent and skips unnecessary updates using the method of
+safe screening~\cite{ghaoui2012Swfe}. It is worth emphasizing that
+Fourier-domain methods cannot benefit from these kinds of speedup
+strategies.
 
-We have also shown the capability of the developed online algorithm to learn representative and meaningful over-complete dictionary from arbitrary large datasets, and the availability of the dictionary is further verified by the application of image inpainting.
-It can be foreseen that this capability has widespread applications in the audio and image related tasks, and higher dimensional signal processing.
-The source code for SBCSC and SOCSC is attached in the supplement for reference.
+In the future, alternative subsampling strategies can be studied to
+improve learning efficiency. Instead of employing uniform subsampling
+strategy, for instance one could employ an importance or correlation
+based sampling strategy that considers the inter-dependency between the
+signals and the sparse codes.
+
+We have also shown the capability of the developed online algorithm to
+learn representative and meaningful over-complete dictionary from
+arbitrary large datasets, and the availability of the dictionary is
+further verified by the application of image inpainting. It can be
+foreseen that this capability has widespread applications in audio
+and image related tasks, and higher dimensional signal processing. The
+source code for SBCSC and SOCSC is attached in the supplement for
+reference.
+\note{Do you really mean source code (as in full matlab code), or just
+  the pseudo-code?}
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2018-11-08 cvpr2019/Introduction.tex
WH edits on full text

@@
 \section{Introduction}
-Convolutional Sparse Coding (CSC) has been demonstrated to be an effective tool to learn translational invariant dictionary from a number of training signals, and shows its applications in recent researches about neural and brain information processing~\cite{jas2017learning,peter2017sparse}, as well as in a variety of image processing tasks, for instance, image inpainting~\cite{heide2015fast}, super-resolution~\cite{gu2015convolutional}, high dynamic range imaging~\cite{serrano2016convolutional}, and high-dimensional signal reconstructions~\cite{choudhury2017consensus,bibi2017high}.
-CSC differs from conventional sparse coding by formulating the signals as a summation of a set of convolutions on dictionary filters and sparse codes, rather than linearly adding up those filters.
-Alternatively, sparse coding, as a patch-based approach, learns filters from partitioned local structures, and this partition manipulation discards inherent correlations between those patches, so as to learns redundant filters (the same or similar ones with translated versions).
-Owing to the convolutional property, the dictionary learned from CSC achieves signal global coherence, tending to be more representative.
-It should be emphasized that the convolutional-based deep learning, evolving from pioneering work~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet}, has shown its extraordinary success in a broad range of high-level image understanding applications.
-This supervised learning based approach refers to one type of discriminative models, whereas, CSC is a kind of generative model, which, in general, is less task-specific than discriminative models.
+Convolutional Sparse Coding (CSC) is a method for learning {\em
+  generative} models in the form of translationally invariant
+dictionaries for a large variety of different training signals.  These
+generative models have been shown effective for solving problems in
+neural and brain information
+processing~\cite{jas2017learning,peter2017sparse}, as well as in a
+variety of image processing tasks, for instance, image
+inpainting~\cite{heide2015fast},
+super-resolution~\cite{gu2015convolutional}, high dynamic range
+imaging~\cite{serrano2016convolutional}, and high-dimensional signal
+reconstructions~\cite{choudhury2017consensus,bibi2017high}. CSC
+differs from conventional sparse coding by formulating the signals as
+the sum of a set of convolutions on dictionary filters and sparse
+codes instead of patch-wise linear combinations of
+filters. In traditional sparse dictionary learning, the patch
+structure significantly degrades the expressiveness of the
+dictionaries by introducing a strong dependency on the position of a
+feature, which the convolutional nature of CSC avoids.
+%% Alternatively, sparse coding, as a patch-based approach,              %%
+%% learns filters from partitioned local structures, and this partition  %%
+%% manipulation discards inherent correlations between those patches, so %%
+%% as to learns redundant filters (the same or similar ones with         %%
+%% translated versions). Owing to the convolutional property, the        %%
+%% dictionary learned from CSC achieves signal global coherence, tending %%
+%% to be more representative.                                            %%
 
-To solve the optimization problems formulated in CSC, Zeiler et al.~\cite{zeiler2010deconvolutional} iteratively solves two subproblems (updating sparse codes and updating filters) using gradient decent in the form of convolutional operations, while performing convolution in spatial domain is computationally expensive.
-Recent algorithms tackles the problem by exploiting Parseval's theorem to express the spatial convolution by multiplication in the frequency domain and using Alternating Direction Method of Multipliers (ADMM)~\cite{boyd2011distributed} to separate the non-smooth terms in the optimization problem, and they show tremendous improvements over prior spatial-domain solvers with respect to running time~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient}.
-Most of the prior work learns the dictionary filters in a batch mode, which indicates that all training signals are involved in every training iteration, and this restricts it from applying to large datasets or streaming data.
+Of course this convolutional approach is also a the heart of many deep
+learning-based methods in the form of
+CNNs~\cite{lecun1998gradient,kavukcuoglu2010learning,krizhevsky2012imagenet},
+which have in recent years been extraordinarily successful for a broad
+range of high-level image understanding applications. However, while
+CNNs generally are used in a {\em supervised} setting and produce {\em
+  discriminative}, task-specific models, CSC is {\em unsupervised} and
+produces {\em generative} models that easily transfer between tasks.
 
-In contrast to batch mode learning, online learning~\cite{shalev2012online} is a well established strategy which processes a single or a portion (mini-batch) of the whole data at each training step, and incrementally updates model variables.
-Herein, the required memory and computing sources are only dependent on the sample size in every observation, independent of the training data size.
-It alleviates the scalability issue arisen in batch approaches, and the convergence of the algorithm was firstly analyzed using stochastic approximation tools~\cite{bottou1998online}.
-Bottou et al.~\cite{bousquet2008tradeoffs} further showed better generalization performance of the stochastic algorithms than standard gradient descent on large scale learning systems.
-Later on, online learning strategies were synergetic with sparse coding, which was then scaled up for learning dictionary from millions of training samples~\cite{mairal2009online,mairal2010online}, and for large-scale matrix factorization with an additionally introduced subsampling strategy~\cite{mensch2016dictionary}.
-More recently, Liu et al.~\cite{liu-2018-first} and Wang et al.~\cite{wang2018scalable} separately proposed similar online learning frameworks for the CSC model, alleviating the memory issues arise in batch-based CSC model on large datasets.
+To solve the optimization problems inherent to CSC, Zeiler et
+al.~\cite{zeiler2010deconvolutional} iteratively solve two subproblems
+(updating sparse codes and updating filters) using gradient decent in
+the form of convolutional operations in the spatial domain, which is
+computationally expensive. Recent algorithms tackle the problem by
+exploiting Parseval's theorem to express the spatial convolution by
+multiplication in the frequency domain and using proximal solver such
+as Alternating Direction Method of Multipliers
+(ADMM)~\cite{boyd2011distributed} to separate the linear least squares
+parts terms from the non-smooth terms in the optimization
+problem. These approaches show tremendous improvements over prior
+spatial-domain solvers with respect to running
+time~\cite{bristow2013fast,heide2015fast,wohlberg2016efficient,choudhury2017consensus}. Most
+of the prior work learns the dictionary filters in a batch mode, which
+indicates that all training signals are involved in every training
+iteration, and this restricts it from applying to large datasets or
+streaming data.
 
-{\bfseries Contributions.} We mainly make three contributions in this work.
-First of all, we introduce a randomization strategy for the CSC model and solve the entire problems in spatial domain.
-It demonstrates that the proposed stochastic spatial-domain solver, with a reasonably selected subsampling rate, outperforms the state-of-the-art frequency-domain solvers with regard to computing efficiency.
-We then formulate an online-learning version of the proposed algorithm, and it shows dramatic runtime improvement over precedent online CSC methods, as well as producing comparable outcomes.
-At last, we demonstrate its capability to learn the over-complete dictionary from thousands of images, and analyze the effectiveness of the learned over-complete dictionary, which has not been reported or analyzed by precedent CSC work.
+In contrast to batch mode learning, online
+learning~\cite{shalev2012online} is a well established strategy which
+processes a single image or a small portion (mini-batch) of the whole
+data at each training step, and incrementally updates model
+variables. Herein, the required memory and computing sources are only
+dependent on the sample size in every observation, independent of the
+training data size. It alleviates the scalability issue that arises in
+batch approaches, and the convergence of the algorithm was firstly
+analyzed using stochastic approximation
+tools~\cite{bottou1998online}. Bottou et
+al.~\cite{bousquet2008tradeoffs} further showed better generalization
+performance of the stochastic algorithms than standard gradient
+descent on large scale learning systems. Later on, online learning
+strategies were synergetic with sparse coding, which was then scaled
+up for learning dictionary from millions of training
+samples~\cite{mairal2009online,mairal2010online}, and for large-scale
+matrix factorization with an additionally introduced subsampling
+strategy~\cite{mensch2016dictionary}. More recently, Liu et
+al.~\cite{liu-2018-first} and Wang et al.~\cite{wang2018scalable}
+separately proposed similar online learning frameworks for the CSC
+model, alleviating the memory issues arise in batch-based CSC model on
+large datasets.
+
+{\bfseries Contributions.} We mainly make three contributions in this
+work. First, we introduce a randomization strategy for the CSC
+model and solve the entire problems in spatial domain. We demonstrate
+that the proposed stochastic spatial-domain solver, with a reasonably
+selected subsampling rate, outperforms the state-of-the-art
+frequency-domain solvers with regard to computing efficiency. We then
+formulate an online-learning version of the proposed algorithm, and 
+show dramatic runtime improvement over current online CSC methods,
+while producing comparable outcomes. Finally, we demonstrate the
+capability to learn the over-complete dictionary from thousands of
+images, and analyze the effectiveness of the learned over-complete
+dictionary for a number of reconstruction tasks.
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2018-11-08 cvpr2019/Results.tex
WH edits on full text

@@
 \section{Results} \label{sec:result}
-We first validate the proposed algorithms on fruit and city datasets~\cite{zeiler2010deconvolutional}, both of which contain 10 training images in the size of $100 \times 100$.
-The online-mode algorithms are then adapted to one thousand $100 \times 100$ image patches randomly picked up from ImageNet~\cite{deng2009imagenet}.
-Note that batch-based CSC commonly can only handle less than 100 images simultaneously.
-The dictionary dimension size is set to $11 \times 11 \times 100$ in all experiments except for over-complete dictionary.
-All training and evaluation processes in this manuscript are performed on contrast normalized images~\cite{zeiler2010deconvolutional,heide2015fast}.
+We first validate the proposed algorithms on the fruit and city
+datasets~\cite{zeiler2010deconvolutional}, which each consist of 10
+training images of size $100 \times 100$. The online-mode algorithms
+are then adapted to one thousand $100 \times 100$ image patches
+randomly picked up from ImageNet~\cite{deng2009imagenet}. Note that
+batch-based CSC commonly can only handle less than 100 images
+simultaneously. The dictionary size is set to $100$ filters of size
+$11 \times 11$ pixels in all experiments except for over-complete
+dictionary. All training and evaluation processes in this manuscript
+are performed on contrast normalized
+images~\cite{zeiler2010deconvolutional,heide2015fast}.
 
@@
 \end{subfigure}
-
 \caption{Top: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling rate, all of which on performed on fruit dataset.
@@
 
-{\bfseries Convergence.} Comparisons of the convergence between the proposed method (SBCSC) and the state-of-the-art batch-mode algorithm~\cite{heide2015fast} are shown in Fig.\ \ref{fig:subsampleResult}.
-A different selection of the subsampling rate reveals that the proposed strategy will slightly influence the convergence and the training objective of the minimization problem.
-Specifically, the more subsampled, the relatively slower convergence and the higher objective will be obtained.
-On the other hand, small subsampling rate will significantly accelerate the computation process, where $10\%$ subsampling achieves about $6 \times$ speedup over no subsampled solver and $2 \times$ speedup over state-of-the-art frequency solver for one iteration.
-We observe that a subsampling rate between $0.1$ and $0.2$ delivers empirically good enough convergence in our settings, as well as achieving at least $3 \times$ speedup.
-In general, the proposed method with various subsampling rates converges at around 10-12 iterations in all testing cases, acting similar to the competing methods.
-Notice that the comparable method has a relatively high objective at first $6-8$ iterations due to different splitting strategies are applied and subproblems are interleaved on the primary variables~\cite{wohlberg2016efficient}, though it converges to an optimum with comparable objective after 10 iterations.
-In summary, the convergence behaviors of the proposed algorithm is only slightly influenced by the subsampling strategy within the testing subsampling rates.
-Comparing to the state-of-the-art frequency solver, the proposed stochastic spatial-domain solver with a subsampling rate of $0.1$ reduces the computation time by a factor of two for the tested example.
-The robustness of the proposed algorithm is evaluated by additional experiments.
-Please see supplementary materials for reference.
+{\bfseries Convergence.} Comparisons of the convergence between the
+proposed method (SBCSC) and the state-of-the-art batch-mode
+algorithm~\cite{heide2015fast} are shown in
+Fig.~\ref{fig:subsampleResult}. A different selection of the
+subsampling rate reveals that the proposed strategy will slightly
+influence the convergence and the training objective of the
+minimization problem. Specifically, the more subsampled, the
+relatively slower convergence and the higher objective will be
+obtained. On the other hand, small subsampling rate will significantly
+accelerate the computation process, where $10\%$ subsampling achieves
+about $6 \times$ speedup over the not subsampled spatial domain solver
+and a $2 \times$ speedup over state-of-the-art Fourier-domain solver
+for one iteration. We observe that a subsampling rate between $p=0.1$
+and $p=0.2$ delivers empirically good enough convergence in our
+settings, as well as achieving at least $3 \times$ speedup. In
+general, the proposed method with various subsampling rates converges
+at around 10-12 iterations in all testing cases, acting similar to the
+competing methods.
+\note{Not sure what you want to say here -- fix grammar:}
+Notice that the comparison method has a relatively
+high objective value during the first $6-8$ iterations due to
+different splitting strategies are applied and subproblems are
+interleaved on the primary variables~\cite{wohlberg2016efficient},
+though it converges to an optimum with comparable objective after 10
+iterations. In summary, the convergence behaviors of the proposed
+algorithm is only slightly influenced by the subsampling strategy
+within the testing subsampling rates. Comparing to the
+state-of-the-art frequency solver, the proposed stochastic
+spatial-domain solver with a subsampling rate of $0.1$ reduces the
+computation time by a factor of two for the tested example. The
+robustness of the proposed algorithm is evaluated by additional
+experiments. Please see supplementary materials for reference.
 
-{\bfseries Reconstruction}.
-The learned filters by SBCSC with subsampling rate $0.1$ are shown in the bottom of Fig.\ \ref{fig:subsampleResult}.
-For a visual comparison, we also show the filters learned from the competing method (bottom left of Figure 3 in~\cite{heide2015fast}).
-As can be observed, both of them learn some seemingly similar Gabor-like filters.
-While after zooming (we also show zoom-in comparisons in supplement), it can be seen that our learned Gabor-like filters have less impure structures.
-Moreover, the compared dictionary contains a number of noise-like filters, which are rarely existed in ours.
-We then demonstrate the effectiveness of the reconstructed filters in the application of image inpainting, which refers to reconstructing a full image from partial measurements.
-A numerical comparison of the reconstruction quality is shown in Fig.\ \ref{fig:PSNRrecon}.
-The filters learned by the proposed method not only show more visually decent structures and less specific features, but also demonstrate its capability to better reconstruct partial observed images with respect to the PSNR value.
-In addition to that, the learning process only takes about $50\%$ of the execution time than the comparison.
+{\bfseries Reconstruction}. The SBSC-learned filters with a
+subsampling rate of $p=0.1$ are shown in the bottom of
+Fig.~\ref{fig:subsampleResult}. For a visual comparison, we also show
+the filters learned from the competing method (bottom left of Figure 3
+in~\cite{heide2015fast}). As can be observed, both of them learn some
+seemingly similar Gabor-like filters. However, zooming into the
+details (please see supplemental materials for high resolution
+versions) reveals that our filters appear less noisy than the ones
+from~\cite{heide2015fast}. We then demonstrate the effectiveness of
+the reconstructed filters in the application of image inpainting,
+which refers to reconstructing a full image from partial
+measurements. A numerical comparison of the reconstruction quality is
+shown in Fig.~\ref{fig:PSNRrecon}. The filters learned by the proposed
+method not only appear less noisy by themselves, but also achieve
+better reconstruction quality on partially observed images with
+respect to the PSNR value. Furthermore, the learning process
+only takes about $50\%$ of the time for our method.\todo{specific
+  times here!}.
+\note{So, how does Bis' work from last year compare in terms of
+  quality and time? It should
+  have much better dictionaries than~\cite{heide2015fast} as well.}
 
-\subsection{Online Learning Settings}
+\subsection{Online Learning}
 
-{\bfseries Convergence.} Unlike the batch-based learning approaches which evaluate its convergence by monitoring the objective value on training datasets, a common way to evaluate the learning process of online learning model is to monitor its objective value on testing datasets.
-The testing objectives of the proposed method (SOCSC) and prior published online frequency-domain CSC method~\cite{liu-2018-first}, with respect to iterations, are shown in Fig.\ \ref{fig:onlineSmall}.
-In the same figure, we also keep track of the capability of the updated filters during the learning process to sparsely represent the testing images, which is demonstrated by the time evolution of PSNR.
-These two approaches stop at optimum positions with close testing objective values, though, they exhibit slightly different convergence behaviors with respect to iterations.
-The final testing PSNR values for both methods also reveal a similar reconstruction performance of the learned filters.
-As for the runtime comparison, the proposed method runs at least 5 times faster than the comparable method.
-Supplement shows additional comparisons for the other datasets.
+{\bfseries Convergence.} Unlike the batch-based learning approaches
+which evaluate its convergence by monitoring the objective value on
+training datasets, a common way to evaluate the learning process of
+online learning model is to monitor its objective value on test
+datasets. In Fig.~\ref{fig:onlineSmall} we plot the objective values
+against the iteration number for the proposed method (SOCSC) and a
+recent online frequency-domain CSC method~\cite{liu-2018-first}. In
+the same figure, we also keep track of the capability of the updated
+filters during the learning process to sparsely represent the test
+images, which is demonstrated by the time evolution of PSNR. These two
+approaches stop at optimum positions with similar objective values.
+%although they exhibit slightly different convergence behaviors with
+%respect to iterations.
+The final PSNR values for both methods also reveal a similar
+reconstruction performance of the learned filters. In terms of runtime
+comparison, however, the proposed method runs at least 5 times faster
+than the comparison method. The supplement shows additional comparisons
+for the other datasets.
 
@@
 
-{\bfseries Over-complete dictionary.} As far as we know, none of the precedent CSC work reported or analyzed the over-complete dictionary (number of the dictionary is more than its degrees of freedom).
-One of the reasons could be that most of the prior work is batch-based, thus learning over-complete dictionary from small datasets would cause the overfitting issue, which may contain quite a few data-specific filters, and therefore be short of the generalization ability (we verify this explanation in supplement).
-The proposed online-based learning strategy (SOCSC) can overcome this issue by scaling the model up to arbitrary sample sizes.
+{\bfseries Over-complete dictionary.} To our knowledge, none of the
+existing CSC work reported or analyzed the over-complete dictionary
+(number of the dictionary is more than its degrees of freedom). One of
+the reasons could be that most of the prior work is batch-based, thus
+learning over-complete dictionary from small datasets would cause
+overfitting issues, which may contain quite a few data-specific
+filters, and therefore limit the ability to generalize the filters to
+other data (we verify this explanation in the supplement). The
+proposed online-based learning strategy (SOCSC) can overcome this
+issue by scaling the model up to arbitrary sample sizes.
 
@@
 \end{minipage}
-\caption{Filters learned from 1000 images by our method (SOCSC) and the state-of-the-art online method~\cite{liu-2018-first}, and their corresponding reconstruction quality using the same hyperparameter settings as in Fig.\ \ref{fig:PSNRrecon}.
+\caption{Filters learned from 1000 images by our method (SOCSC) and the state-of-the-art online method~\cite{liu-2018-first}, and their corresponding reconstruction quality using the same hyperparameter settings as in Fig.~\ref{fig:PSNRrecon}.
 (a) The under-complete dictionary ($11 \times 11 \times 100$) learned by~\cite{liu-2018-first}; (b) The under-complete dictionary ($11 \times 11 \times 100$) learned by SOCSC.
@@
 
-We demonstrate its capability on 1000 image patches with the size of $100 \times 100$, and learn $11 \times 11 \times 400$ over-complete dictionary, all of which are shown in Fig.\ \ref{fig:overCompleteDic} .
-For a visual comparison, 100 learned filters by the same algorithm and its comparable approach~\cite{liu-2018-first} are also represented.
-As can be observed, both of the approaches learn visually similar under-complete dictionary, while the proposed method takes $5 \times$ less training time than the competitive one.
-As for the learned over-complete dictionary, it is composed of the Gabor-like image features as represented in the under-complete dictionaries, as well as a number of low contrast features which are rarely existed in those under-complete dictionaries.
-This additional feature information would play an essential role to better reconstruct the natural images, which can be demonstrated by the results of reconstruction quality shown at the bottom of the same figure.
+We demonstrate this ability on 1000 image patches with the size of
+$100 \times 100$, and learn an $11 \times 11 \times 400$ over-complete
+dictionary, which is shown in Fig.~\ref{fig:overCompleteDic}. For a
+visual comparison, we also show $100$ learned filters generated by the
+same algorithm and another 100 filters generated
+by~\cite{liu-2018-first}. As can be observed, both of the approaches
+learn visually similar under-complete dictionary, while the proposed
+method takes $5 \times$ less training time than the comparison
+method. The learned over-complete dictionary is composed of
+the Gabor-like image features as represented in the under-complete
+dictionaries, as well as a number of low contrast features which are
+not typical for under-complete dictionaries. This additional
+feature information would play an essential role to better reconstruct
+the natural images, which can be demonstrated by the results of
+reconstruction quality shown at the bottom of the same figure.
 
-We further show a bottleneck revealed by the under-complete dictionary in the online-based CSC model.
-The top of Fig.\ \ref{fig:overComDicAndMinibatch} demonstrates that no more apparent progress could be observed when the number of training images is higher than a specific value for both of the online approaches ($K=100$).
-However, owing to more abundant filters, learning over-complete dictionary overcomes this bottleneck, and it shows a considerable improvement, with regard to PSNR, to have a sparse representation of the testing images during the learning process.
-This is also verified by applying these learned dictionaries to the image inpainting application as discussed above.
+We further show a bottleneck revealed by the under-complete dictionary
+in the online-based CSC model. The top of
+Fig.~\ref{fig:overComDicAndMinibatch} demonstrates that no more
+apparent progress could be observed when the number of training images
+is higher than a specific value for both of the online approaches
+($K=100$). However, owing to more abundant filters, learning
+over-complete dictionary overcomes this bottleneck, and it shows a
+considerable improvement in the PSNR of image representations.  This
+is also verified by applying these learned dictionaries to the image
+inpainting application as discussed above.
 
-{\bfseries Mini-batching.} In practice, a mini-batching strategy would be preferred in order to gain advantages from modern parallel computing architectures.
-This is also a standard extension to stochastic optimization algorithms~\cite{Takac2013, PCDM, SCSG}.
-We denote the mini-batch size as $\eta$.
-In the proposed online algorithm (SOCSC), the time complexity for one step dictionary update will not increase linearly with the increase of $\eta$.
-Concretely speaking, updating $\code$ can be implemented by caching the Cholesky decomposition, and one computation of the matrix factorization can be applied to all of the currently selected batches.
-Herein, the complexity for doing updating $\code$ $\eta$ times all together is cheaper than $\eta$ times the complexity of updating one $\code$.
-In addition, the time complexity for updating $\filter$ is not linearly affected by the value of $\eta$, which will be executed only once in each training step regardless of $\eta$.
-One exception is to update surrogate matrices, the complexity of which is $\eta$ linearly dependent, while this step is not dominant in the runtime.
+{\bfseries Mini-batching.} In practice, a mini-batching strategy would
+be preferred in order to gain advantages from modern parallel
+computing architectures. This is also a standard extension to
+stochastic optimization algorithms~\cite{Takac2013, PCDM, SCSG}. We
+denote the mini-batch size as $\eta$. In the proposed online algorithm
+(SOCSC), the time complexity for one step dictionary update will not
+increase linearly with the increase of $\eta$. Concretely speaking,
+updating $\code$ can be implemented by caching the Cholesky
+decomposition, and one computation of the matrix factorization can be
+applied to all of the currently selected batches. Herein, the
+complexity for doing updating $\code$ $\eta$ times all together is
+cheaper than $\eta$ times the complexity of updating one $\code$. In
+addition, the time complexity for updating $\filter$ is not linearly
+affected by the value of $\eta$, which will be executed only once in
+each training step regardless of $\eta$. One exception is the update
+of surrogate matrices which has a complexity that is linear in
+$\eta$. However, this step is not dominant in the runtime.
 
-The runtime comparisons for various mini-batch sizes are shown in the bottom of Fig.\ \ref{fig:overComDicAndMinibatch}.
-Note that larger $\eta$ will result in less number of iterations to process all 1000 samples.
-The plots show that a larger mini-batch size will generally lead to a greater progress in first few training steps, though it takes additional running time and memory.
-Overall, mini-batched updates provides a more runtime efficient learning process in the online-based CSC model, and according to the obtained experimental results, $\eta=20$ achieves one magnitude speedup over $\eta=1$ to reach a condition with the same level convergence on a single-core program.
-Since computing sparse codes is a data-independent process, this mini-batched approach can be further accelerated in a distributed-computing system.
+The runtime comparisons for various mini-batch sizes are shown in the
+bottom of Fig.~\ref{fig:overComDicAndMinibatch}. Note that larger
+$\eta$ will result in a smaller number of iterations to process all
+$1000$ samples. The plots show that a larger mini-batch size will
+generally lead to a greater progress in first few training steps,
+though it takes additional running time and memory. Overall,
+mini-batched updates provides a more runtime efficient learning
+process in the online-based CSC model, and according to the obtained
+experimental results, $\eta=20$ achieves a one order of magnitude
+speedup over $\eta=1$ to reach a a comparable level of
+convergence. Since computing sparse codes is a data-independent
+process, this mini-batched approach can be further accelerated in a
+distributed-computing system.
 \begin{figure}[h]
@@
 \end{figure}
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2018-11-08 cvpr2019/SCSCmodel.tex
WH edits on full text

--- 2018-10-28 cvpr2019/SCSCmodel.tex
@@
 \subsection{The Model}
-Based on the specific sparsity property of the codes, we propose a variant of the CSC model applying subsampling strategy on the codes,
-and formulate the following modified minimization problem:
+\note{The previous description was not accurate: Eq.2 is not a variant
+  of the CSC model, and does not replace Eq.1! Eq.2 is supposed to be
+  used inside an outer loop to implement Eq.1. This outer loop is an
+  implementation of CSC and Eg.1.  In order to really explain this
+  properly, we need to introduce an outer loop parameter for both
+  $\mask$ and $\mathcal{M}$.}
+
+Based on the strong sparsity of the codes $\code$, we propose to
+implement the CSC learning problem~\eqref{eq:CSCmodel} iteratively,
+where in each iteration we only consider a random subset
+$\mathcal{M}_k(\code_k)$ of the codes:
 \begin{align}
-    &\minimize{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k(\code_k) \|_1  \nonumber \\
-    &\text{subject to} ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
+    &\mini{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k(\code_k) \|_1  \nonumber \\
+    &\text{subject to} ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\}.
 \end{align}
-where $\mathcal{M}_k(\code_k)$ is the operation to subsample the corresponding code $\code_k$ following a Bernoulli distribution with probability $p$.
-The probability value $p$ controls the percentage of the sparse codes that will be considered by the solver.
-Basically, in the case of $p=1$, the proposed model is identical with the classical CSC model.
-When $p<1$, otherwise, the algorithm only solves a subset of the sparse codes at chosen positions in each iteration, and accordingly, the update of dictionary $d$ is based on the selected portion of the sparse codes.
-Similar to solving the classical CSC problem, we can apply coordinate descent algorithm, alternating on subproblems of $\mathcal{M}(\code)$ and $\filter$, to solve the above bi-convex optimization problem.
-Specifically, the modified minimization problem for $\code$ can be formulated as:
+\todo{add outer loop variable}
+\todo{There are some notational issues here -- convolution with an
+  irregularly subsampled signal! Lets discuss on Sunday.}
+Here $\mathcal{M}_k(\code_k)$ is the operation to subsample the
+corresponding code $\code_k$ following a Bernoulli distribution with
+probability $p$.
+%The probability value $p$ controls the percentage of
+%the sparse codes that will be considered by the solver.
+In the case of $p=1$, the proposed model is identical with the
+classical CSC model. When $p<1$, the algorithm only solves a subset of
+the sparse codes at chosen positions in each iteration, and
+accordingly, the update of dictionary $d$ is based on the selected
+portion of the sparse codes. Similar to solving the classical CSC
+problem, we can apply a coordinate descent algorithm, alternating on
+subproblems of $\mathcal{M}(\code)$ and $\filter$, to solve the above
+bi-convex optimization problem. Specifically, the modified
+minimization problem for $\code$ can be formulated as:
 \begin{equation} \label{eq:updatingCode}
@@
 \end{equation}
-where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D \times DK}$, $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$, the convolution operator are formulated in matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k * \code_k$.
-Therefore, each part of $\Filter$ is a Toeplitz matrix.
-Matrix $\mask$
-is a $\mathbb{R}^{pDk \times DK}$ random diagonal matrix with ones on the entries corresponding to the sampled sparse codes and zeros elsewhere, performing the function of 
-$\mathcal{M}(\code)$. Matrix $\mask$ will be redrawn at each iteration. It is worth pointing out that $(\Filter \mask^\top)$ is not performing the subsampling operation on 
-dictionary, which is essentially to remove the columns in $\Filter$ those are filtered out by $\mathcal{M}(\code)$. Due to the introduced subsampling matrix, the convolution 
-operator will not hold, hence it cannot be directly solved in the frequency domain. On the other hand, owing to the subsampling strategy, the number of variables that needs 
-to be computed for this subproblem is $pDK$ instead of $DK$, and this can lead to a reduction of the computation time up to a factor of $\frac{1}{p}$ when solving it in spatial domain.
+\todo{add outer loop variable}
+where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D
+  \times DK}$, $\code = [\code_1, \dots, \code_K] \in
+\mathbb{R}^{DK}$. The convolution operators are expressed as a matrix
+multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k *
+\code_k$. Therefore, each part of $\Filter$ is a Toeplitz
+matrix. Matrix $\mask$ is a $\mathbb{R}^{pDk \times DK}$ random
+diagonal matrix with $1$ for the entries corresponding to the sampled
+sparse codes and $0$ elsewhere, performing the function of
+$\mathcal{M}(\code)$. Matrix $\mask$ will be redrawn at each
+iteration. It is worth stressing that $(\Filter \mask^\top)$ is not
+performing a subsampling operation on the dictionary, \note{not sure
+  what this is supposed to say:} which is
+essentially to remove the columns in $\Filter$ those are filtered out
+by $\mathcal{M}(\code)$.
+\note{See notation issue above; we need to discuss this next week:}
+Due to the introduced subsampling matrix, the
+convolution operator cannot be implemented in the Fourier
+domain. However, due to the subsampling 
+strategy, the number of variables that need to be computed for this
+subproblem is $pDK$ instead of $DK$, which leads to a reduction
+of the spatial-domain computation time by a factor of $\frac{1}{p}$.
 
-After obtaining the subsampled sparse codes, we can then project them onto its original spatial support with $0$ filling. Afterwards, the dictionary can be updated by:
+After obtaining the subsampled sparse codes, we can then project them
+onto the original spatial support by substituting $0$ for the
+masked-out vlaues. Afterwards, the dictionary can be updated by:
 \begin{equation} \label{eq:updatingFilter}
@@
 \end{equation}
-where $\Code= [\Code_1, \dots, \Code_K] \in \mathbb{R}^{D \times MK}$ is a concatenation of Toeplitz matrices, and $\Code_k$ is constructed from the associated $\code_k$, $\filter= [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code \filter = \sum_{k=1}^{K} \filter_k * \code_k$.
-In the common settings of CSC problem, $M \ll D$, hence there is no need to perform subsampling on dictionary.
+\todo{add outer loop variable} where $\Code= [\Code_1, \dots, \Code_K]
+\in \mathbb{R}^{D \times MK}$ is a concatenation of Toeplitz matrices,
+and $\Code_k$ is constructed from the associated $\code_k$, $\filter=
+[\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code
+\filter = \sum_{k=1}^{K} \filter_k * \code_k$. In typical CSC
+settings, $M \ll D$, hence there is no need to perform subsampling on
+the dictionary.
 
-The work of~\cite{mensch2016dictionary} also applies a so-called stochastic subsampling strategy for dictionary learning, while the subsampling is randomly performed on the observed data, differing from that of our proposed.
-One can think of our proposed randomization approach as a variant of the stochastic Frank-Wolfe algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which the optimization are performed on a subset of the variables which are randomly extracted based on a certain probability distribution at each iteration.
-For the proposed algorithm, each iteration extracts ($pDK+MK$) variables, where $pDK$ variables are randomly picked out from $DK$ variables with identical probability and the rest remain unchanged.
-Owing to the fact that the codes are highly sparse, the original signals can still be represented by a portion of the codes with a reasonable subsampling rate.
-Herein, unlike the stochastic Frank-Wolfe algorithm that generally requires more iterations to reach convergence, the convergence of the proposed algorithm will not be significantly affected by the subsampling manipulation.
-This will be experimentally verified in Section~\ref{sec:result}.
+\note{I have no idea what the next two sentences are supposed to say:}
+The work of~\cite{mensch2016dictionary} also applies a so-called
+stochastic subsampling strategy for dictionary learning, while the
+subsampling is randomly performed on the observed signals, differing
+from that of our proposed. In addition, it is basically applied for
+factorizing matrix that is large in both dimensions. Although CSC can
+be expressed in a form similar to matrix factorization, the two
+problems are in practice quite different due to the convolutional
+nature of the CSC model.  One can think of our proposed randomization
+approach as a variant of the stochastic Frank-Wolfe
+algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which
+the optimization is performed on a subset of the variables which are
+randomly extracted based on a certain probability distribution at each
+iteration. For the proposed algorithm, each iteration extracts
+($pDK+MK$) variables, where $pDK$ variables are randomly picked from a
+total $DK$ variables, and the rest remain unchanged. Owing to the fact
+that the codes are highly sparse, the original signals can still be
+represented by a portion of the codes with a reasonable subsampling
+rate. Therefore the convergence of the proposed algorithm will not be
+significantly affected by the subsampling manipulation, unlike the
+general case of the stochastic Frank-Wolfe algorithm, which usually
+requires more iterations to reach convergence. This insight is
+experimentally verified in Section~\ref{sec:result}.
 
-The proposed subsampling strategy will be implemented in the fashions of {\em batch mode} (stochastic batch CSC) and {\em online mode} (stochastic online CSC).
+In the following we introduce two different outer loop structures to
+utilize the proposed subsampling strategy. First, we introduce a {\em
+  batch mode} method (stochastic batch CSC) that learns from all
+images simultaneously, and second we introduce an {\em online}
+variant (stochastic online CSC).
 
 \subsection{Stochastic Batch CSC (SBCSC)}
-We first formulate the batch-mode of the proposed method as shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total input images, $\code^i$ is the sparse code associated with $i$-th image, and $p$ is the uniform probability for one code been selected.
-We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this work, where $p=1$ indicates no subsampling, and $p=0.05$ indicates a subsampling rate of $5\%$.
-
-Problem~\ref{eq:updatingCode} is the standard LASSO, which can be solved by plenty of optimization frameworks. We found that solving it by ADMM delivers a good balance 
-between computation time and convergence within a moderate number of iterations. Specifically, the data fitting term and the $L_1$ penalty term are split, forming two 
-separate substeps. The first substep is a quadratic programming (QP) problem, and we can either cache the matrix factorization by Cholesky decomposition 
-(when $N$ is relatively large), or solve it iteratively by Conjugate Gradient (when $N$ is relatively small). The second substep can be solved by a point-wise
- shrinkage operation. The above two substeps alternatively solved within the ADMM iterations. Problem~\ref{eq:updatingFilter} is a quadratic 
-constrained quadratic programming (QCQP) problem, and it can be efficiently solved by projected block coordinate decent.
-Empirically, a single iteration is enough with $\filter$ computed in previous iteration as a warm start.
-We set the hyperparameters $\lambda=1$, the ADMM iteration fixed to 10, the augmented Lagrangian penalty $\rho$ to $10 \lambda$, and the over-relaxation strategy within ADMM is applied with $\alpha = 1.8$.
-For a detailed description of the above two solvers, please refer to the supplement.
-
-Every outer loop of SBCSC involves all of the training images, thus it would be computationally expensive to process them simultaneously and also runs out of memory quickly with the increase of the number of images.
-The batch-based learning algorithm lacks of the capability to scale up to very large datasets or to handle dynamically changed training data.
+We first introduce a batch-mode version of the proposed method as
+shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total
+input images, $\code^i$ is the sparse code associated with $i$-th
+image, and $p$ is the uniform probability for one code been
+selected. We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this
+work, where $p=1$ indicates no subsampling, and $p=0.05$ indicates a
+subsampling rate of $5\%$.
 
@@
 
+Problem~\eqref{eq:updatingCode} is the standard LASSO, which can be
+solved by plenty of optimization frameworks. We found that solving it
+with ADMM delivers a good balance between computation time and
+convergence within a moderate number of iterations. Specifically, the
+data fitting term and the $L_1$ penalty term are split, forming two
+separate substeps. The first substep is a quadratic programming (QP)
+problem, and we can either cache the matrix factorization by Cholesky
+decomposition (when $N$ is relatively large), or solve it iteratively
+by Conjugate Gradient (when $N$ is relatively small). The second
+substep can be solved by a point-wise shrinkage operation.
+%The above two substeps alternatively solved within the ADMM
+%iterations.
+Problem~\ref{eq:updatingFilter} is a quadratic constrained
+quadratic programming (QCQP) problem, and it can be efficiently solved
+by projected block coordinate decent. Empirically, a single iteration
+is enough with $\filter$ computed in previous iteration as a warm
+start. We set the hyperparameters $\lambda=1$, the ADMM iteration
+fixed to 10, the augmented Lagrangian penalty $\rho$ to $10 \lambda$,
+and the over-relaxation strategy within ADMM is applied with $\alpha =
+1.8$. For a detailed description of the above two solvers, please
+refer to the supplement.
+
+Every outer loop of SBCSC involves all of the training images, which
+makes it computationally expensive to process them all simultaneously.
+Furthermore, memory consumption quickly becomes an issue with
+increasing numbers of images. Thus, the batch-based learning algorithm
+lacks the ability to scale up to very large datasets or to handle
+dynamically changing training data.
+
 \subsection{Stochastic Online CSC (SOCSC)}
-We can further tackle the proposed problem in the online fashion for a gain of scalability.
-In the online learning setting as shown in Algorithm~\ref{algo:SOCSC}, each iteration only draws one or a subset (mini-batch) of the total training images, hence the complexity per loop is independent of the training sample size.
-Then, given the sampled image $\signal^t$ at $t$-th iteration, we can compute the corresponding subsampled sparse codes $\code^t$ by
+In order to address this scalability issue, we can tackle the
+Stochastic CSC problem in an online fashion. In the online learning
+setting as shown in Algorithm~\ref{algo:SOCSC}, each iteration only
+draws one or a subset (mini-batch) of the total training images, hence
+the complexity per loop is independent of the training sample
+size. Then, given the sampled image $\signal^t$ at $t$-th iteration,
+we can compute the corresponding subsampled sparse codes $\code^t$ by
 \begin{equation} \label{eq:updatingCodeOnline}
@@
 \end{equation}
-where $\Filter^{t-1}$ is constructed from the dictionary learned by $(t-1)$th iteration, and $\mask^t$ is the subsample matrix at current iteration, which is iteratively 
-redrawn as in SBCSC. After obtaining the sparse codes, the dictionary is updated by:
+\note{Here we have $t$ as an iteration variable now -- I don't think
+  this is a good choice ($t$ is usually reserved for continuous
+  values, better would be $i$ or $j$, and we need to introduce these
+  earlier in the paper.}
+where $\Filter^{t-1}$ is constructed from the dictionary learned by
+$(t-1)$th iteration, and $\mask^t$ is the subsample matrix at current
+iteration, which is iteratively redrawn as in SBCSC. After obtaining
+the sparse codes, the dictionary is updated by:
 \begin{equation}
@@
 \end{equation}
-Notice that updating dictionary involves all of the past training images and sparse codes.
-As shown in~\cite{mairal2009online,mairal2010online}, we can get rid of explicitly storing those data by introducing two surrogate matrices $\surC \in \mathbb{R}^{KM \times KM}$ and $\surB \in \mathbb{R}^{KM \times 1}$, which carry all of the required information for updating $\filter$, and can be iteratively updated by:
+Note that updating the dictionary in this fashion involves all of the
+past training images and sparse codes. Using techniques developed for
+regular (non-convolutional) dictionary
+learning~\cite{mairal2009online,mairal2010online}, we can get rid of
+explicitly storing this data by introducing two surrogate matrices
+$\surC \in \mathbb{R}^{KM \times KM}$ and $\surB \in \mathbb{R}^{KM
+  \times 1}$. These carry all of the required information for updating
+$\filter$, and can be iteratively updated by:
 \begin{equation} \label{eq:updateSur}
@@
 \end{equation}
-If so, the updated dictionary can be obtained by solving:
+With these surrogate matrices, the updated dictionary can be obtained
+by solving
 \begin{equation} \label{eq:updatingFilterOnline}
@@
 \end{equation}
-Problem~\ref{eq:updatingCodeOnline} and problem~\ref{eq:updatingFilterOnline} are solved in the same way as that for SBCSC.
+Problem~\eqref{eq:updatingCodeOnline} and
+problem~\eqref{eq:updatingFilterOnline} are solved in the same way as
+that for SBCSC.
 
@@
 \end{algorithmic}
+\todo{Find the best place for this algorithm (probably higher up)}
 \end{algorithm}
@@
 \subsection{Complexity Analysis}
-Recall that $D$ is the number of pixels for a single image, $K$ is the number of filters, and $M$ is the size of the filter support. Commonly, we can assume
-$K \approx M$. For the state-of-the-art frequency-domain solvers, it has the time complexity $\mathcal{O}(K^2D + KDlog(D))$ for a single data pass.
+Recall that $D$ is the number of pixels for a single image, $K$ is the
+number of filters, and $M$ is the size of the filter
+support. Commonly, we can assume $K \approx M$.  State-of-the-art
+frequency-domain solvers then have the time complexity
+$\mathcal{O}(K^2D + KDlog(D))$ for a single data pass.
 
-Compared with SBCSC, updating $\code$ (suppose we solve it by Conjugate Gradient) has the time complexity of $\mathcal{O}(pKMD \sqrt{\tau})$ where $pKMD$ is the number of non-zero elements in $(\Filter \mask^\top)$ and $\tau$ is the condition number of $(A^\top A + \rho I)$ where $A = \Filter \mask^\top$.
-With a reasonable selection of the subsampling rate, this time complexity is comparable with that of frequency-domain solvers.
-As for updating $\filter$, it takes $\mathcal{O}(K^2M^2)$ time.
-This is comparable to $\mathcal{O}(K^2D)$ in common CSC settings ($M \ll D$), while it requires multiple iterations (ADMM iterations) in frequency domain to compute $\filter$ and only a single pass required by the proposed method, which greatly reduces the computation time.
-Overall, the proposed method has the time complexity of $\mathcal{O}(pKMD \sqrt{\tau} + K^2M^2)$.
+The time complexity of updating $\code$ in our SBCSC algorithm using
+Conjugate Gradient is $\mathcal{O}(pKMD \sqrt{\tau})$, where $pKMD$ is
+the number of non-zero elements in $(\Filter \mask^\top)$ and $\tau$
+is the condition number of $(\matA^\top \matA + \rho I)$ where $\matA
+= \Filter \mask^\top$. With a reasonable selection of the subsampling
+rate, this time complexity is comparable to that of frequency-domain
+solvers.
 
-The time complexity of SOCSC is similar to that of SBCSC, apart from two additional steps to update the surrogate matrices.
-Updating $\surC$ and $\surB$ involves computing $\Code^\top\Code$ and $\Code^\top x$.
-Though $\Code$ has the dimensions of $D \times KM$, it is a highly sparse matrix with only $\mathcal{O}(D)$ non-zero elements.
-Therefore, the total time complexity will not be obviously affected.
+Updating the filters $\filter$ takes $\mathcal{O}(K^2M^2)$ time. This
+is comparable to $\mathcal{O}(K^2D)$ in the common CSC setting ($M \ll
+D$). However, multiple ADMM iterations are required in the frequency
+domain to compute $\filter$ while only a single pass is required by
+the proposed method, which greatly reduces the computation
+time. Overall, the proposed method has the time complexity of
+$\mathcal{O}(pKMD \sqrt{\tau} + K^2M^2)$.
+
+The time complexity of SOCSC is similar to that of SBCSC, apart from
+two additional steps to update the surrogate matrices. Updating
+$\surC$ and $\surB$ involves computing $\Code^\top\Code$ and
+$\Code^\top x$. Although $\Code$ has dimensions of $D \times KM$, it
+is a highly sparse matrix with only $\mathcal{O}(D)$ non-zero
+elements. Therefore, the total performance is not affected
+significantly.
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2018-11-08 cvpr2019/main.tex
WH edits on full text

--- 2018-10-25 cvpr2019/egpaper_for_review.tex
@@
 \begin{abstract}
-The minimization problems formulated in Convolutional Sparse Coding (CSC) have been solved in frequency domain by modern approaches owing to the improved computing efficiency.
-However, solving the problem in frequency domain automatically assumes circular boundary conditions, and also it is restricted by imposing modern optimization strategies for this specific problem.
-In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes.
-Afterwards, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes.
-In both cases, we show experimentally that the proposed method outperforms the state-of-the-art frequency-domain solvers with a reasonable selection of the subsampling rate.
-At last, we learn the over-complete dictionary from large-scale datasets, which demonstrates a better sparse representation of the natural images on account of more abundant learned image features.
+  State-of-the-art methods for Convolutional Sparse Coding usually
+  employ Fourier-domain solvers in order to speed up the convolution
+  operators. However, this approach is not without shortcomings. For
+  example, Fourier-domain representations implicitly assume circular
+  boundary conditions and make it hard to fully exploit the sparsity
+  of the problem as well as the small spatial support of the filters.
+
+  %% The minimization problems formulated in                               %%
+  %% (CSC) have been solved in frequency domain by modern approaches owing %%
+  %% to the improved computing efficiency. However, solving the problem in %%
+  %% frequency domain automatically assumes circular boundary conditions,  %%
+  %% and also it is restricted by imposing modern optimization strategies  %%
+  %% for this specific problem.                                            %%
+
+  In this work, we propose a novel stochastic spatial-domain solver,
+  in which a randomized subsampling strategy is introduced during the
+  learning sparse codes. Afterwards, we extend the proposed strategy
+  in conjunction with online learning, scaling the CSC model up to
+  very large sample sizes. In both cases, we show experimentally that
+  the proposed subsampling strategy, with a reasonable selection of
+  the subsampling rate, outperforms the state-of-the-art
+  frequency-domain solvers in terms of execution time without losing
+  the learning quality. Finally, we evaluate the effectiveness of the
+  over-complete dictionary learned from large-scale datasets that has
+  not been studied by precedent CSC work, which demonstrates an
+  improved sparse representation of the natural images on account of
+  more abundant learned image features.
 \end{abstract}
@@
 \end{document}
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2018-11-10 cvpr2019/Introduction.tex
edits based on wolfgang's comments

@@
 
-Of course this convolutional approach is also a the heart of many deep
+Of course this convolutional approach is also the heart of many deep
 learning-based methods in the form of
@@
 (ADMM)~\cite{boyd2011distributed} to separate the linear least squares
-parts terms from the non-smooth terms in the optimization
+parts from the non-smooth terms in the optimization
 problem. These approaches show tremendous improvements over prior

### 2018-11-10 cvpr2019/Results.tex
edits based on wolfgang's comments

@@
 
-{\bfseries Reconstruction}. The SBSC-learned filters with a
+{\bfseries Reconstruction}. The SBCSC-learned filters with a
 subsampling rate of $p=0.1$ are shown in the bottom of
@@
 respect to the PSNR value. Furthermore, the learning process
-only takes about $50\%$ of the time for our method.\todo{specific
+only takes about $50\%$ of the time for our method. Specifically, SBCSC takes 170 seconds and the comparable method takes 350 seconds for 14 iterations on a Core i7 PC. \todo{specific
   times here!}.
@@
 reconstruction performance of the learned filters. In terms of runtime
-comparison, however, the proposed method runs at least 5 times faster
-than the comparison method. The supplement shows additional comparisons
-for the other datasets.
+comparison, however, the proposed method runs at least $6$ times faster
+than the comparison method.
+Specifically, SOCSC takes 70 seconds and the comparable method takes 440 seconds on a Core i7 PC to process all 10 training images.
+The supplement shows additional comparisons for the other datasets.
 
@@
 Bottom: Testing PSNR with respect to execution time.
-While the quality of the output is comparable, our method achieves $5 \times$ speedup.}
+While the quality of the output is comparable, our method achieves $6 \times$ speedup.}
 \label{fig:onlineSmall}
@@
 learn visually similar under-complete dictionary, while the proposed
-method takes $5 \times$ less training time than the comparison
+method takes $6 \times$ less training time than the comparison
 method. The learned over-complete dictionary is composed of

### 2018-11-10 cvpr2019/SCSCmodel.tex
edits based on wolfgang's comments

@@
 implement the CSC learning problem~\eqref{eq:CSCmodel} iteratively,
-where in each iteration we only consider a random subset
-$\mathcal{M}_k(\code_k)$ of the codes:
+where at $\ite$-th iteration we only consider a random subset
+$\mathcal{M}_k^{\ite}(\code_k)$ of the codes:
 \begin{align}
-    &\mini{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k(\code_k) \|_1  \nonumber \\
+    &\mini{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k^{\ite}(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k^{\ite}(\code_k) \|_1  \nonumber \\
     &\text{subject to} ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\}.
@@
   irregularly subsampled signal! Lets discuss on Sunday.}
-Here $\mathcal{M}_k(\code_k)$ is the operation to subsample the
+Here $\mathcal{M}_k^{\ite}(\code_k)$ is the operation to subsample the
 corresponding code $\code_k$ following a Bernoulli distribution with
-probability $p$.
+probability $p$, drawn at current iteration.
 %The probability value $p$ controls the percentage of
@@
 \begin{equation} \label{eq:updatingCode}
-    \code_{opt} = \minimize{\code} \frac{1}{2}\|\signal - (\Filter \mask^\top)(\mask \code) \|_2^2 + \lambda \|\mask \code\|_1,
+    \code^{\ite} = \minimize{\code} \frac{1}{2}\|\signal - (\Filter^{\ite-1} (\mask^{\ite})^\top) (\mask^{\ite} \code) \|_2^2 + \lambda \|\mask^{\ite} \code\|_1,
 \end{equation}
 \todo{add outer loop variable}
-where $\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D
-  \times DK}$, $\code = [\code_1, \dots, \code_K] \in
+where $\Filter^{\ite-1} = [\Filter_1^{\ite-1}, \dots, \Filter_K^{\ite-1}] \in \mathbb{R}^{D
+  \times DK}$, which is constructed from the dictionary learned by
+$(\ite-1)$-th iteration, $\code = [\code_1, \dots, \code_K] \in
 \mathbb{R}^{DK}$. The convolution operators are expressed as a matrix
@@
 \code_k$. Therefore, each part of $\Filter$ is a Toeplitz
-matrix. Matrix $\mask$ is a $\mathbb{R}^{pDk \times DK}$ random
+matrix. Matrix $\mask^{\ite}$ is a $\mathbb{R}^{pDk \times DK}$ random
 diagonal matrix with $1$ for the entries corresponding to the sampled
 sparse codes and $0$ elsewhere, performing the function of
-$\mathcal{M}(\code)$. Matrix $\mask$ will be redrawn at each
-iteration. It is worth stressing that $(\Filter \mask^\top)$ is not
+$\mathcal{M}^{\ite}(\code)$. Matrix $\mask^{\ite}$ will be redrawn at each
+iteration. It is worth stressing that $(\Filter^{\ite-1} (\mask^{\ite})^\top)$ is not
 performing a subsampling operation on the dictionary, \note{not sure
-  what this is supposed to say:} which is
-essentially to remove the columns in $\Filter$ those are filtered out
-by $\mathcal{M}(\code)$.
+  what this is supposed to say:} which aims to remove the columns in $\Filter^{\ite}$ those are filtered out
+by $\mathcal{M}^{\ite}(\code)$.
 \note{See notation issue above; we need to discuss this next week:}
@@
 
-After obtaining the subsampled sparse codes, we can then project them
+After computing the subsampled sparse codes $\mathcal{M}^{\ite}(\code)$, we can then project them
 onto the original spatial support by substituting $0$ for the
-masked-out vlaues. Afterwards, the dictionary can be updated by:
+masked-out values, obtaining $z^{\ite}$. Afterwards, the dictionary can be updated by:
 \begin{equation} \label{eq:updatingFilter}
 \begin{split}
-   & \filter_{opt} = \minimize{\filter} \frac{1}{2}\|\signal - \Code \filter \|_2^2 \\
+   & \filter^{\ite} = \minimize{\filter} \frac{1}{2}\|\signal - \Code^{\ite} \filter \|_2^2 \\
    & \text{subject to}  ~ \|\filter_k\|^2_2 \leq 1 ~ \forall k \in \{1,\dots,K\},
@@
 \end{equation}
-\todo{add outer loop variable} where $\Code= [\Code_1, \dots, \Code_K]
+\todo{add outer loop variable} where $\Code^{\ite}= [\Code_1^{\ite}, \dots, \Code_K^{\ite}]
 \in \mathbb{R}^{D \times MK}$ is a concatenation of Toeplitz matrices,
-and $\Code_k$ is constructed from the associated $\code_k$, $\filter=
+and $\Code_k^{\ite}$ is constructed from the associated $\code_k^{\ite}$, $\filter=
 [\filter_1,\dots,\filter_K] \in \mathbb{R}^{MK}$ such that $ \Code
@@
 shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total
-input images, $\code^i$ is the sparse code associated with $i$-th
-image, and $p$ is the uniform probability for one code been
+input images, $(\code^i)^{\ite}$ is the sparse code associated with $i$-th
+image at $\ite$-th iteration, and $p$ is the uniform probability for one code been
 selected. We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this
@@
 \begin{algorithmic}[1]
-\State $\text{Initialize } \filter, ~p$
+\State $\text{Initialize}  ~ \ite=0, ~\filter^t, ~p$
 \While {not converge}
-    \State $ \text{Randomly sample }\code \text{ with rate } p $
+    \State $\ite \gets \ite+1$
+    \State $ \text{Randomly sample }\code^{\ite} \text{ with rate } p $
     \For{i=1 to N}
-        \State $ \text{Update } \code^i \text{ by solving problem~(\ref{eq:updatingCode}})$
+        \State $ \text{Compute } (\code^i)^{\ite} \text{ by solving problem~(\ref{eq:updatingCode}})$
     \EndFor
-    \State $\text{Update } \filter \text{ by solving problem~(\ref{eq:updatingFilter}})$
+    \State $\text{Compute } \filter^{\ite} \text{ by solving problem~(\ref{eq:updatingFilter}})$
 \EndWhile
@@
 \subsection{Stochastic Online CSC (SOCSC)}
+
+\begin{algorithm}[H]
+\caption{SOCSC} \label{algo:SOCSC}
+\begin{algorithmic}[1]
+\State $\text{Initialize} ~ t=0, ~\filter^t, ~p, ~\surC^t = 0, ~\surB^t = 0$
+\While {not converge}
+    \State $t \gets t+1$
+    \State $ \text{draw } \signal^t \text{ from training images} $
+    \State $ \text{Randomly sample }\code^t \text{ with rate } p $
+    \State $ \text{Compute } \code^t \text{ by solving problem~(\ref{eq:updatingCodeOnline}) using } \filter^{t-1}$
+    \State Compute $\surC^t$ and $\surB^t$ by Eq.~\ref{eq:updateSur}
+    \State Compute $\filter^t$ by solving problem~(\ref{eq:updatingFilterOnline})
+\EndWhile
+\end{algorithmic}
+\todo{Find the best place for this algorithm (probably higher up)}
+\end{algorithm}
+
 In order to address this scalability issue, we can tackle the
@@
 \begin{equation} \label{eq:updatingCodeOnline}
-    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} (\mask^t)^\top)(\mask^t \code) \|_2^2 + \lambda \|\mask^t \code\|_1,
+    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} (\mask^t)^\top)(\mask^t \code) \|_2^2 + \lambda \|\mask^t \code\|_1.
 \end{equation}
@@
   earlier in the paper.}
-where $\Filter^{t-1}$ is constructed from the dictionary learned by
-$(t-1)$th iteration, and $\mask^t$ is the subsample matrix at current
-iteration, which is iteratively redrawn as in SBCSC. After obtaining
+The only difference between Eq. ~\ref{eq:updatingCode} is that $\signal^t$ only contains a portion of the total images. After obtaining
 the sparse codes, the dictionary is updated by:
@@
 that for SBCSC.
-
-\begin{algorithm}[H]
-\caption{SOCSC} \label{algo:SOCSC}
-\begin{algorithmic}[1]
-\State $\text{Initialize} ~ t=0, ~\filter^t, ~p, ~\surC^t = 0, ~\surB^t = 0$
-\While {not converge}
-    \State $t \gets t+1$
-    \State $ \text{draw } \signal^t \text{ from training images} $
-    \State $ \text{Randomly sample }\code^t \text{ with rate } p $
-    \State $ \text{Compute } \code^t \text{ by solving problem~(\ref{eq:updatingCodeOnline}) using } \filter^{t-1}$
-    \State Compute $\surC^t$ and $\surB^t$ by Eq.~\ref{eq:updateSur}
-    \State Compute $\filter^t$ by solving problem~(\ref{eq:updatingFilterOnline})
-\EndWhile
-\end{algorithmic}
-\todo{Find the best place for this algorithm (probably higher up)}
-\end{algorithm}
 

### 2018-11-10 cvpr2019/supplement.tex
minor edits
edits based on wolfgang's comments

@@
   \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
+  \vspace{0.1cm}
 \end{subfigure}
@@
 We then compare SOCSC with the state-of-the-art online algorithm~\cite{liu-2018-first} on city dataset, the results of which are shown in Fig.\ \ref{fig:onlineSmall-city}.
-Similar to the results presented in Fig.\ \ref{fig:onlineSmall}, our method obtains comparable outcomes, meanwhile, achieves roughly $5 \times$ speedup.
+Similar to the results presented in Fig.\ \ref{fig:onlineSmall}, our method obtains comparable outcomes, meanwhile, achieves roughly $6 \times$ speedup.
 

### 2018-11-11 cvpr2019/Introduction.tex
typo

@@
 
-Of course this convolutional approach is also the heart of many deep
+Of course this convolutional approach is also at the heart of many deep
 learning-based methods in the form of

### 2018-11-12 cvpr2019/SCSCmodel.tex
fix grammar

@@
 \subsection{The Model}
-\note{The previous description was not accurate: Eq.2 is not a variant
-  of the CSC model, and does not replace Eq.1! Eq.2 is supposed to be
-  used inside an outer loop to implement Eq.1. This outer loop is an
-  implementation of CSC and Eg.1.  In order to really explain this
-  properly, we need to introduce an outer loop parameter for both
-  $\mask$ and $\mathcal{M}$.}
-
 Based on the strong sparsity of the codes $\code$, we propose to
@@
 $\mathcal{M}_k^{\ite}(\code_k)$ of the codes:
-\begin{align}
-    &\mini{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k^{\ite}(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k^{\ite}(\code_k) \|_1  \nonumber \\
+\begin{equation} \label{eq:updatingFilter}
+\begin{split}
+    & (\filter^{\ite},\code^{\ite}) =  \\
+    &\minimize{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k^{\ite}(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k^{\ite}(\code_k) \|_1  \\
     &\text{subject to} ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\}.
-\end{align}
-\todo{add outer loop variable}
-\todo{There are some notational issues here -- convolution with an
-  irregularly subsampled signal! Lets discuss on Sunday.}
-Here $\mathcal{M}_k^{\ite}(\code_k)$ is the operation to subsample the
+\end{split}
+\end{equation}
+Here $\mathcal{M}_k^{\ite}(\code_k)$ is a $\mathbb{R}^D \to \mathbb{R}^D$ operator subsampling the
 corresponding code $\code_k$ following a Bernoulli distribution with
@@
 problem, we can apply a coordinate descent algorithm, alternating on
-subproblems of $\mathcal{M}(\code)$ and $\filter$, to solve the above
+subproblems of $\mathcal{M}^{\ite}(\code)$ and $\filter$, to solve the above
 bi-convex optimization problem. Specifically, the modified
@@
 \begin{equation} \label{eq:updatingCode}
-    \code^{\ite} = \minimize{\code} \frac{1}{2}\|\signal - (\Filter^{\ite-1} (\mask^{\ite})^\top) (\mask^{\ite} \code) \|_2^2 + \lambda \|\mask^{\ite} \code\|_1,
+    \code^{\ite} = \minimize{\code} \frac{1}{2}\|\signal - \Filter^{\ite-1} \mask^{\ite} \code \|_2^2 + \lambda \|\mask^{\ite} \code\|_1,
 \end{equation}
-\todo{add outer loop variable}
 where $\Filter^{\ite-1} = [\Filter_1^{\ite-1}, \dots, \Filter_K^{\ite-1}] \in \mathbb{R}^{D
@@
 \code_k$. Therefore, each part of $\Filter$ is a Toeplitz
-matrix. Matrix $\mask^{\ite}$ is a $\mathbb{R}^{pDk \times DK}$ random
-diagonal matrix with $1$ for the entries corresponding to the sampled
+matrix. Matrix $\mask^{\ite}$ is a $\mathbb{R}^{Dk \times DK}$ random binary
+diagonal matrix with $1$s on the diagonal entries corresponding to the sampled
 sparse codes and $0$ elsewhere, performing the function of
-$\mathcal{M}^{\ite}(\code)$. Matrix $\mask^{\ite}$ will be redrawn at each
-iteration. It is worth stressing that $(\Filter^{\ite-1} (\mask^{\ite})^\top)$ is not
-performing a subsampling operation on the dictionary, \note{not sure
-  what this is supposed to say:} which aims to remove the columns in $\Filter^{\ite}$ those are filtered out
-by $\mathcal{M}^{\ite}(\code)$.
-\note{See notation issue above; we need to discuss this next week:}
+$\mathcal{M}^{\ite}(\code)$, which satisfies $\mathrm{Tr}(\mask^{\ite}) = pDK$. When $p=1$, $\mask^{\ite}$ is just an identity matrix.
 Due to the introduced subsampling matrix, the
 convolution operator cannot be implemented in the Fourier
-domain. However, due to the subsampling
+domain. However, owing to the subsampling
 strategy, the number of variables that need to be computed for this
@@
 onto the original spatial support by substituting $0$ for the
-masked-out values, obtaining $z^{\ite}$. Afterwards, the dictionary can be updated by:
+masked-out values, obtaining $\code^{\ite}$. Afterwards, the dictionary can be updated by:
 \begin{equation} \label{eq:updatingFilter}
@@
 \end{equation}
-\todo{add outer loop variable} where $\Code^{\ite}= [\Code_1^{\ite}, \dots, \Code_K^{\ite}]
+where $\Code^{\ite}= [\Code_1^{\ite}, \dots, \Code_K^{\ite}]
 \in \mathbb{R}^{D \times MK}$ is a concatenation of Toeplitz matrices,
@@
 \end{algorithmic}
-\todo{Find the best place for this algorithm (probably higher up)}
 \end{algorithm}
@@
 \begin{equation} \label{eq:updatingCodeOnline}
-    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - (\Filter^{t-1} (\mask^t)^\top)(\mask^t \code) \|_2^2 + \lambda \|\mask^t \code\|_1.
+    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - \Filter^{t-1}\mask^t \code \|_2^2 + \lambda \|\mask^t \code\|_1.
 \end{equation}
-\note{Here we have $t$ as an iteration variable now -- I don't think
-  this is a good choice ($t$ is usually reserved for continuous
-  values, better would be $i$ or $j$, and we need to introduce these
-  earlier in the paper.}
 The only difference between Eq. ~\ref{eq:updatingCode} is that $\signal^t$ only contains a portion of the total images. After obtaining

### 2018-11-13 cvpr2019/Results.tex
fix grammar
edits

@@
 competing methods.
-\note{Not sure what you want to say here -- fix grammar:}
-Notice that the comparison method has a relatively
-high objective value during the first $6-8$ iterations due to
-different splitting strategies are applied and subproblems are
-interleaved on the primary variables~\cite{wohlberg2016efficient},
-though it converges to an optimum with comparable objective after 10
-iterations. In summary, the convergence behaviors of the proposed
+
+We have observed that the comparison method has a relatively
+high objective value during the first $6-8$ iterations.
+The reason is that it introduces an additional mask term handling the boundary issues, therefore different splitting strategies are utilized and the subproblems are
+interleaved on their primary variables (in some sense, the primary variables can be regarded as intermediate results in the ADMM iteration).
+See~\cite{wohlberg2016efficient} for details.
+Despite of this, it converges to an optimum with comparable objective after 10 iterations.
+In summary, the convergence behaviors of the proposed
 algorithm is only slightly influenced by the subsampling strategy
@@
 respect to the PSNR value. Furthermore, the learning process
-only takes about $50\%$ of the time for our method. Specifically, SBCSC takes 170 seconds and the comparable method takes 350 seconds for 14 iterations on a Core i7 PC. \todo{specific
-  times here!}.
-\note{So, how does Bis' work from last year compare in terms of
-  quality and time? It should
-  have much better dictionaries than~\cite{heide2015fast} as well.}
+only takes about $50\%$ of the time for our method. Specifically, SBCSC takes 170 seconds and the comparable method takes 350 seconds for 14 iterations on a Core i7 PC.
 
@@
 
-The runtime comparisons for various mini-batch sizes are shown in the
-bottom of Fig.~\ref{fig:overComDicAndMinibatch}. Note that larger
-$\eta$ will result in a smaller number of iterations to process all
-$1000$ samples. The plots show that a larger mini-batch size will
-generally lead to a greater progress in first few training steps,
-though it takes additional running time and memory. Overall,
-mini-batched updates provides a more runtime efficient learning
-process in the online-based CSC model, and according to the obtained
-experimental results, $\eta=20$ achieves a one order of magnitude
-speedup over $\eta=1$ to reach a a comparable level of
-convergence. Since computing sparse codes is a data-independent
-process, this mini-batched approach can be further accelerated in a
-distributed-computing system.
 \begin{figure}[h]
@@
 
+The runtime comparisons for various mini-batch sizes are shown in the
+bottom of Fig.~\ref{fig:overComDicAndMinibatch}. Note that larger
+$\eta$ will result in a smaller number of iterations to process all
+$1000$ samples. The plots show that a larger mini-batch size will
+generally lead to a greater progress in first few training steps,
+though it takes additional running time and memory. Overall,
+mini-batched updates provides a more runtime efficient learning
+process in the online-based CSC model, and according to the obtained
+experimental results, $\eta=20$ achieves a one order of magnitude
+speedup over $\eta=1$ to reach a a comparable level of
+convergence. Since computing sparse codes is a data-independent
+process, this mini-batched approach can be further accelerated in a
+distributed-computing system.
+
 % --- DO NOT DELETE ---

### 2018-11-13 cvpr2019/SCSCmodel.tex
edits

@@
 where at $\ite$-th iteration we only consider a random subset
-$\mathcal{M}_k^{\ite}(\code_k)$ of the codes:
+$\mathcal{M}^{\ite}(\code)$ of the codes:
 \begin{equation} \label{eq:updatingFilter}
@@
 corresponding code $\code_k$ following a Bernoulli distribution with
-probability $p$, drawn at current iteration.
+probability $p$, drawn at current iteration. Concretely, it retains the sampled codes and zero out the others.
 %The probability value $p$ controls the percentage of
@@
 the sparse codes at chosen positions in each iteration, and
-accordingly, the update of dictionary $d$ is based on the selected
+accordingly, the update of dictionary $\filter$ is based on the selected
 portion of the sparse codes. Similar to solving the classical CSC
@@
 matrix. Matrix $\mask^{\ite}$ is a $\mathbb{R}^{Dk \times DK}$ random binary
-diagonal matrix with $1$s on the diagonal entries corresponding to the sampled
-sparse codes and $0$ elsewhere, performing the function of
+diagonal matrix with $1$s on the diagonal entries corresponding to the sampled codes and $0$ elsewhere, performing the function of
 $\mathcal{M}^{\ite}(\code)$, which satisfies $\mathrm{Tr}(\mask^{\ite}) = pDK$. When $p=1$, $\mask^{\ite}$ is just an identity matrix.
@@
 
-\note{I have no idea what the next two sentences are supposed to say:}
 The work of~\cite{mensch2016dictionary} also applies a so-called
-stochastic subsampling strategy for dictionary learning, while the
+stochastic subsampling strategy for dictionary learning, where the
 subsampling is randomly performed on the observed signals, differing
@@
 factorizing matrix that is large in both dimensions. Although CSC can
-be expressed in a form similar to matrix factorization, the two
+be expressed in a similar mathematical formula as matrix factorization, the two
 problems are in practice quite different due to the convolutional
-nature of the CSC model.  One can think of our proposed randomization
-approach as a variant of the stochastic Frank-Wolfe
+property of the CSC model. Our proposed randomization
+approach shares a similar idea as utilized in the stochastic Frank-Wolfe
 algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which
@@
 that the codes are highly sparse, the original signals can still be
-represented by a portion of the codes with a reasonable subsampling
-rate. Therefore the convergence of the proposed algorithm will not be
+represented by a portion of the codes under a reasonable subsampling
+rate. Therefore, the convergence of the proposed algorithm will not be
 significantly affected by the subsampling manipulation, unlike the
@@
 %iterations.
-Problem~\ref{eq:updatingFilter} is a quadratic constrained
+Problem~\eqref{eq:updatingFilter} is a quadratic constrained
 quadratic programming (QCQP) problem, and it can be efficiently solved
@@
 
-The time complexity of SOCSC is similar to that of SBCSC, apart from
+The time complexity of SOCSC for one data pass is similar to that of SBCSC, apart from
 two additional steps to update the surrogate matrices. Updating

### 2018-11-14 code/SBCSC/BCDproj.m
update code

@@ -1,0 +1,23 @@
+function d = BCDproj( Z, b, d_old, k, num_kernel, MAX_ITER )
+    
+    d = d_old;
+    r = b - Z*d_old;
+    
+    lip = zeros( num_kernel, 1);
+    for i=1:num_kernel
+        ind = (i-1)*k+1 : i*k;
+        lip(i) =  norm(  full(Z(:,ind)'* Z(:,ind)) );
+    end
+    
+    for i=1:MAX_ITER
+       for j=1:num_kernel
+           ind = (j-1)*k+1 : j*k;
+           h = Z(:, ind )'*r / lip(j) ;           
+           d_new = d(ind) + h;
+           d_new = d_new ./ max( norm(d_new), 1 );          
+           r = r + Z(:, ind)*( d(ind) - d_new );
+           d(ind) = d_new;
+       end
+%        fprintf('%10.4f\n', norm(Z*d-b) );
+    end
+end

### 2018-11-14 code/SBCSC/BatchStochasticCSC.m

@@ -1,5 +1,5 @@
 %% first code for CSC in spatial domain
-function [ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
+function [ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, hit_rate, lambda)
 
     k = kernel_size(1);           
     num_kernel  = kernel_size(end);
@@ -17,23 +17,23 @@ function [ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
     d = d(:);
     
     %% parameters
-    outer_ite = 10;
-    max_it_z = 10;
-    max_it_d = 10;
+    outer_ite = 12;
+    max_ite_z  = 10;
+    bcd_ite    = 1;
     
-    batch_size = num_image;   
-    rho_d = 50*lambda;
-    rho_z = 10*lambda;
-    hit_rate = 0.1;    % probability for choosing one specific code 
+    batch_size = num_image;        
+    
+    % rho_z needs to be propoerly chosen for better convergence
+    rho_z = 10;
+    if( hit_rate == 1 )
+        rho_z = 15;
+    end
+    
     total_time = 0;
+    z          = zeros( n*n*num_kernel, batch_size );
+    cur_image  = 1:num_image; 
     
-    u_d     = zeros( k*k*num_kernel, 1 );
-    x_hat_d = zeros( k*k*num_kernel, 1 );
-    z       = zeros( n*n*num_kernel, batch_size );
-
-    cur_image = 1:num_image; 
     for ite = 1:outer_ite
-
         %% compute codes
         t_train = tic;
         
@@ -44,9 +44,9 @@ function [ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
         [ind1, ind2, v] = find( d_ind(:,ind) );
         D = sparse( ind1, ind2, d(v), n*n, numel(ind) );
         
-        z_tmp = lasso(D, b(:,cur_image), lambda, rho_z, 1.8, max_it_z, 1);
+        z_tmp = lasso(D, b(:,cur_image), lambda, rho_z, 1.8, max_ite_z, 1);
         
-        % project the results onto its original domain
+        % project the results onto its original spatial support
         z = zeros(n*n*num_kernel, batch_size);
         z(ind,:) = z_tmp;
         
[…]

### 2018-11-14 code/SBCSC/l2proj.m

@@ -1,58 +1,0 @@
-function z = l2proj(A, b, d, rho, alpha, k, num_kernel, MAX_ITER)
-
-ABSTOL   = 1e-4;
-RELTOL   = 1e-2;
-
-[m, n] = size(A);
-
-% save a matrix-vector multiply
-Atb = A'*b;
-
-if isempty(d)
-    z = zeros(n,1);
-else
-    z = d;
-end
-
-x_hat = zeros(n,1);
-u = zeros(n,1);
-
-% cache the factorization
-A_cal = @(p) A'*(A*p) + rho.*p;
-
-for i = 1:MAX_ITER
-
-    % x-update
-    q = Atb + rho*(z - u);    % temporary value
-
-    x = conj_grad(q, A_cal, x_hat, 100, 1e-5, 2);
-
-    % z-update with relaxation
-    zold = z;
-    x_hat = alpha*x + (1 - alpha)*zold;
-    z = proj_l2(x_hat + u, k, num_kernel);
-    % u-update
-    u = u + (x_hat - z);
-
-
-    history.r_norm(i)  = norm(x - z, 'fro');
-    history.s_norm(i)  = norm(-rho*(z - zold), 'fro');
-
-    history.eps_pri(i) = sqrt(n)*ABSTOL + RELTOL*max(norm(x, 'fro'), norm(-z,'fro'));
-    history.eps_dual(i)= sqrt(n)*ABSTOL + RELTOL*norm(rho*u, 'fro');
-
-    if (history.r_norm(i) < history.eps_pri(i) && ...
-       history.s_norm(i) < history.eps_dual(i))
-         break;
-    end
-
-end
-
-end
-
-function z = proj_l2(x, k, num_kernel)
-    z = zeros(size(x));
-    for i=1:num_kernel
-       z((i-1)*k+1:i*k) =  x((i-1)*k+1:i*k) ./ max( norm(x((i-1)*k+1:i*k)), 1);
-    end
-end

### 2018-11-14 code/SBCSC/main.m

@@ -1,25 +1,32 @@
 addpath('../image_helpers');
-CONTRAST_NORMALIZE = 'local_cn'; 
-ZERO_MEAN = 1;   
-COLOR_IMAGES = 'gray'; 
 
-% read images
-% we suggest to work on 100*100 (square) image patches (avoid working on large images and
+%% read images
+% we suggest to work on square image patches (avoid working on large images and
 % large number of filters at the same time)
-[b] = CreateImages('../datasets/city_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-b = reshape(b, size(b,1), size(b,2), [] );
+
+% CONTRAST_NORMALIZE = 'local_cn'; 
+% ZERO_MEAN = 1;   
+% COLOR_IMAGES = 'gray'; 
+% [b] = CreateImages('../datasets/fruit_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES);
+% b = reshape(b, size(b,1), size(b,2), [] );
+
+load city;
+% load fruit;
 
 %% Define the parameters
 kernel_size = [11, 11, 100];
-lambda = 1;
+lambda = 1;        % different normalize methods may lead to different lambda and rho
+hit_rate = 0.1;    % probability for choosing one specific code
 
 %% cache the vector to matrix info for efficient indexing
-% It may take some time (roughly 40s), while you only need to compute it once and store it
-d_ind = constructDicIndex(  kernel_size, size(b,1), size(b,2) );
-z_ind = constructCodeIndex( kernel_size, size(b,1) );
+% It may take some time (roughly 30s), while you only need to compute it once and store it
+
+% d_ind = constructDicIndex(  kernel_size, size(b,1), size(b,2) );
+% z_ind = constructCodeIndex( kernel_size, size(b,1) );
+load d_ind; load z_ind;
 
 %% Batch stochastic CSC
-[ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, lambda);
+[ d, z ]  = BatchStochasticCSC(b, d_ind, z_ind, kernel_size, hit_rate, lambda);
 
 %% visualize dictionary
 plotDic( d, 10, max(d(:)), min(d(:)) );

### 2018-11-14 code/SOCSC/BCDdicUpdate.m

@@ -1,0 +1,21 @@
+function d = BCDdicUpdate(C, B, d_old, k, num_kernel, MAX_ITER )
+       
+    d = d_old;
+
+    lip = zeros( num_kernel, 1);
+    for i=1:num_kernel
+        ind = (i-1)*k+1 : i*k;
+        lip(i) =  norm( C(ind, ind) );
+    end
+
+    for i=1:MAX_ITER
+       for j=1:num_kernel
+           ind = (j-1)*k+1 : j*k;
+           h = ( B(ind) - C(ind,:)*d ) ./ lip(j) ;           
+           d_new = d(ind) + h;
+           d_new = d_new ./ max( norm(d_new), 1 );          
+           d(ind) = d_new;
+       end
+    end
+
+end

### 2018-11-14 code/SOCSC/OnlineStochasticCSC.m

@@ -1,5 +1,5 @@
 %% online code for CSC in spatial domain
-function [ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
+function [ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, hit_rate, lambda)
 
     k = kernel_size(1);           
     num_kernel  = kernel_size(end);
@@ -17,14 +17,12 @@ function [ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
     d = d(:);
     
     %% set up parameters
-    outer_ite = 10;  % num_image;
-    max_it_z = 10;
-    max_it_d = 10;
+    outer_ite = num_image;
+    max_ite_z = 10;
+    bcd_ite    = 1;
     
     batch_size = 1;
-    rho_d = 50*lambda;
-    rho_z = 10*lambda;
-    hit_rate = 0.1;    % probability for choosing one specific code 
+    rho_z = 10;
     gamma = 1;         % forget factor
     total_time = 0;
     
@@ -32,7 +30,6 @@ function [ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
     sequence = randperm(outer_ite*batch_size);
     
     for ite = 1:outer_ite
-
         %% compute sparse codes
         t_train = tic;
         
@@ -45,13 +42,13 @@ function [ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda)
         [ind1, ind2, v] = find( d_ind(:,ind) );        
         D = sparse( ind1, ind2, d(v), n*n, numel(ind) );
         
-        % if batch_size is large, use Cholesky decomposition
-        % otherwise use conjugate gradient.
-        % this is important for an efficient compute especially when
+        % if batch_size is large, use Cholesky decomposition (1)
+        % otherwise use conjugate gradient (2).
+        % this is essential for an efficient computation especially when
         % batch_size is large.
-        z_tmp = lasso(D, b(:,cur_image), lambda, rho_z, 1.8, max_it_z, 2);
+        z_tmp = lasso(D, b(:,cur_image), lambda, rho_z, 1.8, max_ite_z, 2);
         
-        % project the results onto its original domain
+        % project the results onto its original spatial support
[…]

### 2018-11-14 code/SOCSC/dicUpdate.m

@@ -1,55 +1,0 @@
-function z = dicUpdate(A, Atb, d, rho, alpha, k, num_kernel, MAX_ITER)
-
-ABSTOL   = 1e-4;
-RELTOL   = 1e-2;
-
-[~, n] = size(A);
-
-if isempty(d)
-    z = zeros(n,1);
-else
-    z = d;
-end
-
-x_hat = zeros(n,1);
-u = zeros(n,1);
-
-% [L U] = factor(A, rho);
-A_cal = @(p) A*p + rho.*p;
-
-for i = 1:MAX_ITER
-
-    % x-update
-    q = Atb + rho*(z - u);    % temporary value
-
-%     x = U \ (L \ q);
-    x = conj_grad(q, A_cal, x_hat, 100, 1e-5, 2);
-
-    % z-update with relaxation
-    zold = z;
-    x_hat = alpha*x + (1 - alpha)*zold;
-    z = proj_l2(x_hat + u, k, num_kernel);
-    % u-update
-    u = u + (x_hat - z);
-
-    history.r_norm(i)  = norm(x - z, 'fro');
-    history.s_norm(i)  = norm(-rho*(z - zold), 'fro');
-
-    history.eps_pri(i) = sqrt(n)*ABSTOL + RELTOL*max(norm(x, 'fro'), norm(-z,'fro'));
-    history.eps_dual(i)= sqrt(n)*ABSTOL + RELTOL*norm(rho*u, 'fro');
-
-    if (history.r_norm(i) < history.eps_pri(i) && ...
-       history.s_norm(i) < history.eps_dual(i))
-         break;
-    end
-
-end
-
-end
-
-function z = proj_l2(x, k, num_kernel)
-    z = zeros(size(x));
-    for i=1:num_kernel
-       z((i-1)*k+1:i*k) =  x((i-1)*k+1:i*k) ./ max( norm(x((i-1)*k+1:i*k)), 1);
-    end
-end

### 2018-11-14 code/SOCSC/main.m

@@ -1,24 +1,30 @@
 addpath('../image_helpers');
-CONTRAST_NORMALIZE = 'local_cn'; 
-ZERO_MEAN = 1;   
-COLOR_IMAGES = 'gray'; 
+
 % read images
-% we suggest to work on 100*100 (square) image patches (avoid working on large images and
+% we suggest to work on square image patches (avoid working on large images and
 % large number of filters at the same time)
-[b] = CreateImages('../datasets/city_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES); % Replace directory with large image data directory.
-b = reshape(b, size(b,1), size(b,2), [] );
+% CONTRAST_NORMALIZE = 'local_cn'; 
+% ZERO_MEAN = 1;   
+% COLOR_IMAGES = 'gray'; 
+% [b] = CreateImages('../datasets/fruit_100_100',CONTRAST_NORMALIZE,ZERO_MEAN,COLOR_IMAGES);
+% b = reshape(b, size(b,1), size(b,2), [] );
+
+load city;
+% load fruit;
 
 %% Define the parameters
 kernel_size = [11, 11, 100];
 lambda = 1;
+hit_rate = 1;    % probability for choosing one specific code
 
 %% cache the vector to matrix info for efficient indexing
-% It may take some time (roughly 40s), while you only need to compute it once and store it
-d_ind = constructDicIndex(  kernel_size, size(b,1), size(b,2) );
-z_ind = constructCodeIndex( kernel_size, size(b,1) );
+% It may take some time (roughly 30s), while you only need to compute it once and store it
+% d_ind = constructDicIndex(  kernel_size, size(b,1), size(b,2) );
+% z_ind = constructCodeIndex( kernel_size, size(b,1) );
+load d_ind; load z_ind;
 
 %% online stochastic CSC
-[ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, lambda);
+[ d, z ]  = OnlineStochasticCSC(b, d_ind, z_ind, kernel_size, hit_rate, lambda);
 
 %% visualize dictionary
 plotDic( d, 10, max(d(:)), min(d(:)) );

### 2018-11-14 cvpr2019/SCSCmodel.tex
fix notation

@@
 \subsection{The Model}
+We first define $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$.
 Based on the strong sparsity of the codes $\code$, we propose to
 implement the CSC learning problem~\eqref{eq:CSCmodel} iteratively,
-where at $\ite$-th iteration we only consider a random subset
-$\mathcal{M}^{\ite}(\code)$ of the codes:
-\begin{equation} \label{eq:updatingFilter}
-\begin{split}
-    & (\filter^{\ite},\code^{\ite}) =  \\
-    &\minimize{\filter,\code}  \frac{1}{2}\|\signal - \sum_{k=1}^{K} \filter_k * \mathcal{M}_k^{\ite}(\code_k) \|_2^2 + \lambda \sum_{k=1}^{K}\| \mathcal{M}_k^{\ite}(\code_k) \|_1  \\
-    &\text{subject to} ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\}.
-\end{split}
+where at $\ite$-th iteration we only consider a random subset of the codes, denoted as $\subcode^t$.
+We subsample the sparse codes $\code$ following a Bernoulli distribution with
+probability $p$. Herein, $\subcode^t \in \mathbb{R}^{pDK}$, which satisfies:
+\begin{equation}
+    \subcode^t = \mask^{\ite} \code^\ite,
 \end{equation}
-Here $\mathcal{M}_k^{\ite}(\code_k)$ is a $\mathbb{R}^D \to \mathbb{R}^D$ operator subsampling the
-corresponding code $\code_k$ following a Bernoulli distribution with
-probability $p$, drawn at current iteration. Concretely, it retains the sampled codes and zero out the others.
-%The probability value $p$ controls the percentage of
-%the sparse codes that will be considered by the solver.
-In the case of $p=1$, the proposed model is identical with the
-classical CSC model. When $p<1$, the algorithm only solves a subset of
-the sparse codes at chosen positions in each iteration, and
-accordingly, the update of dictionary $\filter$ is based on the selected
-portion of the sparse codes. Similar to solving the classical CSC
-problem, we can apply a coordinate descent algorithm, alternating on
-subproblems of $\mathcal{M}^{\ite}(\code)$ and $\filter$, to solve the above
-bi-convex optimization problem. Specifically, the modified
-minimization problem for $\code$ can be formulated as:
+where $\mask^{\ite}$ is a $\mathbb{R}^{pDk \times DK}$ random binary matrix redrawn at current iteration, with $1$s on the entries corresponding to the sampled codes and $0$s elsewhere.
+Concretely, it projects the codes $\code^\ite$ to a random subspace, retaining the sampled ones and filtering out the others.
+In the case of $p=1$, the proposed model is identical with the classical CSC model, and $\mask$ is simply an identity matrix.
+When $p<1$, the algorithm only solves a subset of the codes at chosen positions in each iteration, and accordingly, the update of dictionary $\filter$ is based on the selected
+portion of the codes $\subcode$. Similar to solving the classical CSC problem, we can apply a coordinate descent algorithm, alternating on
+subproblems of $\subcode$ and $\filter$, to tackle the bi-convex optimization problem. Specifically, the modified
+minimization problem for $\subcode$ can be formulated as:
 \begin{equation} \label{eq:updatingCode}
-    \code^{\ite} = \minimize{\code} \frac{1}{2}\|\signal - \Filter^{\ite-1} \mask^{\ite} \code \|_2^2 + \lambda \|\mask^{\ite} \code\|_1,
+    \subcode^{\ite} = \minimize{\subcode} \frac{1}{2}\| \signal - \Filter^{\ite-1} (\mask^{\ite})^\top \subcode \|_2^2 + \lambda \| \subcode \|_1,
 \end{equation}
@@
   \times DK}$, which is constructed from the dictionary learned by
-$(\ite-1)$-th iteration, $\code = [\code_1, \dots, \code_K] \in
-\mathbb{R}^{DK}$. The convolution operators are expressed as a matrix
+$(\ite-1)$-th iteration. The convolution operators are expressed as a matrix
 multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k *
 \code_k$. Therefore, each part of $\Filter$ is a Toeplitz
-matrix. Matrix $\mask^{\ite}$ is a $\mathbb{R}^{Dk \times DK}$ random binary
-diagonal matrix with $1$s on the diagonal entries corresponding to the sampled codes and $0$ elsewhere, performing the function of
-$\mathcal{M}^{\ite}(\code)$, which satisfies $\mathrm{Tr}(\mask^{\ite}) = pDK$. When $p=1$, $\mask^{\ite}$ is just an identity matrix.
-Due to the introduced subsampling matrix, the
+matrix. Due to the introduced subsampling matrix, the
 convolution operator cannot be implemented in the Fourier
@@
 
-After computing the subsampled sparse codes $\mathcal{M}^{\ite}(\code)$, we can then project them
-onto the original spatial support by substituting $0$ for the
-masked-out values, obtaining $\code^{\ite}$. Afterwards, the dictionary can be updated by:
+After computing the subsampled codes $\subcode^\ite$, we can then project them
+onto the original spatial support by
+\begin{equation} \label{eq:upsampleCode}
+    \code^\ite = (\mask^{\ite})^\top \subcode^\ite.
+\end{equation}
+Afterwards, the dictionary can be updated by:
 \begin{equation} \label{eq:updatingFilter}
@@
 shown in Algorithm~\ref{algo:SBCSC}, where $N$ is the number of total
-input images, $(\code^i)^{\ite}$ is the sparse code associated with $i$-th
-image at $\ite$-th iteration, and $p$ is the uniform probability for one code been
+input images, $(\subcode^i)^{\ite}$ is the sampled codes associated with $i$-th
+image at $\ite$-th iteration and $(\code^i)^{\ite}$ is the corresponding codes in the original spatial support, $p$ is the uniform probability for one code been
 selected. We choose $p=\{1, 0.5, 0.2, 0.1, 0.05\}$ for testing in this
@@
     \For{i=1 to N}
-        \State $ \text{Compute } (\code^i)^{\ite} \text{ by solving problem~(\ref{eq:updatingCode}})$
+        \State $ \text{Compute } (\subcode^i)^{\ite} \text{ by solving problem~(\ref{eq:updatingCode}})$
+        \State $ \text{Compute } (\code^i)^{\ite}   \text{ by Eq.~\ref{eq:upsampleCode}}$
     \EndFor  
@@
     \State $ \text{Randomly sample }\code^t \text{ with rate } p $
-    \State $ \text{Compute } \code^t \text{ by solving problem~(\ref{eq:updatingCodeOnline}) using } \filter^{t-1}$
+    \State $ \text{Compute } \subcode^t \text{ by solving problem~(\ref{eq:updatingCodeOnline}) using } \filter^{t-1}$
+    \State Compute $\code^t$ by Eq.~\ref{eq:upsampleCode}
     \State Compute $\surC^t$ and $\surB^t$ by Eq.~\ref{eq:updateSur}
@@
 size. Then, given the sampled image $\signal^t$ at $t$-th iteration,
-we can compute the corresponding subsampled sparse codes $\code^t$ by
+we can compute the corresponding subsampled sparse codes $\subcode^t$ by
 \begin{equation} \label{eq:updatingCodeOnline}
-    \code^t = \minimize{\code} \frac{1}{2}\|\signal^t - \Filter^{t-1}\mask^t \code \|_2^2 + \lambda \|\mask^t \code\|_1.
+    \subcode^t = \minimize{\subcode} \frac{1}{2}\|\signal^t - \Filter^{t-1} (\mask^t)^\top \subcode \|_2^2 + \lambda \|\subcode\|_1.
 \end{equation}
-The only difference between Eq. ~\ref{eq:updatingCode} is that $\signal^t$ only contains a portion of the total images. After obtaining
-the sparse codes, the dictionary is updated by:
+The only difference between Eq.
+~\ref{eq:updatingCode} is that $\signal^t$ only contains a portion of the total images.
+After projecting $\subcode^t$ onto the original spatial support and obtaining the sparse codes $\code^t$, the dictionary is updated by:
 \begin{equation}

### 2018-11-15 cvpr2019/SCSCmodel.tex
slight reshuffle

@@
 \subsection{The Model}
-We first define $\code = [\code_1, \dots, \code_K] \in \mathbb{R}^{DK}$.
+We first define a stacked vector $\code = [\code_1, \dots, \code_K]
+\in \mathbb{R}^{DK}$ for the codes, as well as a stacked matrix
+$\Filter = [\Filter_1, \dots, \Filter_K] \in \mathbb{R}^{D \times DK}$
+for the filter convolutions. The convolution operators are expressed
+as a matrix multiplication so that $ \Filter \code = \sum_{k=1}^{K}
+\filter_k * \code_k$.  Therefore, each part of $\Filter$ is a Toeplitz
+matrix.
+
 Based on the strong sparsity of the codes $\code$, we propose to
 implement the CSC learning problem~\eqref{eq:CSCmodel} iteratively,
-where at $\ite$-th iteration we only consider a random subset of the codes, denoted as $\subcode^t$.
-We subsample the sparse codes $\code$ following a Bernoulli distribution with
-probability $p$. Herein, $\subcode^t \in \mathbb{R}^{pDK}$, which satisfies:
+where at the $\ite$-th iteration we only consider a random subset of
+the codes, denoted as $\subcode^t\in \mathbb{R}^{pDK}$.  We subsample
+the sparse codes $\code$ following a Bernoulli distribution with
+probability $p$. This subsampling process can be expressed as a matrix
+operation
 \begin{equation}
@@
 \end{equation}
-where $\mask^{\ite}$ is a $\mathbb{R}^{pDk \times DK}$ random binary matrix redrawn at current iteration, with $1$s on the entries corresponding to the sampled codes and $0$s elsewhere.
-Concretely, it projects the codes $\code^\ite$ to a random subspace, retaining the sampled ones and filtering out the others.
-In the case of $p=1$, the proposed model is identical with the classical CSC model, and $\mask$ is simply an identity matrix.
-When $p<1$, the algorithm only solves a subset of the codes at chosen positions in each iteration, and accordingly, the update of dictionary $\filter$ is based on the selected
-portion of the codes $\subcode$. Similar to solving the classical CSC problem, we can apply a coordinate descent algorithm, alternating on
-subproblems of $\subcode$ and $\filter$, to tackle the bi-convex optimization problem. Specifically, the modified
-minimization problem for $\subcode$ can be formulated as:
+where $\mask^{\ite}$ is a $\mathbb{R}^{pDk \times DK}$ binary matrix,
+where exactly one entry per row has a value of $1$, and the other
+entries are $0$. For each iteration $\ite$, a different matrix
+$\mask^{\ite}$ is generated randomly. This matrix projects the
+codes $\code^\ite$ to a random subspace, retaining the sampled codes
+and filtering out the others. In the case of $p=1$, the proposed model
+is identical to the classical CSC model, and $\mask$ is simply an
+identity matrix. When $p<1$, the algorithm only solves a subset of the
+codes at chosen positions in each iteration, and accordingly, the
+update of dictionary $\filter$ is based on the selected portion of the
+codes $\subcode$. Similar to solving the classical CSC problem, we can
+apply a coordinate descent algorithm, alternating on subproblems of
+$\subcode$ and $\filter$, to tackle the bi-convex optimization
+problem. Specifically, the modified minimization problem for
+$\subcode$ can be formulated as:
 \begin{equation} \label{eq:updatingCode}
@@
 \end{equation}
-where $\Filter^{\ite-1} = [\Filter_1^{\ite-1}, \dots, \Filter_K^{\ite-1}] \in \mathbb{R}^{D
-  \times DK}$, which is constructed from the dictionary learned by
-$(\ite-1)$-th iteration. The convolution operators are expressed as a matrix
-multiplication so that $ \Filter \code = \sum_{k=1}^{K} \filter_k *
-\code_k$. Therefore, each part of $\Filter$ is a Toeplitz
-matrix. Due to the introduced subsampling matrix, the
-convolution operator cannot be implemented in the Fourier
-domain. However, owing to the subsampling
-strategy, the number of variables that need to be computed for this
-subproblem is $pDK$ instead of $DK$, which leads to a reduction
-of the spatial-domain computation time by a factor of $\frac{1}{p}$.
+where $\Filter^{\ite-1}$ is composed of the dictionary learned in the
+$(\ite-1)$-th iteration.
+ Due to the introduced subsampling matrix, the convolution
+operator cannot be implemented in the Fourier domain. However, owing
+to the subsampling strategy, the number of variables that need to be
+computed for this subproblem is $pDK$ instead of $DK$, which leads to
+a reduction of the spatial-domain computation time by a factor of
+$\frac{1}{p}$.
 
@@
 \end{equation}
-Afterwards, the dictionary can be updated by:
+Afterwards, the dictionary can be updated by solving the optimization problem
 \begin{equation} \label{eq:updatingFilter}

### 2018-11-20 cvpr2019/supplement.tex
supplement edits

--- 2018-10-25 cvpr2019/supplement.tex
@@
-\begin{strip}
-\begin{center}
-{\Large \bf Stochastic Convolutional Sparse Coding \\ Supplementary Material }
-\end{center}
-\end{strip}
+\documentclass[10pt,twocolumn,letterpaper]{article}
+
+\usepackage{cvpr}
+\usepackage{times}
+\usepackage{epsfig}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+% Include other packages here, before hyperref.
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{wrapfig}
+\usepackage{subcaption}
+
+\usepackage{caption}
+\captionsetup[table]{position=bottom}
+
+\usepackage{array}
+\usepackage{epstopdf}
+\usepackage{cuted}
+
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+% \cvprfinalcopy % *** Uncomment this line for the final submission
+
+\def\cvprPaperID{3722} % *** Enter the CVPR Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ifcvprfinal\pagestyle{empty}\fi
+
+\input{macro}
+\begin{document}
+
+%%%%%%%%% TITLE
+\title{Stochastic Convolutional Sparse Coding \\ Supplementary Material}
+
+\author{First Author\\
+Institution1\\
+Institution1 address\\
+{\tt\small firstauthor@i1.org}
+% For a paper whose authors are all at the same institution,
+% omit the following lines up until the closing ``}''.
+% Additional authors and addresses can be added with ``\and'',
+% just like the second author.
+% To save space, use either the email address or home page, not both
+\and
+Second Author\\
+Institution2\\
+First line of institution2 address\\
+{\tt\small secondauthor@i2.org}
+}
+
+\maketitle
 
@@
 
-Algorithm~\ref{algo:BCDQCQP} is used to optimize a QCQP problem in the following form:
-\begin{equation}
-\begin{split}
-    \minimize{\filter} & \frac{1}{2}\|\signal - \Code \filter \|_2^2 \\
-    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
-\end{split}
-\end{equation}
-
 \begin{algorithm}
@@
 \end{algorithm}
+
+Algorithm~\ref{algo:BCDQCQP} is used to optimize a QCQP problem in the following form:
+\begin{equation}
+\begin{split}
+    \minimize{\filter} & \frac{1}{2}\|\signal - \Code \filter \|_2^2 \\
+    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
+\end{split}
+\end{equation}
+
 $L_k$ is the Lipschitz constant of $\Code_k^\top \Code_k$.
 
-\section{Zooming in on the Filters}
-
-Here we zoom in on the filters from Fig.\ \ref{fig:subsampleResult}. Notice that our filters look more smooth for those Gabor-like filters and also contains less number of noise-like filters.
-
-\begin{figure}[h]
+\begin{figure*}[h]
 \centering
@@
   \end{subfigure}
-\caption{Zoom-in view of the filters from Figure~\ref{fig:subsampleResult}.}
-\end{figure}
+\caption{Zoom-in view of the filters from Fig.~1 of the main manuscript.}
+\end{figure*}
+
+\section{Zooming in on the Filters}
+
+Here we zoom in on the filters from Fig.~1 in the main manuscript. Notice that our filters look more smooth for those Gabor-like filters and also contains less number of noise-like filters.
 
@@
 In order to show the robustness of the proposed algorithms, We also conduct experiments on city dataset.
-We first compare SBCSC with the state-of-the-art batch-mode algorithm~\cite{heide2015fast}, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}.
-Similar to the results shown in Fig.\ \ref{fig:subsampleResult}, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm with better outcomes and runtime performance.
+We first compare SBCSC with the state-of-the-art batch-mode algorithm, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}.
+Similar to the results shown in Fig.~1 in the main manuscript, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm with better outcomes and runtime performance.
 Since the learning is performed on handful datasets, both of them learn quite a few data-specific image features.
-The reconstruction quality also shows a shortage of the generalization ability.
-For example, the eighth image, which contains a large portion of texture information existed in the filters learned from city dataset, can be significantly better reconstructed by such filters compared to those learned from fruit dataset, while it may have poorer performance on other types of images.
-Furthermore, compared with the over-complete dictionary, we can observe that the presented over-complete dictionary contains both of the image features (superficially similar) appeared in the filters learned from fruit and city dataset, even though they use totally different training images.
-It also experimentally shows a better reconstruction performance on all kinds of testing images.
-
-\begin{figure}[h]
-\centering
-\begin{subfigure}{0.5\textwidth}
-  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
-\end{subfigure}
-\begin{subfigure}{0.5\textwidth}
-  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
-\end{subfigure}
-
-\caption{Experimental results obtained on city dataset.
-Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
-Bottom: Testing PSNR with respect to execution time.}
-\label{fig:onlineSmall-city}
-\end{figure}
+These data-specific image features have the shortage of the generalization ability, which can be revealed in the image inpainting application.
+For example, the eighth image, which contains a large portion of the texture information existed in the filters learned from city dataset, can be significantly better reconstructed by such filters compared to using those learned from fruit dataset.
+However, it may exhibit poorer performance on other types of images.
 
@@
             \hline
-            PSNR~\cite{heide2015fast} & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
+            PSNR~[10] & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
             \hline
@@
 \caption{Experimental results obtained on the city dataset.
-Top: Convergence comparison between the-state-of-art batch method~\cite{heide2015fast} and SBCSC with different subsampling probability.
+Top: Convergence comparison between the-state-of-art batch method and SBCSC with different subsampling probability.
 Middle: Learned filters by SBCSC with $p=0.1$ and the comparable method.
 Even though these dictionaries look similar, our method learns more smooth filters.
-Compared to the learned filters in Fig.\ \ref{fig:subsampleResult}, they have different representations of the dictionaries, where data-specific features are learned from handful training images.
-Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters.}
+Compared to the learned filters in Fig.~1 of the main manuscript, they have different representations of the dictionaries, where data-specific features are learned from handful training images.
+Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters in the image inpainting application.}
 \label{fig:subsampleResult-city}
@@
 
-We then compare SOCSC with the state-of-the-art online algorithm~\cite{liu-2018-first} on city dataset, the results of which are shown in Fig.\ \ref{fig:onlineSmall-city}.
-Similar to the results presented in Fig.\ \ref{fig:onlineSmall}, our method obtains comparable outcomes, meanwhile, achieves roughly $5 \times$ speedup.
+We then compare SOCSC with the state-of-the-art online algorithm on city dataset, the results of which are shown in Fig.\ \ref{fig:onlineSmall-city}.
+Similar to the results presented in Fig.~3 of the main manuscript, our method obtains comparable outcomes, meanwhile, achieves roughly $6 \times$ speedup.
 
 \section{Over-complete Dictionary and Large Datasets}
-In this section, we verify the importance of a large dataset when learning the over-complete dictionary.
-in Fig.~\ref{fig:overCompleteDic-dataset}, we show a visual and quantitative comparisons between the over-complete dictionaries respectively learned by batch-mode algorithm on small dataset (the fruit dataset) and online-mode algorithm on large dataset (1000 images).
-Most of the filters learned from small dataset have poor structures and reveal very limited representative ability.
-The numerical results also demonstrate that it even shows a degraded reconstruction performance compared to the under-complete dictionary.
-Owing to plentiful training samples, our over-complete dictionary not only shows visually decent structures and more representative image features, but also leads to a significant improvement on image reconstruction.
-Based on all experimental results, it implies that the number of filters and number of training samples are both essential in the CSC model, therefore, the proposed algorithm has prominent advantages over the existing approaches.
+\begin{figure*}[h]
+\centering
+\begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
+\end{subfigure}
+\begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
+\end{subfigure}
+
+\caption{Experimental results obtained on city dataset.
+Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach.
+Right: Testing PSNR with respect to execution time.}
+\label{fig:onlineSmall-city}
+\end{figure*}
+
+\begin{figure*}[h]
+\centering
+\begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=1\linewidth]{figure/nonZeroElement.pdf}
+\end{subfigure}
+\begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=1\linewidth]{figure/reconPSNR.pdf}
+\end{subfigure}
+
+\caption{Left: number of non-zero elements in the codes for different images ($10 ~ 256 \times 256$ images). Right: PSNR between the reconstructed images and the original ones.}
+\label{fig:overVSunder}
+\end{figure*}
 
@@
             \hline
-            PSNR~\cite{heide2015fast} & 29.60 & 28.11 & 29.47 & 28.98 & 28.79 & 29.21 & 28.03  & 29.31 & 27.42 & 30.52 \\
+            PSNR~[10] & 29.60 & 28.11 & 29.47 & 28.98 & 28.79 & 29.21 & 28.03  & 29.31 & 27.42 & 30.52 \\
             \hline
@@
   \caption{ Visual and numerical comparisons between the learned over-complete dictionaries by batch-mode algorithm and by online-mode algorithm.
-Top: Over-complete dictionary learned by batch CSC model~\cite{heide2015fast} on small dataset, and proposed online CSC model (SOCSC) on large dataset.
-Bottom: Respective reconstruction quality for these two over-complete dictionaries.}
+Top: Over-complete dictionary learned by batch CSC model on small dataset, and proposed online CSC model (SOCSC) on large dataset.
+Bottom: Respective reconstruction quality for these two over-complete dictionaries applied for image inpainting.}
   \label{fig:overCompleteDic-dataset}
 \end{figure*}
+
+In this section, we first show the improved sparse representation of the natural images with over-complete dictionaries ($K=400$) over under-complete ones ($K=100$).
+The numerical comparisons of number of non-zero elements and its corresponding reconstruction PSNR for various images are shown in Fig.~\ref{fig:overVSunder}.
+Here, we define the non-zero elements as the codes whose coefficient is no less than $0.1$.
+We could observe that at all times, using over-complete dictionary leads to a sparser representation of the images, roughly $8\%-10\%$ reduction on the non-zero elements.
+Meanwhile, it achieves dramatically improved reconstruction quality, over $1$ dB on average.
+
+We then verify the importance of a large dataset when learning the over-complete dictionary.
+in Fig.~\ref{fig:overCompleteDic-dataset}, we show a visual and quantitative comparisons between the over-complete dictionaries respectively learned by batch-mode algorithm on small dataset (the fruit dataset) and online-mode algorithm on large dataset (1000 images).
+Most of the filters learned from small dataset have poor structures and reveal very limited representative ability.
+The numerical results also demonstrate that it even shows a degraded reconstruction performance compared to the under-complete dictionary.
+Owing to plentiful training samples, our over-complete dictionary not only shows visually decent structures and more representative image features, but also leads to a significant improvement on image reconstruction.
+Based on all experimental results, it implies that the number of filters and number of training samples are both essential in the CSC model, therefore, the proposed algorithm has prominent advantages over the existing approaches.
+
+\end{document}
+
+% --- DO NOT DELETE ---
+% Local Variables:
+% mode: latex
+% mode: flyspell
+% mode: TeX-PDF
+% End:

### 2019-01-30 cvpr2019/rebuttal/egrebuttal.tex
add rebuttal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\input{macro}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3722} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Author Response for Stochastic Convolutional Sparse Coding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

\underline{Reviewer 1}

\textbf{Novelty:}
It should be emphasized that the proposed method is the first spatial-domain solver for CSC problems that outperforms all the other Fourier-domain solvers in terms of time both in batch mode and online mode. Solving CSC problem in spatial domain brings higher capabilities of handling arbitrary boundary conditions, additional regularization terms (also see response to reviewer 3: \textbf{comparisons}) those can not be handled in fourier domain and multi-layered structures, offering CSC model higher feasibility to wider applications.

\textbf{Algorithm:}
It is not reasonable to value an algorithm by its complexity, while it should be valued by its effectiveness and efficiency. Easing complicated problems is also a key motivation for conducting researches.

\underline{Reviewer 2}

\textbf{Specific questions:}

1. $\Filter_k \in \mathbb{R}^{D \times D}$ is a Toeplitz matrix for filter $\filter_k \in \mathbb{R}^{M}$, specifically,
%\begin{equation}\label{toeplitz}
% \Filter_k =
% \begin{bmatrix}
%    \filter_{k,1} \\
%    \filter_{k,2} & \filter_{k,1}\\
%    \vdots        & \filter_{k,2} & \filter_{k,1}\\
%    \filter_{k,M} & \vdots        & \filter_{k,2}\\
%                  & \filter_{k,M} & \vdots       \\
%                  &               & \filter_{k,M} & \ddots\\
%                  &               &               &        & \ddots
%  \end{bmatrix}
%\end{equation}
\begin{equation}\label{toeplitz}
 \Filter_k =
 \begin{bmatrix}
    \filter_{k,1} \\
    \filter_{k,2} & \filter_{k,1}\\
    \vdots        & \filter_{k,2}\\
    \filter_{k,M} & \vdots       \\
                  & \filter_{k,M} & \ddots\\
                  &               &        & \ddots          
  \end{bmatrix}
\end{equation}
$\Filter = [\Filter_1, \dots, \Filter_K]$, therefore $\Filter$ has the size of $D \times DK$.

2. Problem (5) is solved according to all the data. For notation simplicity, we omit the notation for data samples. In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of training samples. We will make this more clear in revised version.

3. For deriving updating rule (8), we can expand equation (7) as:
\begin{equation}
    \filter^t = \minimize{\filter} \frac{1}{2t} \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i})\filter - \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i})
\end{equation}
Let $\surC^t = \frac{1}{t}\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i}$ and $\surB^t = \frac{1}{t} \sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i}$, then we obtain equation (9), and the updating rule (8) is obvious.

\underline{Reviewer 3}

\textbf{Sparsity:}
We have demonstrated the sparsity in the figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters. It also shows that using over-complete dictionary leads to $8\% - 10\%$ reduction on the non-zero elements and achieves significantly improved representation ability.

\textbf{Connections:}
The connections between section 2 and the proposed method can be understood from 2 aspects. The first two points in section 2 contributes to the first motivation. CSC model is an overparameterized model, and the sparsity property of the codes can hardly be exploited if solving the problem in fourier domain. The third point accounts for the second motivation that the dimension size of updating dictionary step is $D$ when solving it in fourier domain, instead of $M$ in spatial domain ($M \ll D$).

\textbf{PSNR:}
PSNR is the peak signal-to-noise ratio, measuring the difference between the reconstructed signal and the original one. We will explain it in the revised version.

\textbf{Parameter:}
The parameter sensitivity in CSC model has been extensively studied in Wohlberg et al.. We are not indented to re-report the parameter sensitivity.

\textbf{Comparisons:}
The comparisons between (3)(Choudhury et al.) and (4)(Degraux et al.) are not applicable because (3) distributes the data to multiple machines to ease the memory issue, while it stills has the heavy computational burden. The proposed single-core program is fair to compare with single-core implementations. (4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal image formation model is not convolution based. We emphasize that our proposed strategy can be perfectly aligned with this types of problem and achieve roughly one magnitude speedup (also see response to reviewer 1).

To achieve the final convergence, (2)(Papyan et al.) requires about $1.5 \times$ runtime over the presented fourier-domain solver (Heide et al.), that is to say our proposed SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al. and ours SBCSC need only 12-14 iterations). We will add the convergence comparison with (2) in supplementary. The execution time of ours SOCSC is comparable to the reported results in (1)(Wang et al.), roughly $70-80$ seconds to process 10 images in fruit and city dataset, we will add the comparison in revised version. Notice that (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated. All the discussions will be added.

We emphasize that none of the precedent work represent the importance of the over-complete dictionaries learned in CSC model, and we have shown that they are essential in image reconstruction tasks.

%{\small
%\bibliographystyle{ieee}
%\bibliography{egbib}
%}

\end{document}

### 2019-02-07 cvpr2019/rebuttal/egrebuttal.tex
edits
WH edits

@@
 
-\textbf{Novelty:}
-It should be emphasized that the proposed method is the first spatial-domain solver for CSC problems that outperforms all the other Fourier-domain solvers in terms of time both in batch mode and online mode.
-Solving CSC problem in spatial domain brings higher capabilities of handling arbitrary boundary conditions, additional regularization terms (also see response to reviewer 3: \textbf{comparisons}) those can not be handled in fourier domain and multi-layered structures, offering CSC model higher feasibility to wider applications.
+\textbf{Novelty:} It should be emphasized that the proposed method is
+the first spatial-domain solver for CSC problems that outperforms all
+the other Fourier-domain solvers in terms of time both in batch mode
+and online mode. Solving CSC problem in spatial domain brings higher
+capabilities of handling arbitrary boundary conditions, additional
+regularization terms (also see response to reviewer 3:
+\textbf{comparisons}) those can not be handled in the Fourier domain
+and multi-layered structures, offering CSC model higher feasibility to
+wider applications.
 
-\textbf{Algorithm:}
-It is not reasonable to value an algorithm by its complexity, while it should be valued by its effectiveness and efficiency.
-Easing complicated problems is also a key motivation for conducting researches.
+\textbf{Simplicity:} We believe an algorithm should be judged based on
+by its effectiveness and efficiency, now on how complicated it is. In
+fact, simplicity is a virtue, and simplifying complicated problems is
+also a key motivation for conducting research.
 
@@
 Problem (5) is solved according to all the data.
-For notation simplicity, we omit the notation for data samples.
+For notational simplicity, we omit the notation for data samples.
 In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of training samples.
@@
 \textbf{Sparsity:}
-We have demonstrated the sparsity in the figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters.
+We have demonstrated the sparsity in the Figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters.
 It also shows that using over-complete dictionary leads to $8\% - 10\%$ reduction on the non-zero elements and achieves significantly improved representation ability.
@@
 \textbf{Connections:}
-The connections between section 2 and the proposed method can be understood from 2 aspects.
-The first two points in section 2 contributes to the first motivation.
-CSC model is an overparameterized model, and the sparsity property of the codes can hardly be exploited if solving the problem in fourier domain.
-The third point accounts for the second motivation that the dimension size of updating dictionary step is $D$ when solving it in fourier domain, instead of $M$ in spatial domain ($M \ll D$).
+The connections between section 2 and the proposed method can be
+understood from 2 aspects. The first two points in Section 2
+contribute to the first motivation. CSC model is an overparameterized
+model, and the sparsity property of the codes can hardly be exploited
+if solving the problem in the Fourier domain. The third point accounts
+for the second motivation that the dimension size of updating
+dictionary step is $D$ when solving it in the Fourier domain, instead of $M$ in spatial domain ($M \ll D$).
 
@@
 
-\textbf{Comparisons:}
-The comparisons between (3)(Choudhury et al.) and (4)(Degraux et al.) are not applicable because (3) distributes the data to multiple machines to ease the memory issue, while it stills has the heavy computational burden.
-The proposed single-core program is fair to compare with single-core implementations.
+\textbf{Comparisons:} The comparisons between (3)(Choudhury et al.)
+and (4)(Degraux et al.)  are not applicable. (3) is focused on memory
+efficiency by splitting a large problem into smaller chunks, which can
+be solved sequentially on one node or in parallel on multiple
+nodes. This splitting however introduces additional computational
+overhead compared to Heide et al, which we compare against.
 (4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal image formation model is not convolution based.
@@
 
-To achieve the final convergence, (2)(Papyan et al.) requires about $1.5 \times$ runtime over the presented fourier-domain solver (Heide et al.), that is to say our proposed SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al.
+To achieve the final convergence, (2)(Papyan et al.) requires about $1.5 \times$ runtime over the presented Fourier-domain solver (Heide et al.), that is to say our proposed SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al.
 and ours SBCSC need only 12-14 iterations).
-We will add the convergence comparison with (2) in supplementary.
 The execution time of ours SOCSC is comparable to the reported results in (1)(Wang et al.), roughly $70-80$ seconds to process 10 images in fruit and city dataset, we will add the comparison in revised version.
 Notice that (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated.
-All the discussions will be added.
+These additional comparisons affirm the superiority of the proposed method.
+All the comparisons and discussions will be added.
 

### 2019-02-07 cvpr2019/rebuttal/egrebuttal.tex
edits

@@
 
+\underline{General comments}
+
+\textbf{Convergence:} This work is application-oriented addressing limitations in existing methods, and explores new directions tackling the problem and achieves improved learning efficiency.
+The empirical convergence has been validated on multiple datasets, and the demonstrated efficiency offers broader potential research directions on CSC model those fit well with CVPR interests.
+We agree a theoretical analysis is desired for the proposed method, however, judging the work \textbf{only} by its theoretical guarantee is biased.
+
+%The work should not only be valued by its theoretical guarantee, but also its experimental performance and contributions to this field that fit well with CVPR venue.
+
 \underline{Reviewer 1}
 
-\textbf{Novelty:} It should be emphasized that the proposed method is
-the first spatial-domain solver for CSC problems that outperforms all
-the other Fourier-domain solvers in terms of time both in batch mode
-and online mode. Solving CSC problem in spatial domain brings higher
-capabilities of handling arbitrary boundary conditions, additional
-regularization terms (also see response to reviewer 3:
-\textbf{comparisons}) those can not be handled in the Fourier domain
-and multi-layered structures, offering CSC model higher feasibility to
-wider applications.
+\textbf{Novelty:}
+It should be emphasized that the proposed method is the first spatial-domain solver for CSC problem that outperforms existing Fourier-domain solvers in terms of time both in batch mode and online mode.
+Solving CSC problem in spatial domain brings higher capabilities of handling arbitrary boundary conditions, additional regularization terms those can not be handled in Fourier domain (also see response to reviewer 3: \textbf{comparisons}), offering CSC model higher feasibility to wider applications.
 
-\textbf{Simplicity:} We believe an algorithm should be judged based on
-by its effectiveness and efficiency, now on how complicated it is. In
-fact, simplicity is a virtue, and simplifying complicated problems is
-also a key motivation for conducting research.
+\textbf{Simplicity:} We believe an algorithm should be judged by its effectiveness and efficiency, not on how complicated it is.
+Simplicity is a virtue, and simplifying complicated problems is also a key motivation for conducting research.
+
+%\textbf{Algorithm:}
+%It is unfair to value an algorithm by its complexity, while it should be valued by its effectiveness and efficiency. Easing complicated problems is also a key motivation for conducting researches.
 
@@
 
-1. $\Filter_k \in \mathbb{R}^{D \times D}$ is a Toeplitz matrix for filter $\filter_k \in \mathbb{R}^{M}$, specifically,
+1. $\Filter_k \in \mathbb{R}^{D \times D}$ is a Toeplitz matrix for filter $\filter_k \in \mathbb{R}^{M}$,
 %\begin{equation}\label{toeplitz}
@@
     \filter_{k,M} & \vdots       \\
-                  & \filter_{k,M} & \ddots\\
-                  &               &        & \ddots
-  \end{bmatrix}
+                  & \filter_{k,M} & \ddots
+  \end{bmatrix} \nonumber
 \end{equation}
@@
 2.
-Problem (5) is solved according to all the data.
+Problem (5) is solved according to all data.
 For notational simplicity, we omit the notation for data samples.
-In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of training samples.
+In line 145, we declare the equations are applied to all training samples for batch mode, and in line 351 we emphasize that the equations in online mode only applies to a portion of the samples.
 We will make this more clear in revised version.
 
-3. For deriving updating rule (8), we can expand equation (7) as:
-\begin{equation}
-    \filter^t = \minimize{\filter} \frac{1}{2t} \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i})\filter - \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i})
-\end{equation}
-Let $\surC^t = \frac{1}{t}\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i}$ and $\surB^t = \frac{1}{t} \sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i}$, then we obtain equation (9), and the updating rule (8) is obvious.
+3. In order to deriving updating rule (8), we can expand equation (7) as:
+%\begin{equation}
+$\filter^t = \minimize{\filter} \frac{1}{2t} \filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i})\filter - \frac{1}{t}\filter^{\top} (\sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i})$ . %\nonumber
+%\end{equation}
+Let $\surC^t = \frac{1}{t}\sum_{i=1}^{t}{(\Code^i)^{\top}\Code^i}$ and $\surB^t = \frac{1}{t} \sum_{i=1}^{t}{(\Code^i)^{\top}\signal^i}$, then we obtain equation (9), and the rule (8) is obvious for a recursive computation.
 
@@
 \textbf{Sparsity:}
-We have demonstrated the sparsity in the Figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters.
+We have demonstrated the sparsity in Figure 4 of supplementary material, which states that on average the codes has $0.18\%$ non-zero elements for 100 filters.
 It also shows that using over-complete dictionary leads to $8\% - 10\%$ reduction on the non-zero elements and achieves significantly improved representation ability.
@@
 \textbf{Connections:}
-The connections between section 2 and the proposed method can be
-understood from 2 aspects. The first two points in Section 2
-contribute to the first motivation. CSC model is an overparameterized
-model, and the sparsity property of the codes can hardly be exploited
-if solving the problem in the Fourier domain. The third point accounts
-for the second motivation that the dimension size of updating
-dictionary step is $D$ when solving it in the Fourier domain, instead of $M$ in spatial domain ($M \ll D$).
+The connections between section 2 and the proposed method can be understood from 2 aspects.
+The first two points in section 2 contributes to the first motivation.
+CSC model is an overparameterized model, and the sparsity property of the codes can hardly be exploited if solving the problem in Fourier domain.
+The third point accounts for the second motivation that the dimension size of updating dictionary step is $D$ when solving it in Fourier domain, instead of $M$ in spatial domain ($M \ll D$).
 
@@
 \textbf{Parameter:}
-The parameter sensitivity in CSC model has been extensively studied in Wohlberg et al.. We are not indented to re-report the parameter sensitivity.
+The parameter sensitivity in CSC model has been extensively studied in Wohlberg et al. 2016. If the reviewer asks for, we will add it in supplement.
 
-\textbf{Comparisons:} The comparisons between (3)(Choudhury et al.)
-and (4)(Degraux et al.)  are not applicable. (3) is focused on memory
-efficiency by splitting a large problem into smaller chunks, which can
-be solved sequentially on one node or in parallel on multiple
-nodes. This splitting however introduces additional computational
-overhead compared to Heide et al, which we compare against.
-(4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal image formation model is not convolution based.
+\textbf{Comparisons:}
+The comparisons with (3)(Choudhury et al. ICCV 2017) and (4)(Degraux et al. ICIP 2017) are not applicable. (3) focuses on memory
+efficiency by splitting a large problem into smaller chunks, which can be solved sequentially on one node or in parallel on multiple
+nodes.
+This splitting however introduces additional computational overhead compared to Heide et al, which we compare against.
+(4) formulates the multimodal image reconstruction into the CSC model, and uses the basic coordinate descent algorithm to solve the problem in spatial domain (which are known to have poor runtime performance) because the multimodal imaging model is not convolution based.
 We emphasize that our proposed strategy can be perfectly aligned with this types of problem and achieve roughly one magnitude speedup (also see response to reviewer 1).
 
-To achieve the final convergence, (2)(Papyan et al.) requires about $1.5 \times$ runtime over the presented Fourier-domain solver (Heide et al.), that is to say our proposed SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al.
-and ours SBCSC need only 12-14 iterations).
-The execution time of ours SOCSC is comparable to the reported results in (1)(Wang et al.), roughly $70-80$ seconds to process 10 images in fruit and city dataset, we will add the comparison in revised version.
-Notice that (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated.
-These additional comparisons affirm the superiority of the proposed method.
+% because (3) distributes the data to multiple machines to ease the memory issue, while it stills has the heavy computational burden.
+The proposed single-core program is fair to compare with single-core implementations.
+
+To achieve the final convergence, (2)(Papyan et al.
+ICCV 2017) requires $1.5 \times$ runtime over the compared Fourier-domain solver (Heide et al.), namely ours SBCSC can run $3 \times$ faster than (2) ((2) needs over 300 iterations to converge while Heide et al.
+and ours need only 12-14 iterations).
+The runtime of ours SOCSC is \textbf{comparable} to the reported results in (1)(Wang et al.
+ICML 2018), roughly $70$ seconds to process the fruit and city dataset.
+\textbf{Notice that} (1) runs on GPUs and introduces base filters to represent the original filters, making the problem more complicated.
+These additional comparisons \textbf{affirm the superiority} of the proposed method.
 All the comparisons and discussions will be added.
 
-We emphasize that none of the precedent work represent the importance of the over-complete dictionaries learned in CSC model, and we have shown that they are essential in image reconstruction tasks.
+We emphasize that none of the precedent work represent the importance of the over-complete dictionary learned in CSC model, and we have shown that they play an important role in image reconstruction tasks.
 

### 2019-08-19 VMV19/CSCmodel.tex
add directory

--- 2018-11-08 cvpr2019/CSCmodel.tex
@@
-\section{Convolutional Sparse Coding (CSC)}
+\section{Convolutional Sparse Coding (CSC)} \label{CSCmodel}
 The dictionary learning problem for CSC problem has the form
@@
 where $\signal \in \mathbb{R}^D$ is a $D$-dimensional signal or a
-vectorized image\footnote{In this manuscript, we work on 2D images.},
+vectorized image,
 $\filter_k \in \mathbb{R}^M$ is the $k$-th dictionary, $\code_k\in

### 2019-08-19 VMV19/Conclusion.tex
add directory

--- 2018-11-08 cvpr2019/Conclusion.tex
@@
 In this work, we present a novel stochastic subsampling strategy for
-solving the CSC problem in the spatial domain. This method
-significantly improves the runtime performance over the prior
+solving the CSC problem in the spatial domain. This method exploits 
+the sparsity of the \changed{over-parameterized} model and improves the runtime performance over the prior
 frequency-domain solvers, which applies to both batch mode and
@@
 safe screening~\cite{ghaoui2012Swfe}. It is worth emphasizing that
-Fourier-domain methods cannot benefit from these kinds of speedup
+Frequency-domain methods cannot benefit from these kinds of speedup
 strategies.
 
-In the future, alternative subsampling strategies can be studied to
-improve learning efficiency. Instead of employing uniform subsampling
-strategy, for instance one could employ an importance or correlation
-based sampling strategy that considers the inter-dependency between the
-signals and the sparse codes.
+%In the future, alternative subsampling strategies can be studied to
+%improve learning efficiency. Instead of employing uniform subsampling
+%strategy, for instance one could employ an importance or correlation
+%based sampling strategy that considers the inter-dependency between the
+%signals and the sparse codes.
 
@@
 foreseen that this capability has widespread applications in audio
-and image related tasks, and higher dimensional signal processing. The
-source code for SBCSC and SOCSC is attached in the supplement for
-reference.
-\note{Do you really mean source code (as in full matlab code), or just
-  the pseudo-code?}
+and image related tasks, and higher dimensional signal processing.
 

### 2019-08-19 VMV19/Introduction.tex
add directory

--- 2018-11-10 cvpr2019/Introduction.tex
@@
 
-Of course this convolutional approach is also the heart of many deep
+\changed{This convolutional approach is also at the heart of many deep
 learning-based methods in the form of
@@
   discriminative}, task-specific models, CSC is {\em unsupervised} and
-produces {\em generative} models that easily transfer between tasks.
+produces {\em generative} models that can easily be transferred between tasks.}
 
@@
 
-{\bfseries Contributions.} We mainly make three contributions in this
+{\bfseries Contributions.} \changed{We mainly make three contributions in this
 work. First, we introduce a randomization strategy for the CSC
-model and solve the entire problems in spatial domain. We demonstrate
+model and solve the entire problems in the spatial domain. We demonstrate
 that the proposed stochastic spatial-domain solver, with a reasonably
 selected subsampling rate, outperforms the state-of-the-art
-frequency-domain solvers with regard to computing efficiency. We then
+frequency-domain solvers with regard to computing efficiency. Secondly, we
 formulate an online-learning version of the proposed algorithm, and
@@
 while producing comparable outcomes. Finally, we demonstrate the
-capability to learn the over-complete dictionary from thousands of
+capability to learn the meaningful over-complete dictionary from thousands of
 images, and analyze the effectiveness of the learned over-complete
-dictionary for a number of reconstruction tasks.
+dictionary for a number of reconstruction tasks.}
 

### 2019-08-19 VMV19/Results.tex
add directory

--- 2018-11-13 cvpr2019/Results.tex
@@
-\section{Results} \label{sec:result}
+\section{Experiments and Results} \label{sec:result}
+
+\changed{ \subsection{Experimental Design}
 We first validate the proposed algorithms on the fruit and city
-datasets~\cite{zeiler2010deconvolutional}, which each consist of 10
+datasets~\cite{zeiler2010deconvolutional}, where each consists of 10
 training images of size $100 \times 100$. The online-mode algorithms
 are then adapted to one thousand $100 \times 100$ image patches
-randomly picked up from ImageNet~\cite{deng2009imagenet}. Note that
-batch-based CSC commonly can only handle less than 100 images
-simultaneously. The dictionary size is set to $100$ filters of size
-$11 \times 11$ pixels in all experiments except for over-complete
-dictionary. All training and evaluation processes in this manuscript
-are performed on contrast normalized
-images~\cite{zeiler2010deconvolutional,heide2015fast}.
+randomly picked up from ImageNet~\cite{deng2009imagenet}. Note that batch-based CSC commonly can only handle less than 100 images
+simultaneously due to the memory limitation.
+The dictionary size is set to $100$ filters of size $11 \times 11$ pixels in all experiments except for over-complete dictionary.
+All training and evaluation processes in this manuscript are performed on contrast normalized
+images~\cite{zeiler2010deconvolutional,heide2015fast}.}
 
@@
 \centering
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/iteVSobj.pdf}
@@
 
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/timeVSobj.pdf}
@@
 
-\begin{subfigure}{0.23\textwidth}
-  \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
-\end{subfigure}
-\begin{subfigure}{0.23\textwidth}
-  \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
-\end{subfigure}
-\caption{Top: Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling rate, all of which on performed on fruit dataset.
-Convergence is evaluated by monitoring the objective value of Eq.~\ref{eq:CSCmodel} on training images versus iterations and time, respectively.
-Bottom: Learned filters by the proposed method with $p=0.1$ and the comparable method.
-In these represented learned filters, our method learns more smooth Gabor-like filters and less number of noise-like filters with the same $\lambda$.
-Beyond this, it runs faster with regard to each iteration and shows better convergence behavior.}
+%\begin{subfigure}{0.23\textwidth}
+%  \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
+%\end{subfigure}
+%\begin{subfigure}{0.23\textwidth}
+%  \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
+%\end{subfigure}
+\caption{Convergence comparison between the-state-of-art method~\cite{heide2015fast} and the proposed method with different subsampling rate, all of which are performed on fruit dataset.
+Convergence is evaluated by monitoring the objective value of Eq.~\ref{eq:CSCmodel} on training images versus iterations and time, respectively.}
 \label{fig:subsampleResult}
 \end{figure}
-
-\begin{figure*}[h]
-    \centering
-    \includegraphics[width=1\textwidth]{figure/reconImage.pdf}
-    \resizebox{0.9\linewidth}{!}{
-        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
-            \cline{1-11}
-            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
-            \hline
-            PSNR~\cite{heide2015fast} & 29.54 & 28.16 & 29.40 & 29.22 & 28.89 & 29.29 & 28.10  & 29.57 & 27.46 & 30.72 \\
-            \hline
-            PSNR ours & \textbf{29.65} & \textbf{28.18} & \textbf{29.52} & \textbf{29.43} & \textbf{28.99} & \textbf{29.38} & \textbf{28.19} & \textbf{29.63} & \textbf{27.62} & \textbf{30.98} \\
-            \hline
-        \end{tabular} }
-    \caption{Numerical comparisons of the reconstruction quality obtained from the presented filters and its comparison.
-The reconstructions are performed on $50\%$ randomly observed images, with $\lambda = 0.4$ and $50$ ADMM iterations for both cases.
-Obtained PSNR values are averaged on 5 trials.
-Note that none of the testing images are in the training sets.} \label{fig:PSNRrecon}
-\end{figure*}
 
@@
 algorithm~\cite{heide2015fast} are shown in
-Fig.~\ref{fig:subsampleResult}. A different selection of the
+Fig.~\ref{fig:subsampleResult} \changed{(the compared method uses a similar number of iterations as ours to reach convergence)}. A different selection of the
 subsampling rate reveals that the proposed strategy will slightly
@@
 about $6 \times$ speedup over the not subsampled spatial domain solver
-and a $2 \times$ speedup over state-of-the-art Fourier-domain solver
+and a $2 \times$ speedup over state-of-the-art Frequency-domain solver
 for one iteration. We observe that a subsampling rate between $p=0.1$
@@
 
-We have observed that the comparison method has a relatively
-high objective value during the first $6-8$ iterations.
+%We have observed that the comparison method has a relatively
+%high objective value during the first $6-8$ iterations.
 The reason is that it introduces an additional mask term handling the boundary issues, therefore different splitting strategies are utilized and the subproblems are
-interleaved on their primary variables (in some sense, the primary variables can be regarded as intermediate results in the ADMM iteration).
+%interleaved on their primary variables (in some sense, the primary variables can be regarded as intermediate results in the ADMM iteration).
 See~\cite{wohlberg2016efficient} for details.
@@
 spatial-domain solver with a subsampling rate of $0.1$ reduces the
-computation time by a factor of two for the tested example. The
+computation time by a factor of two for the tested example. Specifically,
+SBCSC takes 170 seconds and the comparable method takes 350 seconds for
+14 iterations on a Core i7 PC. The
 robustness of the proposed algorithm is evaluated by additional
@@
 
-{\bfseries Reconstruction}. The SBCSC-learned filters with a
-subsampling rate of $p=0.1$ are shown in the bottom of
-Fig.~\ref{fig:subsampleResult}. For a visual comparison, we also show
-the filters learned from the competing method (bottom left of Figure 3
-in~\cite{heide2015fast}). As can be observed, both of them learn some
-seemingly similar Gabor-like filters. However, zooming into the
-details (please see supplemental materials for high resolution
-versions) reveals that our filters appear less noisy than the ones
-from~\cite{heide2015fast}. We then demonstrate the effectiveness of
-the reconstructed filters in the application of image inpainting,
-which refers to reconstructing a full image from partial
-measurements. A numerical comparison of the reconstruction quality is
-shown in Fig.~\ref{fig:PSNRrecon}. The filters learned by the proposed
-method not only appear less noisy by themselves, but also achieve
-better reconstruction quality on partially observed images with
-respect to the PSNR value. Furthermore, the learning process
-only takes about $50\%$ of the time for our method. Specifically, SBCSC takes 170 seconds and the comparable method takes 350 seconds for 14 iterations on a Core i7 PC.
+%{\bfseries Reconstruction}. The SBCSC-learned filters with a
+%subsampling rate of $p=0.1$ are shown in the bottom of
+%Fig.~\ref{fig:subsampleResult}. For a visual comparison, we also show
+%the filters learned from the competing method (bottom left of Figure 3
+%in~\cite{heide2015fast}). As can be observed, both of them learn some
+%seemingly similar Gabor-like filters. However, zooming into the
+%details (please see supplemental materials for high resolution
+%versions) reveals that our filters appear less noisy than the ones
+%from~\cite{heide2015fast}. We then demonstrate the effectiveness of
+%the reconstructed filters in the application of image inpainting,
+%which refers to reconstructing a full image from partial
+%measurements. A numerical comparison of the reconstruction quality is
+%shown in Fig.~\ref{fig:PSNRrecon}. The filters learned by the proposed
+%method not only appear less noisy by themselves, but also achieve
+%better reconstruction quality on partially observed images with
+%respect to the PSNR value. Furthermore, the learning process
+%only takes about $50\%$ of the time for our method. Specifically, SBCSC takes 170 seconds and the comparable method takes 350 seconds for 14 iterations on a Core i7 PC.
 
 \subsection{Online Learning}
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite-fruit.pdf}
+\end{subfigure}
+\begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time-fruit.pdf}
+\end{subfigure}
+
+\caption{The experiments are performed on fruit dataset, and each iteration randomly choose one samples from the training datasets.
+Top: Convergence of the test set objectives (objective value of Eq.~\ref{eq:CSCmodel} on testing datasets) for our method (SOCSC) and the current online approach~\cite{liu-2018-first}.
+Bottom: Testing PSNR with respect to execution time.
+While the quality of the output is comparable, our method achieves $6 \times$ speedup.}
+\label{fig:onlineSmall}
+\end{figure}
 
@@
 against the iteration number for the proposed method (SOCSC) and a
-recent online frequency-domain CSC method~\cite{liu-2018-first}. In
+recent online frequency-domain CSC method~\cite{liu-2018-first} (both
+ approaches use Matlab built-in functions only). In
 the same figure, we also keep track of the capability of the updated
 filters during the learning process to sparsely represent the test
-images, which is demonstrated by the time evolution of PSNR. These two
+images, which is demonstrated by the time evolution of PSNR (PSNR is the 
+peak signal-to-noise ratio, measuring the difference between the 
+reconstructed signal and the original one). These two
 approaches stop at optimum positions with similar objective values.
@@
 
-{\bfseries Over-complete dictionary.} To our knowledge, none of the
-existing CSC work reported or analyzed the over-complete dictionary
-(number of the dictionary is more than its degrees of freedom). One of
-the reasons could be that most of the prior work is batch-based, thus
-learning over-complete dictionary from small datasets would cause
-overfitting issues, which may contain quite a few data-specific
-filters, and therefore limit the ability to generalize the filters to
-other data (we verify this explanation in the supplement). The
-proposed online-based learning strategy (SOCSC) can overcome this
-issue by scaling the model up to arbitrary sample sizes.
-
 \begin{figure}[h]
 \centering
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite-fruit.pdf}
+\begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=1\linewidth]{figure/nonZeroElement.pdf}
 \end{subfigure}
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time-fruit.pdf}
+\begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=1\linewidth]{figure/reconPSNR.pdf}
 \end{subfigure}
 
-\caption{The experiments are performed on fruit dataset, and each iteration randomly choose one samples from the training datasets.
-Top: Convergence of the test set objectives (objective value of Eq.~\ref{eq:CSCmodel} on testing datasets) for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}.
-Bottom: Testing PSNR with respect to execution time.
-While the quality of the output is comparable, our method achieves $6 \times$ speedup.}
-\label{fig:onlineSmall}
+\caption{Top: number of non-zero elements in the codes for different images (on average $0.2\%$ of the variables are non-zero when $K=100$).
+Bottom: PSNR between the reconstructed images and the original ones with under-complete and over-complete dictionaries, respectively.}
+\label{fig:overVSunder}
 \end{figure}
@@
 \centering
+\includegraphics[width=0.9\textwidth]{figure/reconImage.pdf}
+\vspace*{2mm}
+\end{minipage}
+\begin{minipage}{1\textwidth}
+    \centering
     \resizebox{0.8\linewidth}{!}{
@@
 \end{minipage}
-\caption{Filters learned from 1000 images by our method (SOCSC) and the state-of-the-art online method~\cite{liu-2018-first}, and their corresponding reconstruction quality using the same hyperparameter settings as in Fig.~\ref{fig:PSNRrecon}.
+\caption{Top: Filters learned from large-scale datasets by our method (SOCSC) and the comparable online method~\cite{liu-2018-first}.
+Bottom: $10 ~ 256 \times 256$ testing images and their corresponding reconstruction quality in the image inpainting application.
 (a) The under-complete dictionary ($11 \times 11 \times 100$) learned by~\cite{liu-2018-first}; (b) The under-complete dictionary ($11 \times 11 \times 100$) learned by SOCSC.
@@
 \end{figure*}
+
+{\bfseries Over-complete dictionary.}
+%To our knowledge, none of the
+%existing CSC work reported or analyzed the over-complete dictionary
+%(number of the dictionary is more than its degrees of freedom). One of
+%the reasons could be that most of the prior work is batch-based, thus
+%learning over-complete dictionary from small datasets would cause
+%overfitting issues, which may contain quite a few data-specific
+%filters, and therefore limit the ability to generalize the filters to
+%other data (we verify this explanation in the supplement). The
+%proposed online-based learning strategy (SOCSC) can overcome this
+%issue by scaling the model up to arbitrary sample sizes.
+Learning over-complete dictionary (number of the dictionary is more
+than its degrees of freedom) from small datasets would cause
+overfitting issues, which may contain quite a few data-specific
+filters, and therefore limit the ability to generalize the filters to
+other data (we verify this explanation in the supplement). The
+proposed online-based learning strategy (SOCSC) can overcome this
+issue by scaling the model up to arbitrary sample sizes.
 
@@
 not typical for under-complete dictionaries. This additional
-feature information would play an essential role to better reconstruct
-the natural images, which can be demonstrated by the results of
-reconstruction quality shown at the bottom of the same figure.
+feature information would play an essential role to reveal an improved sparse representation of
+the natural images.
+The numerical comparisons of number of non-zero elements and its corresponding reconstruction PSNR for testing images ($10 ~ 256 \times 256$ images presented in Fig.~\ref{fig:overCompleteDic}) are shown in Fig.~\ref{fig:overVSunder}.
+Here, we define the non-zero elements as the codes whose coefficient is no less than $0.1$.
+We could observe that at all times, using over-complete dictionary leads to a sparser representation of the images, roughly $8\%-10\%$ reduction on the non-zero elements.
+Meanwhile, it achieves dramatically improved reconstruction quality, over $1$ dB on average.
 
-We further show a bottleneck revealed by the under-complete dictionary
-in the online-based CSC model. The top of
-Fig.~\ref{fig:overComDicAndMinibatch} demonstrates that no more
+We further demonstrate the effectiveness of the over-complete
+dictionary in the application of image inpainting,
+which refers to reconstructing a full image from partial
+measurements. A numerical comparison of the reconstruction quality is
+shown in the bottom of Fig.~\ref{fig:overCompleteDic}. The reconstructions
+are performed on $50\%$ randomly observed images, with $\lambda = 0.4$ and
+$50$ ADMM iterations for all cases. Obtained PSNR values are averaged on
+5 trials. The over-complete filters learned by the proposed
+method achieves significantly improved reconstruction quality on partially 
+observed images in terms of the PSNR value.
+
+We also observe a bottleneck revealed by the under-complete dictionary
+in the online-based CSC model. The top of Fig.~\ref{fig:overComDicAndMinibatch} demonstrates that no more
 apparent progress could be observed when the number of training images
@@
 over-complete dictionary overcomes this bottleneck, and it shows a
-considerable improvement in the PSNR of image representations.  This
-is also verified by applying these learned dictionaries to the image
-inpainting application as discussed above.
+considerable improvement in the PSNR of image representations. All 
+presented experimental results imply that the number of filters and 
+number of training samples are both essential in the CSC model.
 
@@
 \centering
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/overComplete-ite.pdf}
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/minibatch.pdf}
@@
 though it takes additional running time and memory. Overall,
-mini-batched updates provides a more runtime efficient learning
+mini-batched update provides a more runtime efficient learning
 process in the online-based CSC model, and according to the obtained
-experimental results, $\eta=20$ achieves a one order of magnitude
+experimental results, $\eta=20$ achieves one order of magnitude
 speedup over $\eta=1$ to reach a a comparable level of

### 2019-08-19 VMV19/SCSCmodel.tex
add directory

--- 2018-11-15 cvpr2019/SCSCmodel.tex
@@
 \section{Stochastic Convolutional Sparse Coding}
-\subsection{The Model}
+\subsection{The SCSC Model}
 We first define a stacked vector $\code = [\code_1, \dots, \code_K]
@@
 settings, $M \ll D$, hence there is no need to perform subsampling on
-the dictionary.
+the dictionary. Notice that the time complexity of solving the $\filter$-update 
+step in spatial domain is dependent of $M$, in contrast with that of frequency-domain 
+solvers, which is $D$ dependent. This addresses the third issue in Section~\ref{CSCmodel}.
 
-The work of~\cite{mensch2016dictionary} also applies a so-called
-stochastic subsampling strategy for dictionary learning, where the
-subsampling is randomly performed on the observed signals, differing
-from that of our proposed. In addition, it is basically applied for
-factorizing matrix that is large in both dimensions. Although CSC can
-be expressed in a similar mathematical formula as matrix factorization, the two
-problems are in practice quite different due to the convolutional
-property of the CSC model. Our proposed randomization
-approach shares a similar idea as utilized in the stochastic Frank-Wolfe
-algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}, in which
-the optimization is performed on a subset of the variables which are
-randomly extracted based on a certain probability distribution at each
-iteration. For the proposed algorithm, each iteration extracts
+%The work of~\cite{mensch2016dictionary} also applies a so-called
+%stochastic subsampling strategy for dictionary learning, where the
+%subsampling is randomly performed on the observed signals, differing
+%from that of our proposed. In addition, it is basically applied for
+%factorizing matrix that is large in both dimensions. Although CSC can
+%be expressed in a similar mathematical formula as matrix factorization, the two
+%problems are in practice quite different due to the convolutional
+%property of the CSC model.
+\changed{Our proposed randomization approach shares a similar idea as utilized in the stochastic Frank-Wolfe
+algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}.  The general idea of that is to solve the optimization problem on a subset of the variables at each iteration, which are
+randomly extracted based on a certain probability distribution.} For the proposed algorithm, each iteration extracts
 ($pDK+MK$) variables, where $pDK$ variables are randomly picked from a
 total $DK$ variables, and the rest remain unchanged. Owing to the fact
-that the codes are highly sparse, the original signals can still be
-represented by a portion of the codes under a reasonable subsampling
+that CSC model is \changed{over-parameterized} and the codes are highly 
+sparse, the original signals can still be represented by a portion of 
+the codes under a reasonable subsampling
 rate. Therefore, the convergence of the proposed algorithm will not be
@@
 is enough with $\filter$ computed in previous iteration as a warm
-start. We set the hyperparameters $\lambda=1$, the ADMM iteration
+start. We set the \changed{hyper-parameters} $\lambda=1$, the ADMM iteration
 fixed to 10, the augmented Lagrangian penalty $\rho$ to $10 \lambda$,
@@
 
-\subsection{Complexity Analysis}
+\subsection{Complexity Analysis}\label{complexity}
 Recall that $D$ is the number of pixels for a single image, $K$ is the

### 2019-08-19 VMV19/main.tex
add directory

% ---------------------------------------------------------------------------
% Author guideline and sample document for EG publication using LaTeX2e input
% D.Fellner, v1.15, Dec 14, 2018

\documentclass{egpubl}
\usepackage{EGVMV19}

% --- for  Annual CONFERENCE
% \ConferenceSubmission   % uncomment for Conference submission
% \ConferencePaper        % uncomment for (final) Conference Paper
% \STAR                   % uncomment for STAR contribution
% \Tutorial               % uncomment for Tutorial contribution
% \ShortPresentation      % uncomment for (final) Short Conference Presentation
% \Areas                  % uncomment for Areas contribution
% \MedicalPrize           % uncomment for Medical Prize contribution
% \Education              % uncomment for Education contribution
% \Poster                 % uncomment for Poster contribution
% \DC                     % uncomment for Doctoral Consortium
%
% --- for  CGF Journal
% \JournalSubmission    % uncomment for submission to Computer Graphics Forum
% \JournalPaper         % uncomment for final version of Journal Paper
%
% --- for  CGF Journal: special issue
% \SpecialIssueSubmission    % uncomment for submission to , special issue
% \SpecialIssuePaper         % uncomment for final version of Computer Graphics Forum, special issue
%                          % EuroVis, SGP, Rendering, PG
% --- for  EG Workshop Proceedings
\WsSubmission      % uncomment for submission to EG Workshop
%\WsPaper           % uncomment for final version of EG Workshop contribution
% \WsSubmissionJoint % for joint events, for example ICAT-EGVE
% \WsPaperJoint      % for joint events, for example ICAT-EGVE
% \Expressive        % for SBIM, CAe, NPAR
% \DigitalHeritagePaper
% \PaperL2P          % for events EG only asks for License to Publish

% --- for EuroVis
% for full papers use \SpecialIssuePaper
% \STAREurovis   % for EuroVis additional material
% \EuroVisPoster % for EuroVis additional material
% \EuroVisShort  % for EuroVis additional material

% !! *please* don't change anything above
% !! unless you REALLY know what you are doing
% ------------------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage{dfadobe}

\usepackage{cite}  % comment out for biblatex with backend=biber
% ---------------------------
%\biberVersion
\BibtexOrBiblatex
%\usepackage[backend=biber,bibstyle=EG,citestyle=alphabetic,backref=true]{biblatex}
%\addbibresource{egbibsample.bib}
% ---------------------------
\electronicVersion
\PrintedOrElectronic
% for including postscript figures
% mind: package option 'draft' will replace PS figure by a filename within a frame
\ifpdf \usepackage[pdftex]{graphicx} \pdfcompresslevel=9
\else \usepackage[dvips]{graphicx} \fi

\usepackage{egweblnk}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{wrapfig}
\usepackage{subcaption}

\usepackage{caption}
\captionsetup[table]{position=bottom}

\usepackage{array}
\usepackage{epstopdf}
\usepackage{cuted}
\input{macro}
% ---------------------------------------------------------------------
% end of prologue

% EG author guidelines plus sample file for EG publication using LaTeX2e input
% D.Fellner, v2.03, Dec 14, 2018

\title{Stochastic Convolutional Sparse Coding}

% for anonymous conference submission please enter your SUBMISSION ID
% instead of the author's name (and leave the affiliation blank) !!
% for final version: please provide your *own* ORCID in the brackets following \orcid; see https://orcid.org/ for more details.
\author{Submission ID: 1010}
%\author[J. Xiong \& P. Richtarik \& W. Heidrich]
%{\parbox{\textwidth}{\centering J. Xiong\orcid{0000-0002-1507-6070},
%		P. Richtarik\orcid{}
%		and W. Heidrich\orcid{}
 %       S. Spencer$^2$\thanks{Chairman Siggraph Publications Board}
%       }
%        \\
%% For Computer Graphics Forum: Please use the abbreviation of your first name.
%{\parbox{\textwidth}{\centering King Abdullah University of Science and Technology (KAUST), Saudi Arabia
%%        $^2$ Another Department to illustrate the use in papers from authors
%%             with different affiliations
%       }
%}
%}
% ------------------------------------------------------------------------

% if the Editors-in-Chief have given you the data, you may uncomment
% the following five lines and insert it here
%
% \volume{36}   % the volume in which the issue will be published;
% \issue{1}     % the issue number of the publication
% \pStartPage{1}      % set starting page

%-------------------------------------------------------------------------
\begin{document}
\begin{titlepage} 
\part*{Cover Letter: Author Response for Stochastic Convolutional Sparse Coding}

We would like to thank the reviewers for the detailed feedback, and are excited to see that our work is overall seen positively.

\begin{itemize}
\item Unclear and unspecific definitions and names: we have adjusted these as the reviewers suggest.

\item The selection of alternative candidates: For the batch-based algorithm comparison, Heide et al. is chosen because the required number of iterations to achieve convergence is comparable to ours (10-12 iterations), while the other approaches require hundreds of iterations. Even though their per iteration cost is less, the total runtime is longer than the chosen method. (we have the comparison regarding convergence with respect to both of the time and iterations)

For the online-based comparison, both of the implementations of Liu et al. and ours use Matlab built-in functions only, while the others invoke c++ pre-complied functions for computing efficiency, which affects a fair comparison. All these are revealed in the manuscript.

\item Nested chart in Figure 1: For the top one: nested charts are used because the information of the first few iterations is missed in the main figure.  For the bottom one: it shows a zoom-in view to deliver a better representation about the convergence with respect to time.

\item Colored shapes: Considering not everyone has the access to the colored printer, representing the curves in different shapes makes the information still visible in black and white versions.

\item Conclusion: the conclusion part has been shorten.

\item The linguistic and reference errors have been corrected.
\end{itemize}

\end{titlepage}
% uncomment for using teaser
% \teaser{
%  \includegraphics[width=\linewidth]{eg_new}
%  \centering
%   \caption{New EG Logo}
% \label{fig:teaser}
%}

\maketitle
%-------------------------------------------------------------------------
\begin{abstract}
  State-of-the-art methods for Convolutional Sparse Coding usually
  employ Fourier-domain solvers in order to speed up the convolution
  operators. However, this approach is not without shortcomings. For
  example, Fourier-domain representations implicitly assume circular
  boundary conditions and make it hard to fully exploit the sparsity
  of the problem as well as the small spatial support of the filters.

  In this work, we propose a novel stochastic spatial-domain solver,
  in which a randomized subsampling strategy is introduced during the
  learning sparse codes. Afterwards, we extend the proposed strategy
  in conjunction with online learning, scaling the CSC model up to
  very large sample sizes. In both cases, we show experimentally that
  the proposed subsampling strategy, with a reasonable selection of
  the subsampling rate, outperforms the state-of-the-art
  frequency-domain solvers in terms of execution time without losing
  the learning quality. Finally, we evaluate the effectiveness of the
  over-complete dictionary learned from large-scale datasets, which demonstrates an
  improved sparse representation of the natural images on account of
  more abundant learned image features.
%-------------------------------------------------------------------------
%  ACM CCS 1998
%  (see https://www.acm.org/publications/computing-classification-system/1998)
% \begin{classification} % according to https://www.acm.org/publications/computing-classification-system/1998
% \CCScat{Computer Graphics}{I.3.3}{Picture/Image Generation}{Line and curve generation}
% \end{classification}
%-------------------------------------------------------------------------
%  ACM CCS 2012
%   (see https://www.acm.org/publications/class-2012)
%The tool at \url{http://dl.acm.org/ccs.cfm} can be used to generate
% CCS codes.
%Example:
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010178.10010224.10010240.10010241</concept_id>
<concept_desc>Computing methodologies~Image representations</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003809.10010047.10010048</concept_id>
<concept_desc>Theory of computation~Online learning algorithms</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Image representations}
\ccsdesc[100]{Theory of computation~Online learning algorithms}

\printccsdesc
\end{abstract}

\input{Introduction}

\input{CSCmodel}

\input{SCSCmodel}

\input{Results}

\input{Conclusion}

% bibtex
\bibliographystyle{eg-alpha-doi}
\bibliography{egbib}

\end{document}

### 2019-08-19 VMV19/supplement.tex
add directory

--- 2018-11-20 cvpr2019/supplement.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% ---------------------------------------------------------------------------
+% Author guideline and sample document for EG publication using LaTeX2e input
+% D.Fellner, v1.15, Dec 14, 2018
 
-\usepackage{cvpr}
+\documentclass{egpubl}
+\usepackage{EGVMV19}
+
+% --- for  Annual CONFERENCE
+% \ConferenceSubmission   % uncomment for Conference submission
+% \ConferencePaper        % uncomment for (final) Conference Paper
+% \STAR                   % uncomment for STAR contribution
+% \Tutorial               % uncomment for Tutorial contribution
+% \ShortPresentation      % uncomment for (final) Short Conference Presentation
+% \Areas                  % uncomment for Areas contribution
+% \MedicalPrize           % uncomment for Medical Prize contribution
+% \Education              % uncomment for Education contribution
+% \Poster                 % uncomment for Poster contribution
+% \DC                     % uncomment for Doctoral Consortium
+%
+% --- for  CGF Journal
+% \JournalSubmission    % uncomment for submission to Computer Graphics Forum
+% \JournalPaper         % uncomment for final version of Journal Paper
+%
+% --- for  CGF Journal: special issue
+% \SpecialIssueSubmission    % uncomment for submission to , special issue
+% \SpecialIssuePaper         % uncomment for final version of Computer Graphics Forum, special issue
+%                          % EuroVis, SGP, Rendering, PG
+% --- for  EG Workshop Proceedings
+ \WsSubmission      % uncomment for submission to EG Workshop
+% \WsPaper           % uncomment for final version of EG Workshop contribution
+% \WsSubmissionJoint % for joint events, for example ICAT-EGVE
+% \WsPaperJoint      % for joint events, for example ICAT-EGVE
+% \Expressive        % for SBIM, CAe, NPAR
+% \DigitalHeritagePaper
+% \PaperL2P          % for events EG only asks for License to Publish
+
+% --- for EuroVis
+% for full papers use \SpecialIssuePaper
+% \STAREurovis   % for EuroVis additional material
+% \EuroVisPoster % for EuroVis additional material
+% \EuroVisShort  % for EuroVis additional material
+
+% !! *please* don't change anything above
+% !! unless you REALLY know what you are doing
+% ------------------------------------------------------------------------
+\usepackage[T1]{fontenc}
+\usepackage{dfadobe}
+
+\usepackage{cite}  % comment out for biblatex with backend=biber
+% ---------------------------
+%\biberVersion
+\BibtexOrBiblatex
+%\usepackage[backend=biber,bibstyle=EG,citestyle=alphabetic,backref=true]{biblatex}
+%\addbibresource{egbibsample.bib}
+% ---------------------------
+\electronicVersion
+\PrintedOrElectronic
+% for including postscript figures
+% mind: package option 'draft' will replace PS figure by a filename within a frame
+\ifpdf \usepackage[pdftex]{graphicx} \pdfcompresslevel=9
+\else \usepackage[dvips]{graphicx} \fi
+
+\usepackage{egweblnk}
+
 \usepackage{times}
@@
 \usepackage{cuted}
+\input{macro}
+% ---------------------------------------------------------------------
+% end of prologue
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+% EG author guidelines plus sample file for EG publication using LaTeX2e input
+% D.Fellner, v2.03, Dec 14, 2018
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\title{Stochastic Convolutional Sparse Coding \\
+        Supplementary Material}
 
-\def\cvprPaperID{3722} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+% for anonymous conference submission please enter your SUBMISSION ID
+% instead of the author's name (and leave the affiliation blank) !!
+% for final version: please provide your *own* ORCID in the brackets following \orcid; see https://orcid.org/ for more details.
+\author{Submission ID: 1010}
+%\author[D. Fellner \& S. Behnke]
+%{\parbox{\textwidth}{\centering D.\,W. Fellner\thanks{Chairman Eurographics Publications Board}$^{1,2}$\orcid{0000-0001-7756-0901}
+%        and S. Behnke$^{2}$\orcid{0000-0001-5923-423X}
+%%        S. Spencer$^2$\thanks{Chairman Siggraph Publications Board}
+%        }
+%        \\
+%% For Computer Graphics Forum: Please use the abbreviation of your first name.
+%{\parbox{\textwidth}{\centering $^1$TU Darmstadt \& Fraunhofer IGD, Germany\\
+%         $^2$Graz University of Technology, Institute of Computer Graphics and Knowledge Visualization, Austria
+%%        $^2$ Another Department to illustrate the use in papers from authors
+%%             with different affiliations
+%       }
+%}
+%}
+% ------------------------------------------------------------------------
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+% if the Editors-in-Chief have given you the data, you may uncomment
+% the following five lines and insert it here
+%
+% \volume{36}   % the volume in which the issue will be published;
+% \issue{1}     % the issue number of the publication
+% \pStartPage{1}      % set starting page
 
-\input{macro}
+%-------------------------------------------------------------------------
 \begin{document}
 
-%%%%%%%%% TITLE
-\title{Stochastic Convolutional Sparse Coding \\ Supplementary Material}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
+% uncomment for using teaser
+% \teaser{
+%  \includegraphics[width=\linewidth]{eg_new}
+%  \centering
+%   \caption{New EG Logo}
+% \label{fig:teaser}
+%}
 
 \maketitle
-
+%-------------------------------------------------------------------------
 \section{Solvers for LASSO and QCQP}
@@
 
-\begin{figure*}[h]
-\centering
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
-\end{subfigure}
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
-  \end{subfigure}
-\caption{Zoom-in view of the filters from Fig.~1 of the main manuscript.}
-\end{figure*}
+\section{Additional Experiments}
 
-\section{Zooming in on the Filters}
-
-Here we zoom in on the filters from Fig.~1 in the main manuscript. Notice that our filters look more smooth for those Gabor-like filters and also contains less number of noise-like filters.
-
-\section{Additional Experiments}
-In order to show the robustness of the proposed algorithms, We also conduct experiments on city dataset.
-We first compare SBCSC with the state-of-the-art batch-mode algorithm, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}.
-Similar to the results shown in Fig.~1 in the main manuscript, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm with better outcomes and runtime performance.
-Since the learning is performed on handful datasets, both of them learn quite a few data-specific image features.
-These data-specific image features have the shortage of the generalization ability, which can be revealed in the image inpainting application.
-For example, the eighth image, which contains a large portion of the texture information existed in the filters learned from city dataset, can be significantly better reconstructed by such filters compared to using those learned from fruit dataset.
-However, it may exhibit poorer performance on other types of images.
-
-\begin{figure*}[h]
-\begin{subfigure}{0.5\textwidth}
+\begin{figure}[h]
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/iteVSobj-city.pdf}
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/timeVSobj-city.pdf}
@@
 
+\caption{Experimental results obtained on the city dataset. Convergence comparison between the-state-of-art batch method and SBCSC with different subsampling probability.}
+\label{fig:subsampleResult-city}
+\end{figure}
+
+In order to show the robustness of the proposed algorithms, We also conduct experiments on city dataset.
+We first compare SBCSC with the state-of-the-art batch-mode algorithm, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}.
+Similar to the results shown in Fig.~1 in the main manuscript, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm in terms of runtime performance.
+
+\begin{figure}[h]
 \centering
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/batchCity100.pdf}
-\end{subfigure}
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/heideCity100.pdf}
-\end{subfigure}
-\vspace{0.2cm}
-
-    \resizebox{0.8\linewidth}{!}{
-        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
-            \cline{1-11}
-            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
-            \hline
-            PSNR~[10] & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
-            \hline
-            PSNR ours & \textbf{29.78} & \textbf{28.14} & \textbf{29.67}  & \textbf{29.85} & \textbf{28.88} & \textbf{29.95} & \textbf{27.97} & \textbf{30.37} & \textbf{27.14} & \textbf{30.89} \\
-            \hline
-        \end{tabular} }
-
-\caption{Experimental results obtained on the city dataset.
-Top: Convergence comparison between the-state-of-art batch method and SBCSC with different subsampling probability.
-Middle: Learned filters by SBCSC with $p=0.1$ and the comparable method.
-Even though these dictionaries look similar, our method learns more smooth filters.
-Compared to the learned filters in Fig.~1 of the main manuscript, they have different representations of the dictionaries, where data-specific features are learned from handful training images.
-Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters in the image inpainting application.}
-\label{fig:subsampleResult-city}
-\end{figure*}
-
-We then compare SOCSC with the state-of-the-art online algorithm on city dataset, the results of which are shown in Fig.\ \ref{fig:onlineSmall-city}.
-Similar to the results presented in Fig.~3 of the main manuscript, our method obtains comparable outcomes, meanwhile, achieves roughly $6 \times$ speedup.
-
-\section{Over-complete Dictionary and Large Datasets}
-\begin{figure*}[h]
-\centering
-\begin{subfigure}{0.49\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
 \end{subfigure}
-\begin{subfigure}{0.49\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
@@
 \caption{Experimental results obtained on city dataset.
-Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach.
-Right: Testing PSNR with respect to execution time.}
+Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach.
+Bottom: Testing PSNR with respect to execution time.}
 \label{fig:onlineSmall-city}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[h]
-\centering
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/nonZeroElement.pdf}
-\end{subfigure}
-\begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=1\linewidth]{figure/reconPSNR.pdf}
-\end{subfigure}
-
-\caption{Left: number of non-zero elements in the codes for different images ($10 ~ 256 \times 256$ images). Right: PSNR between the reconstructed images and the original ones.}
-\label{fig:overVSunder}
-\end{figure*}
+We then compare SOCSC with the state-of-the-art online algorithm on city dataset, the results of which are shown in Fig.\ \ref{fig:onlineSmall-city}.
+Similar to the results presented in Fig.~3 of the main manuscript, our method obtains comparable outcomes, meanwhile, achieves roughly $6 \times$ speedup.
 
@@
 
-In this section, we first show the improved sparse representation of the natural images with over-complete dictionaries ($K=400$) over under-complete ones ($K=100$).
-The numerical comparisons of number of non-zero elements and its corresponding reconstruction PSNR for various images are shown in Fig.~\ref{fig:overVSunder}.
-Here, we define the non-zero elements as the codes whose coefficient is no less than $0.1$.
-We could observe that at all times, using over-complete dictionary leads to a sparser representation of the images, roughly $8\%-10\%$ reduction on the non-zero elements.
-Meanwhile, it achieves dramatically improved reconstruction quality, over $1$ dB on average.
+\section{Over-complete Dictionary and Large Datasets}
 
-We then verify the importance of a large dataset when learning the over-complete dictionary.
+We verify the importance of a large dataset when learning the over-complete dictionary.
 in Fig.~\ref{fig:overCompleteDic-dataset}, we show a visual and quantitative comparisons between the over-complete dictionaries respectively learned by batch-mode algorithm on small dataset (the fruit dataset) and online-mode algorithm on large dataset (1000 images).
@@
 \end{document}
-
-% --- DO NOT DELETE ---
-% Local Variables:
-% mode: latex
-% mode: flyspell
-% mode: TeX-PDF
-% End:

### 2019-08-20 VMV19/Results.tex
small edits

@@
 We first validate the proposed algorithms on the fruit and city
-datasets~\cite{zeiler2010deconvolutional}, where each consists of 10
+datasets~\cite{zeiler2010deconvolutional}, that each consist of 10
 training images of size $100 \times 100$. The online-mode algorithms
@@
 algorithm~\cite{heide2015fast} are shown in
-Fig.~\ref{fig:subsampleResult} \changed{(the compared method uses a similar number of iterations as ours to reach convergence)}. A different selection of the
+Fig.~\ref{fig:subsampleResult} \changed{(the comparison method uses a similar number of iterations as ours to reach convergence)}. A different selection of the
 subsampling rate reveals that the proposed strategy will slightly

### 2019-08-20 VMV19/SCSCmodel.tex
small edits

@@
 %property of the CSC model.
-\changed{Our proposed randomization approach shares a similar idea as utilized in the stochastic Frank-Wolfe
-algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}.  The general idea of that is to solve the optimization problem on a subset of the variables at each iteration, which are
+\changed{Our proposed randomization approach utilizes ideas similar to the stochastic Frank-Wolfe
+algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}.  The general idea is to solve the optimization problem on a subset of the variables at each iteration, which are
 randomly extracted based on a certain probability distribution.} For the proposed algorithm, each iteration extracts
